---
title: "_1_TextualAnalysis"
author: "André K. Rodarte"
date: "2026-05-07"
output: html_document
---

```{r setup, echo=TRUE, results='hide', message=FALSE, warning=FALSE}
library(here)
library(tidyverse)
library(tidytext)
library(tokenizers)
library("lexiconPT")
library(readr)
library(dplyr)
library(stringi)
library(rlang)
library(fuzzyjoin)
library(stringi)
library(tibble)
library(purrr)
library(tidyr)
library(stringr)
```

**Set up**

```{r}
# Set working directory
setwd("C:/Users/andre/Documents/UT GitHub/VotingMachines")


# Cleaning set up
clean_text <- function(x) {
  x %>%
    stringi::stri_trans_general(id = "Latin-ASCII") %>%
    tolower() %>%
    gsub("[[:punct:]]", "", ., perl = TRUE) %>%
    gsub("[^[:print:]]", "", ., perl = TRUE) %>%
    gsub("🄲|🯲", "", ., perl = TRUE)
}

# Formatting options
format_p_apa <- function(p) {
  dplyr::case_when(
    is.na(p)        ~ NA_character_,
    p < .001        ~ "< .001",
    p < .01         ~ paste0("= .", stringr::str_pad(round(p, 3) * 1000, 3, pad = "0")),
    p < .05         ~ paste0("= .", stringr::str_pad(round(p, 3) * 1000, 3, pad = "0")),
    TRUE            ~ paste0("= .", stringr::str_pad(round(p, 2) * 100, 2, pad = "0"))
  )
}

# Textual analysis function
make_re <- function(keywords) {
  # whole-word boundary for Unicode letters:
  # not preceded by a letter, not followed by a letter
  str_c("(?<!\\p{L})(?:", str_c(keywords, collapse = "|"), ")(?!\\p{L})")
}

count_re <- function(x, re) {
  stringi::stri_count_regex(
    x, re,
    opts_regex = stringi::stri_opts_regex(
      case_insensitive = FALSE,
      dotall = TRUE
      # uword not needed when you already control boundaries with lookarounds
    )
  )
}



sig_stars <- function(p) {
  dplyr::case_when(
    is.na(p) ~ "",
    p < .001 ~ "***",
    p < .01  ~ "**",
    p < .05  ~ "*",
    TRUE     ~ ""
  )
}
```

## Format text

```{r, results='hide', message=FALSE, warning=FALSE}
df_FB <- readr::read_csv(
  here::here("..", "_data",
             "Updated_FB_Data_with_OCR.csv"),
  show_col_types = FALSE) %>%
  dplyr::select(
    -id, -unix_timestamp, -page_category, -page_top_country,
    -page_description, -sponsor_name, -sponsor_id, -sponsor_category
  ) %>%
  dplyr::mutate(
    timestamp = as.POSIXct(timestamp, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")
  ) %>%
  dplyr::filter(
    timestamp >= as.POSIXct("2019-01-01 00:00:00", tz = "UTC") &
      timestamp <= as.POSIXct("2022-12-30 23:59:59", tz = "UTC")
  ) %>%
  dplyr::mutate(postID = dplyr::row_number())



df_FB <- df_FB %>%
  mutate(across(
    c(body, body_image, body_link, body_description, ocr_text),
    clean_text
  ))

#Combine text
df_FB <- df_FB %>%
  mutate(
    text_combined = paste(
      coalesce(body, ""),
      coalesce(body_image, ""),
      coalesce(body_link, ""),
      coalesce(body_description, ""),
      coalesce(ocr_text, ""),
      sep = " "
    ) %>%
      str_squish()  
  )
```

```{r}
df_FB$post_format <- dplyr::recode(df_FB$type, 
                         #Visual formats
                         "Photo" = "Image",
                         #Textual formats
                         "Link" = "Text", 
                         "Status" = "Text", 
                         #Video formats
                         "Native Video" = "Video", 
                         "Video" = "Video", 
                         "Live Video Complete" = "Video", 
                         "YouTube" = "Video", 
                         "Live Video Scheduled" = "Video", 
                         "Live Video" = "Video")

df_FB$post_format <- factor(df_FB$post_format, levels = c("Image", "Video", "Text"))

# Followers
df_FB$page_followers <- as.numeric(gsub("[^0-9]", "", df_FB$page_followers))

# Hashtags
df_FB$has_hashtags <- ifelse(is.na(df_FB$hashtags) | df_FB$hashtags == "", 0, 1)
df_FB$has_hashtags <- factor(df_FB$has_hashtags)

#ENGAGEMENT
df_FB <- df_FB %>%
  mutate(engagement = rowSums(dplyr::select(., 
    likes, likes_love, likes_wow, likes_haha, 
    likes_sad, likes_angry, likes_care, 
    comments, shares), 
    na.rm = TRUE))

# Dealing with exceptions
df_FB <- df_FB %>%
  dplyr::mutate(
    author = dplyr::if_else(
      author == "geninhozuliani.pag",
      "geninhozuliani",
      author
    )
  )
```


```{r}
deputados_df_handles <- read_csv("C:/Users/andre/OneDrive/UT Austin/Dissertation [PhD UT]/Dissertation Articles/Lacracao Logic/_unprocessed_data/Platform_Handles.csv") 

norm_key <- function(x) {
  x %>%
    as.character() %>%
    stringi::stri_trans_general("Latin-ASCII") %>%
    str_to_lower() %>%
    str_replace("^@", "") %>%
    str_replace_all("[0-9]+", "") %>% 
    str_replace_all("[^a-z0-9]", "") %>%
    str_squish()
}
  
# Safe left join with exact match
handles_unique <- deputados_df_handles %>%
  dplyr::mutate(fb_key = norm_key(facebook_handle)) %>%
  dplyr::filter(!is.na(fb_key), fb_key != "") %>%
  dplyr::distinct(fb_key, .keep_all = TRUE) %>%
  dplyr::select(fb_key, party, state)


# Join into df_FB
df_FB <- df_FB %>%
  dplyr::mutate(fb_key = norm_key(author)) %>%
  dplyr::left_join(handles_unique, by = "fb_key")  %>%
  dplyr::select(-fb_key)
 
 #Check
 # unmatched_authors <- df_FB %>%
 #  dplyr::filter(is.na(party)) %>%
 #  dplyr::distinct(author) %>%
 #  dplyr::arrange(author)

 # Exceptions
 df_FB <- df_FB %>%
  dplyr::mutate(
    party = dplyr::case_when(
      author == "cleberverde.1010"     ~ "REPUBLICANOS",
      author == "deputadojoaocampos"   ~ "PSB",
      author == "joaobacelaroficial"   ~ "PL",
      TRUE ~ party
    ),
    state = dplyr::case_when(
      author == "cleberverde.1010"     ~ "MA",
      author == "deputadojoaocampos"   ~ "PE",
      author == "joaobacelaroficial"   ~ "BA",
      TRUE ~ state
    )
  )
```

##### Parties' Ideology
```{r}
# List of parties and their respective ideological score
parties <- read_csv("C:/Users/andre/OneDrive/UT Austin/Dissertation [PhD UT]/Dissertation Articles/Lacracao Logic/_unprocessed_data/parties.csv")

df_FB <- df_FB %>%
  mutate(party = str_to_upper(party))   

parties <- parties %>%
  mutate(Party = str_to_upper(Party))

# Join ideological score
df_FB <- df_FB %>%
  left_join(
    parties %>% dplyr::select(Party, `2021_ideological_score`),
    by = c("party" = "Party")
  )
```

Note: I added the same ideological score as SOLIDARIEDADE to PROS considering: <https://www.tse.jus.br/comunicacao/noticias/2023/Fevereiro/partido-republicano-da-ordem-social-pros-e-incorporado-ao-solidariedade>. By the same criterium, I gave the same ideological score to PTB and PATRIOTA: <https://www.cnnbrasil.com.br/politica/tse-aprova-fusao-de-ptb-e-patriota-e-novo-partido-tera-direito-a-r-228-mi/>.

#### PEC135

**Adding information about parliamentarians and how they voted**. Information about votes taken from: <https://www.camara.leg.br/presenca-comissoes/votacao-portal?reuniao=62583&itemVotacao=9968>.
<https://www.cartacapital.com.br/cartaexpressa/pec-do-voto-impresso-veja-como-votou-cada-deputado/>.


```{r}
handles <- readr::read_csv(
  "data/Platform_Handles_Voting_Records.csv",
  col_types = cols(PEC135 = col_double())
) 

handles_pec <- handles %>%
  dplyr::select(facebook_handle, PEC135) %>%
  dplyr::distinct(facebook_handle, .keep_all = TRUE)

df_FB_with_PEC135 <- df_FB %>%
  dplyr::left_join(
    handles_pec,
    by = c("author" = "facebook_handle")
  )

# Check
# 5. Check how many posts received PEC135 information
df_FB_with_PEC135 %>%
  dplyr::summarise(
    total_posts = dplyr::n(),
    matched_posts = sum(!is.na(PEC135)),
    unmatched_posts = sum(is.na(PEC135)),
    matched_prop = mean(!is.na(PEC135))
  )

# Inspect
unmatched_authors <- df_FB_with_PEC135 %>%
  dplyr::filter(is.na(PEC135)) %>%
  dplyr::distinct(author) %>%
  dplyr::arrange(author)

df_FB_with_PEC135 %>%
  dplyr::distinct(author, PEC135) %>%
  dplyr::count(PEC135)
```

449 deputados registraram voto na PEC 135/19 e cerca de 64 deputados não tiveram voto computado — ou estavam ausentes ou não interagiram com o painel. Há 192 parlamentares que votaram a favor da PEC e estão no sample. Há 201 que votaram contra e estão no sample. 92 não tiveram match. 

# Communication Style

```{r}
keywords_parochial <- c(
  # support / credit-claiming / delivery
  "apoio",
  "apoi(?:ar|o|a|am|amos|ei|ou|aram|ando|ad[oa]s?)",

  # infrastructure / public works
  "asfaltic[oa]s?",
  "calcad(?:a|as)?",
  "infraestrutura",
  "investimento(?:s)?",
  "obra(?:s)?",
  "paviment(?:ar|a|ou|amos|aram|ando)",
  "pavimentac(?:ao|oes)",
  "recapeamento(?:s)?",
  "revitalizac(?:ao|oes)",

  # goods/services delivered
  "assistencia(?:s)?",
  "beneficio(?:s)?",
  "equipamento(?:s)?",
  "exame(?:s)?",
  "mobiliari[oa]s?",
  "multira(?:o|os)",

  # earmarks
  "liberei",
  "repass(?:ar|o|a|am|amos|ei|ou|aram|ando|ad[oa]s?)",
  "destin(?:ar|o|a|am|amos|ei|ou|aram|ando|ad[oa]s?)",
  "custeio",
  "emenda(?:s)?",
  "recurso(?:s)?",
  "verba(?:s)?",
  "repasse(?:s)?",
  "remessa(?:s)?",
  "destinad[ao]s?",
  "destinacao",
  "milha(?:o|oes)",

  # local politics / municipal actors
  "municipal(?:es)?",
  "municipio(?:s)?",
  "lideranc(?:a|as)",
  "prefeit(?:o|a|os|as)",
  "prefeitura(?:s)?",
  "vereador(?:a|as|es)?",
  "secretari[ao]s?",
  "superintendente(?:s)?",
  "gestor[ae]s? municipal(?:es)?",
  "demandas do municipio",
  "demandas municipais",
  "necessidade(?:s)?"
)

pattern_parochial <- paste(keywords_parochial, collapse = "|")


#######################################
#######################################
keywords_programmatic <- c(
  # institutional arenas
  "ccj",
  "comiss(?:ao|oes)",
  "plenario",
  "pauta(?:s)?",
  "pautar",
  "sess(?:ao|oes)",
  "tramit(?:ar|e)",
  "tramitac(?:ao|oes)",
  "urgencia",

  # core legislative objects
  "lei(?:s)?",
  "legislacao",
  "legislativo",
  "projeto(?:s)?",
  "decreto(?:s)?",
  "medida(?:s)?",
  "dispositivo(?:s)?",
  "materia(?:s)?",
  "normativ[oa]s?",
  "diretriz(?:es)?",
  "mudancas no codigo",

  # legality / constitutionality
  "constitucional(?:idade)?",
  "inconstitucional(?:idade)?",

  # deliberation / evaluation
  "analise(?:s)?",
  "analisad[oa]s?",
  "apreci(?:ar|ac(?:ao|oes))",
  "articulac(?:ao|oes)",
  "articulad[oa]s?",
  "deliberac(?:ao|oes)",
  "debate(?:s)?",
  "definic(?:ao|oes)",
  "validade",

  # approval / enactment
  "aprova(?:r|c(?:ao|oes))",
  "aprovad[oa]s?",
  "promulgac(?:ao|oes)",
  "promulgar",
  "publicac(?:ao|oes)",
  "sanc(?:ao|ionar|ionad[ao]s?)",
  "veto(?:s)?",
  "vetar",
  "vigor",

  # regulation / reform
  "reforma(?:s)?",
  "regimental",
  "regimento",
  "regulamentac(?:ao|oes)",
  "regulamentar",
  "revog(?:ar|ac(?:ao|oes))?",
  "suprimir",
  "suspens(?:ao|oes)",
  "suspender",
  "proibic(?:ao|oes)",
  "isenc(?:ao|oes)",

  # legislative protocols
  "coautora?s?",
  "oficio(?:s)?",
  "parecer(?:es)?",
  "redac(?:ao|oes)",
  "requerimento(?:s)?",
  "protocol(?:ar|o|os|ei|amos|ou|aram|ando)?",

  # voting
  "voto(?:s)?",
  "vot(?:ar|ac(?:ao|oes))",
  "votei",
  "votamos",
  "votaram",
  "votarei"
)

pattern_programmatic <- paste(keywords_programmatic, collapse = "|")
#######################################
#######################################


#######################################
#######################################
keywords_propagandistic <- c(
  # attention / urgency
  "atencao",
  "urgente",
  "grave(?:s)?",
  "gravissim[oa]s?",
  "bomb(?:a|astica|asticas)",
  "escandal(?:o|osa)",
  "absurdo",

  # exposure / revelation / denunciation frames
  "investig(?:ar|a(?:cao|coes)|o|ou|uei|amos|am|ando)",
  "irregularidad(?:e|es)",
  "suspeit[oa]s?",
  "mentir(?:a|u|am|emos|ei|ou|indo)?",
  "esquema(?:s)?",
  "vazamento(?:s)?",
  "indicio(?:s)?",
  "prova(?:s)?",
  "revel(?:ar|a(?:cao|coes)|ei|ou|am|amos|ad[oa]s?)",
  "revelaram",
  "exposic(?:ao|oes)",
  "expost[oa]s?",
  "expor",
  "exp(?:o|u)s(?:t[oa]s?)?",
  "descobr(?:ir|i|iu|indo|imos|iram)",
  "denunc(?:ia|iar|iei|iou|iam|iamos|as|os)",
  "denunciad[oa]s?",
  "apur(?:ar|ou)",
  "deflagrad[oa]s?",
  "delat(?:ar|ou)",
  "demonstr(?:a|am|ou|aram)",
  "fato(?:s)?",

  # press/media + narrative framing
  "imprensa",
  "jornalista(?:s)?",
  "midia",
  "revista(?:s)?",
  "censura",
  "censurad[oa]s?",
  "narrativa(?:s)?",
  "fake\\s+news",
  "fals[oa]s?",
  "farsa(?:s)?|farso(?:s|a|as|os)?",
  "mentir(?:a|u|am|emos|ei|ou|indo)?|mentira(?:s)?|mentiros[oa]s?",

  # “explainer” posture
  "entenda",
  "esclarecedor",
  "explic(?:a|acoes|ativo|ativa|ativos|ativas)",
  "resumo",
  "mostra\\s+bem",
  "tese",
  "opiniao",
  "question(?:ar|ou|ei|amos|am|ando)?",
  "depoimento(?:s)?",
  "testemunhei",
  "descobr(?:ir|i|iu|indo|imos|iram)",
  "desmascar(?:ar|ei|ou|amos|ad[oa]s?)"
)

pattern_propagandistic <- paste(keywords_propagandistic, collapse = "|")
```

```{r}
re_programmatic   <- make_re(keywords_programmatic)
re_parochial      <- make_re(keywords_parochial)
re_propagandistic <- make_re(keywords_propagandistic)

df_FB_with_PEC135 <- df_FB_with_PEC135 %>%
  mutate(
    programmatic_matches   = count_re(text_combined, re_programmatic),
    parochial_matches      = count_re(text_combined, re_parochial),
    propagandistic_matches = count_re(text_combined, re_propagandistic)
  )
```



# Export

```{r}
# df_FB_clean <- df_FB_with_PEC135 %>%
#   dplyr::rename(ideology_2021 = `2021_ideological_score`)

df_FB_processed <- df_FB_with_PEC135 %>%
  dplyr::select(postID, 
                author,
                page_name,
                thread_id,
                text_combined,
                timestamp,
                page_created,
                page_likes,
                page_id,
                page_followers,
                type,
                post_format,
                has_hashtags,
                engagement,
                interactions,
                comments,
                shares,        
                likes, 
                likes_love,  
                likes_wow,   
                likes_haha,   
                likes_sad,   
                likes_angry,
                likes_care,
                views_post,
                views_total,
                views_total_crossposts,
                hashtags,
                url,
                url_original,
                party,
                state,
                ideology_2021,
                PEC135,
                programmatic_matches,
                parochial_matches,
                propagandistic_matches
                )

# Save as CSV
readr::write_csv2(
  df_FB_processed,
  file.path("_processed_data", "df_FB_processed.csv")
)

# Save as RDS
readr::write_rds(
  df_FB_processed,
  file.path("_processed_data", "df_FB_processed.rds")
)
```



