---
title: "_Practice_Mapping"
author: "André K. Rodarte"
date: "2026-05-11"
output: html_document
---

```{r setup, include=FALSE}
library(here)
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(Matrix)
library(quanteda)
library(spacyr)

library(igraph)
library(showtext)
library(sysfonts)
library(ggraph)
library(ggplot2)
library(tibble)
library(ggrepel)
library(graphlayouts)
```

# Set up
```{r}
# Data
df_fb <- read_rds(
  here("_processed_data", "df_fb_GPT.rds"))
df_fb_election <- read_rds(
  here("_processed_data", "df_fb_election.rds"))
# Quick check
glimpse(df_fb)

# Other
options(digits = 3)
set.seed(999) 

#Output
output_path <- "C:/Users/andre/Documents/GitHub/VotingMachines/_output"
```

### Helpers

```{r}
# -------------------------
# Convert long account-feature data into a sparse account-by-feature matrix.
# Rows = individual politicians' accounts.
# Columns = practice-vector dimensions.
# -------------------------
make_sparse_practice_matrix <- function(data, account_col, feature_col, value_col = "n") {
  
  account_col <- rlang::ensym(account_col)
  feature_col <- rlang::ensym(feature_col)
  value_col   <- rlang::ensym(value_col)
  
  data_clean <- data %>%
    filter(
      !is.na(!!account_col),
      !is.na(!!feature_col)
    ) %>%
    group_by(!!account_col, !!feature_col) %>%
    summarise(value = sum(!!value_col, na.rm = TRUE), .groups = "drop")
  
  accounts <- sort(unique(dplyr::pull(data_clean, !!account_col)))
  features <- sort(unique(dplyr::pull(data_clean, !!feature_col)))
  
  i <- match(dplyr::pull(data_clean, !!account_col), accounts)
  j <- match(dplyr::pull(data_clean, !!feature_col), features)
  
  sparseMatrix(
    i = i,
    j = j,
    x = data_clean$value,
    dims = c(length(accounts), length(features)),
    dimnames = list(accounts, features)
  )
}


# Normalize each account vector by its row sum.
# This is useful when we want feature values to represent each account's
# relative composition of practices rather than absolute counts.
# For pairwise similarity, however, raw volume is removed mainly by
# cosine similarity, which L2-normalizes vectors internally.
row_l1_normalize <- function(mat) {
  rs <- Matrix::rowSums(mat)
  rs[rs == 0] <- 1
  mat / rs
}


# L2-normalization for cosine similarity.
row_l2_normalize <- function(mat) {
  rs <- sqrt(Matrix::rowSums(mat^2))
  rs[rs == 0] <- 1
  mat / rs
}


# Compute cosine similarity between account-level practice vectors.
cosine_similarity <- function(mat) {
  mat_l2 <- row_l2_normalize(mat)
  sim <- tcrossprod(mat_l2)
  diag(sim) <- 0
  sim
}


# Convert a cosine similarity matrix into a fixed-threshold edge list.
similarity_to_edgelist <- function(sim_mat, threshold = 0.10) {
  
  sim_df <- as.data.frame(as.table(as.matrix(sim_mat)), stringsAsFactors = FALSE) %>%
    dplyr::rename(
      source = Var1,
      target = Var2,
      weight = Freq
    ) %>%
    dplyr::mutate(
      source = as.character(source),
      target = as.character(target)
    ) %>%
    dplyr::filter(
      source < target,
      weight >= threshold
    )
  
  sim_df
}


# Align matrices so that all practice matrices contain the same accounts.
align_sparse_rows <- function(mat, all_accounts) {
  
  missing_accounts <- setdiff(all_accounts, rownames(mat))
  
  if (length(missing_accounts) > 0) {
    zero_mat <- sparseMatrix(
      i = integer(0),
      j = integer(0),
      dims = c(length(missing_accounts), ncol(mat)),
      dimnames = list(missing_accounts, colnames(mat))
    )
    
    mat <- rbind(mat, zero_mat)
  }
  
  mat[all_accounts, , drop = FALSE]
}

# -------------------------
# TF-IDF weighting for sparse account-by-feature matrices
# -------------------------
apply_tfidf_sparse <- function(mat, smooth = TRUE) {
  # mat should be an account-by-feature sparse matrix.
  # Rows = accounts/documents.
  # Columns = practice features.
  df_terms <- Matrix::colSums(mat > 0)
  n_docs <- nrow(mat)
  
  if (smooth) {
    # Smoothed IDF avoids extreme values and division issues.
    idf <- log((1 + n_docs) / (1 + df_terms)) + 1
  } else {
    idf <- log(n_docs / df_terms)
  }
  
  mat_tfidf <- mat %*% Matrix::Diagonal(x = as.numeric(idf))
  
  rownames(mat_tfidf) <- rownames(mat)
  colnames(mat_tfidf) <- colnames(mat)
  
  mat_tfidf
}

# -------------------------
# Top features for one account
# -------------------------
get_top_features_account <- function(mat, account, n = 20, clean_prefix = TRUE) {
  
  if (!account %in% rownames(mat)) {
    stop("Account not found in matrix rownames: ", account)
  }
  
  row_vec <- mat[account, , drop = TRUE]
  
  # Extract only non-zero values
  nonzero_idx <- which(row_vec != 0)
  
  if (length(nonzero_idx) == 0) {
    return(
      tibble::tibble(
        account = account,
        feature = character(),
        value = numeric()
      )
    )
  }
  
  out <- tibble::tibble(
    account = account,
    feature = colnames(mat)[nonzero_idx],
    value = as.numeric(row_vec[nonzero_idx])
  ) %>%
    dplyr::arrange(dplyr::desc(value)) %>%
    dplyr::slice_head(n = n)
  
  if (clean_prefix) {
    out <- out %>%
      dplyr::mutate(
        feature_clean = stringr::str_remove(feature, "^[^:]+:")
      ) %>%
      dplyr::select(account, feature, feature_clean, value)
  }
  
  out
}
```

## Stopwords & Domains
```{r}
# Stop-words: states, political parties, social-media vernacular, and procedural words (e.g. "celebrate")
# Municipalities from IBGE API
municipality_terms <- jsonlite::fromJSON(
  "https://servicodados.ibge.gov.br/api/v1/localidades/municipios"
)$nome %>%
  stringi::stri_trans_general(id = "Latin-ASCII") %>%
  stringr::str_to_lower() %>%
  stringr::str_trim() %>%
  unique()

# -------------------------
# Geographic terms
# -------------------------
# Includes Brazilian states, state abbreviations, demonyms, regional terms,
# and geographic hashtag variants identified during inspection.

geographic_terms <- c("ac", "acre", "acreana", "acreano", "afederaldemt", "al", "alagoana", "alagoano", "alagoas", "am", "amapa", "amapaense", "amazona", "amazonas", "amazonense", "amorporroraima", "ap", "araguaia", "arraialdocabo",
  "ba", "bahia", "baiana", "baiano", "bancadacapixaba", "belohorizonte", "boavista", "boraparaiba", "brasil", "brasileira", "brasileiras", "brasileiro", "brasileiros", "brasiliense", "brasilur", "camposdosgoytacazes", "camposgerais", "camposs", "capital", "capitais", "capixaba", "catarina", "catarinense", "ce", "ceara", "cearense", "cearenses", "centro oeste", "centrooeste", "chuvasmg", "cidadaniapr", "compromissocomoparana", "df", "distrito federal", "distritofederal", "duasbarras", "errejota", "es", "espirito santo", "espiritosanto", "estadodabahia", "estadodaparaiba", "estadodeacre", "estadodealagoas", "estadodegoias", "estadodemato grosso", "estadodematogrosso", "estadodematogrossodosul", "estadodemg", "estadodemina", "estadodeminas", "estadodeminasgerais", "estadodepernambuco", "estadoderondonia", "estadoderoraima", "estadoders", "estadodesantacatarina", "estadodesaopaulo", "estadodesc", "estadodesergipe", "estadodesp", "estadodetocantins", "estadodoacre", "estadodoamapa", "estadodoamazonas", "estadodoceara", "estadododistritofederal", "estadodoespiritosanto", "estadodomaranhao", "estadodopara", "estadodoparana", "estadodopiaui", "estadodoriodejaneiro", "estadodoriograndedosul", "estadodorn", "federalrj", "fluminense", "frentepopulardorecife", "gaucha", "gaucho", "go", "goia", "goiana", "goiano", "goias", "governodabahia", "governodoceara", "governorj", "governosp", "grosso", "ibiritemg", "ibiritimig", "interiorsp", "jaraguadosul", "ma", "maranhao", "maranhense", "maranhenses", "maranhaozinho", "mato", "mato grosso", "mato grosso do sul", "matogrossense", "matogrosso", "matogrossodosul", "mg", "miguelcoelhope", "minas", "minas gerais", "minasgeral", "minasgerais", "mineira", "mineiro", "ms", "mt", "mudapiaui", "nordeste", "nordestina", "nordestino", "noroeste", "norte", "novaiguacu", "oeste", "pa", "para", "paraense", "paraiba", "paraibana", "paraibano", "parambuense", "parana", "paranaense", "paulista", "pb", "pe", "pelabahia", "pelomaranhao", "peloparana", "peloparano", "pelopiaui", "pernambuco", "pernambucana", "pernambucano", "pernambucoemfoco", "pi", "piaui", "piauiense", "pontagrossa", "porminas", "porsergipe", "potiguar", "pr", "prafrentesp", "psbma", "psolpa", "ptbahia", "riobonito", "rio", "rio de janeiro", "rio grande do norte", "rio grande do sul", "riodasostras", "riodejaneiro", "riograndedonorte", "riograndedosul", "rj", "rn", "ro", "rondonia", "rondoniense", "roraima", "roraimense", "rr", "rs", "santa catarina", "santacatarina", "santacatarino", "sao paulo", "saogoncalo", "saopaulo", "saopedrodaaldeia", "saudegoias", "saudemg", "sc", "se", "sergipana", "sergipano", "sergipe", "sorocabano", "sp", "spaulo", "sudeste", "sudoeste", "sudoestegoiano", "sul", "sulmatogrossense", "sulmatogrossenses", "to", "tocantinense", "tocantins", "todosporminas", "trabalhandoporgoias", "trabalhandoporpernambuco", "trabalhandoporsergipe", "trabalhandoporsp", "trabalhopelaparaiba", "votuporangasp", "jaraguaense", "itaperiu", "itapocu", "capixabo", "iguacu", "macapenses", "lagartense", "arapiraquense")

# -------------------------
# Party and partisan labels
# -------------------------

party_terms <- c(
  "avante", "avante70", "pensandoavante", "cidadania", "cidadania23", "cidadaniapr", "contecomonovo", "convencaorepublicanos", "dem", "democrata", "democratas", "juntospodemos", "juntospodemosmais", "juntospodemosmal", "mdb", "novo", "novo30", "novodeverdade", "novonacamara", "partido", "partidoliberal", "partidonovo", "partidonovo30", "partidos", "patriota", "patriotape", "patriotarj", "pcb", "psdbac", "pcdob", "pco", "pdt", "phs", "pl22", "plsp", "pmdb", "pmn", "podemos", "pp", "pps", "pr", "prb", "progressista", "progressistas", "progressistassp", "prp", "prtb", "psb", "psb40", "psbma", "psc", "psc20", "pscnacional20", "psd", "psdb", "psdc", "psdnacamara", "psl", "psl17", "pslbrasil", "pslnacamara", "pslraiz", "psol", "psolpa", "pstu", "pt", "ptbahia", "ptb", "ptc", "ptdob", "ptn", "pv", "republicano", "republicanos", "republicanos10", "republicanosnacamara", "republicanosrs", "republicanoss", "solidariedade", "solidariedadecer", "soumdb", "uniaobrasil", "vote19"
)

# -------------------------
# Platform and social media vernacular
# -------------------------

social_media_vernacular_terms <- c(
  "ao vivo", "aovivo", "boanoite", "boasemana", "boatarde", "bomdia", "comente",
  "comentem", "compartilhar", "compartilhe", "compartilhem", "confira", "curta",
  "curtir", "descricao", "detalhe", "dizer", "direct", "email", "foryou", "foryoupage", "foto", "fyp", "getrepost", "hashtag", "inscreva", "instaphoto", "leia", "link", "namidia", "page", "paratodosverem", "pracegover", "pracegorver", "pratodosverem", "published", "repost", "segue", "seguem", "seguindo", "siga", "sigame", "sugestao", "tamo", "tamojunto", "tbt", "tbtdehoje", "text", "timeline", "vamo", "vamo que vamo", "vamoquevamo", "vamos", "viral", "viralvideo", "viralvideos", "video", "post", "from", "live", "play", "reshare",
"makerepost", "storie", "online", "card")

# -------------------------
# Political titles, offices, and generic mandate terms
# -------------------------

political_title_terms <- c(
  "amudancajacomecou", "boratrabalhar", "camara", "camaradosdeputados", "camaradosdeputar", "dep", "depfederal", "deputada", "deputadafederal", "deputado", "deputadofederal", "deputadosdem", "equipe", "federal", "federals", "gabinete", "semprepresente", "praseguiremfrente", "trabalhoquedaresultado", "mandatoderesultados", "politico", "politicos", "pracimadeles", "quemvotounaosearrepende", "senador", "trabalho", "vamosemfrente", "eleicao2022", "eleição2022", "eleicoes2022", "eleições2022")

# -------------------------
# Generic temporal markers
# -------------------------

time_terms <- c(
  "abril", "agosto", "anos", "atras", "atual", "calendario", "ciclo", "dezembro", "domingo", "fevereiro", "fimdesemana", "janeiro", "julho", "junho", "maio", "marco", "novembro", "outubro", "quarta", "quinta", "resumo da semana", "resumodasemana", "resumodasemano", "restrospectiva2020", "retrospectiva", "retrospectiva2018", "retrospectiva2019", "retrospectiva2020", "retrospectiva2021", "sabado", "segunda", "serie", "setembro", "sexta", "terca", "felizdiadospais", "felizdiadasmaes"
)

# -------------------------
# Celebration and greetings
# -------------------------

celebration_terms <- c(
  "abraco", "afetuoso", "agradeco", "amar", "celebrar", "comemoramos", "companheiro", "conforto", "excelente", "felicitacao", "felicidade", "felicidades", "fraterno", "linda", "lindo", "otimo", "parabens", "recebam", "satisfacao", "saudar", "valeu")

# -------------------------
# Generic high-frequency or low-substantive terms
# -------------------------
generic_stop_words <- c("acelerar", "achar", "assuntos", "busco", "cadastro", "cara", "cobrar", "colocamos", "comigo", "correr", "cumpro", "deixe", "detalhe", "dificil", "entao", "escritorio", "espero", "essencial", "estado", "existir", "fiquem", "fique", "foco", "gostaria", "ideal", "imenso", "individual", "iniciar", "intenso", "longo", "misturar", "parar", "peco", "pedir", "pensar", "pessoal", "podemos", "positivo", "precisamos", "profundo", "prol", "pude", "ramal", "referente", "seguimos", "sensacao", "terminamos", "unidade", "usar", "vago", "visar")

# -------------------------
# Combined custom stopwords
# -------------------------
custom_stopwords <- c(
  quanteda::stopwords("pt"),
  municipality_terms,
  geographic_terms,
  party_terms,
  social_media_vernacular_terms,
  political_title_terms,
  time_terms,
  celebration_terms,
  generic_stop_words
) %>%
  stringi::stri_trans_general(id = "Latin-ASCII") %>%
  stringr::str_to_lower() %>%
  stringr::str_trim() %>%
  unique()
```

```{r}
# -------------------------
# Account-specific self terms
# -------------------------
generic_profile_terms <- c(
  "oficial", "deputado", "deputada", "dep", "federal", "senador", "senadora", "vereador", "vereadora", "dr", "dra", "professor", "professora", "psl", "pl", "pt", "psdb", "mdb", "novo", "psol", "brasil", "br", "politico", "politica")


clean_self_term <- function(x) {
  x %>%
    stringr::str_replace_na("") %>%
    stringi::stri_trans_general(id = "Latin-ASCII") %>%
    stringr::str_to_lower() %>%
    stringr::str_replace_all("[^a-z0-9]", " ") %>%
    stringr::str_squish()
}


make_self_terms <- function(author, page_name) {
  
  author_clean <- clean_self_term(author)
  page_clean   <- clean_self_term(page_name)
  
  # Individual components
  author_tokens <- author_clean %>%
    stringr::str_split("\\s+") %>%
    unlist()
  
  page_tokens <- page_clean %>%
    stringr::str_split("\\s+") %>%
    unlist()
  
  # Remove generic profile descriptors
  author_tokens <- author_tokens[
    author_tokens != "" &
      !author_tokens %in% generic_profile_terms
  ]
  
  page_tokens <- page_tokens[
    page_tokens != "" &
      !page_tokens %in% generic_profile_terms
  ]
  
  # Collapsed forms
  author_no_space <- stringr::str_replace_all(author_clean, "\\s+", "")
  page_no_space   <- stringr::str_replace_all(page_clean, "\\s+", "")
  
  author_collapsed <- paste0(author_tokens, collapse = "")
  page_collapsed   <- paste0(page_tokens, collapse = "")
  
  # Remove common profile prefixes/suffixes from author handles
  author_variants <- author_no_space %>%
    stringr::str_replace_all(
      "(oficial|dep|deputado|deputada|federal|senador|senadora)$",
      ""
    ) %>%
    stringr::str_replace_all(
      "^(oficial|dep|deputado|deputada|federal|senador|senadora)",
      ""
    )
  
  # Remove trailing numeric residues
  author_variants_no_numbers <- author_variants %>%
    stringr::str_replace_all("[0-9]+$", "")
  
  # Core name forms
  core_terms <- unique(c(
    author_tokens,
    author_collapsed,
    author_variants,
    author_variants_no_numbers,
    page_tokens,
    page_collapsed
  ))
  
  core_terms <- core_terms[
    !is.na(core_terms) & core_terms != ""
  ]
  
  # Common concatenated profile forms
  # Examples: deputadopimenta, otonidepfederal
  profile_variants <- unique(c(
    core_terms,
    paste0("dep", core_terms),
    paste0("deputado", core_terms),
    paste0("deputada", core_terms),
    paste0("senador", core_terms),
    paste0("senadora", core_terms),
    paste0(core_terms, "oficial"),
    paste0(core_terms, "dep"),
    paste0(core_terms, "federal"),
    paste0(core_terms, "depfederal"),
    paste0(core_terms, "deputadofederal"),
    paste0(core_terms, "deputadafederal")
  ))
  
  # Possessive-like residues after punctuation removal
  profile_variants <- unique(c(
    profile_variants,
    paste0(profile_variants, "s")
  ))
  
  unique(c(
    author_clean,
    author_no_space,
    page_clean,
    page_no_space,
    core_terms,
    profile_variants
  ))
}


account_self_terms <- df_fb %>%
  dplyr::distinct(author, page_name) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(
    term = list(make_self_terms(author, page_name))
  ) %>%
  tidyr::unnest(term) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    term = term %>%
      stringi::stri_trans_general(id = "Latin-ASCII") %>%
      stringr::str_to_lower() %>%
      stringr::str_replace_all("[^a-z0-9]", "")
  ) %>%
  dplyr::filter(
    term != "",
    nchar(term) > 2,
    !term %in% generic_profile_terms,
    !term %in% custom_stopwords
  ) %>%
  dplyr::distinct(author, term)
```

### Domain Setup
```{r}
# Helper functions
normalize_domain <- function(x) {
  x %>%
    stringi::stri_trans_general(id = "Latin-ASCII") %>%
    stringr::str_to_lower() %>%
    stringr::str_trim() %>%
    stringr::str_remove("^https?://") %>%
    stringr::str_remove("^www\\.") %>%
    stringr::str_remove("/.*$") %>%
    stringr::str_trim()
}

make_domain_key <- function(x) {
  x %>%
    stringi::stri_trans_general(id = "Latin-ASCII") %>%
    stringr::str_to_lower() %>%
    stringr::str_replace_all("[^a-z0-9]", "") %>%
    stringr::str_trim()
}

regex_escape <- function(x) {
  stringr::str_replace_all(x, "([][{}()+*^$|\\\\?.])", "\\\\\\1")
}


# -------------------------
# Exclusions
# -------------------------
domains_to_exclude <- c(
  "acessa", "agora", "amazonia", "aovivo", "apple", "archive", "arte",
  "beta", "bit.do", "bit.ly", "bitly", "boatos", "brasis", "buff.ly",
  "campanha", "caneta", "caras", "china", "bolsonaro", "cutt.ly",
  "disparada", "ft", "leiaja", "universal", "unicef", "vice", "contigo",
  "defesa", "dol", "lance", "naoviu", "mural", "page.link", "videos",
  "waze", "24h", "amanha", "anistia", "belem", "clicr", "clicrdc",
  "clicrsc", "clicsc", "cpp", "delegados", "ecoa", "go", "guia",
  "ingresso", "interior", "leia", "liberal", "mapping", "messenger",
  "nossas", "polis", "previ", "revide", "sabesp", "t.ly", "une", "em", "lula", 'leandre', "m.me", "painel", "surgiu", "atarde", "m", "t.co", "bol", "dilma", "unica", "un", "uai", "temas", "politicos", "novo", "pros", "time", "bonde")

domains_to_exclude_lookup <- tibble::tibble(
  excluded_domain_raw = domains_to_exclude) %>%
  dplyr::mutate(
    excluded_domain = normalize_domain(excluded_domain_raw),
    excluded_domain_key = make_domain_key(excluded_domain)
  ) %>%
  dplyr::filter(
    excluded_domain != "",
    excluded_domain_key != ""
  ) %>%
  dplyr::distinct(excluded_domain_key, .keep_all = TRUE)


# -------------------------
# Manually specified media/domain list
# -------------------------
domains_list_manual <- c(
  "94fm", "almapreta", "anchor.fm", "aosfatos", "appsindicato", "band", 
  "bandnewsfm", "bandnewsfmcuritiba", "bandnewsfmrio", "bbc", 
  "brasilsemmedo", "buzzfeed", "cartacapital", "catracalivre", 
  "cbncaruaru", "cbncuritiba", "cbnlondrina", "cbnmaringa", 
  "cbnrecife", "cbnvitoria", "clarin", "cnn", "cnnbrasil", 
  "coalizaonegrapordireitos", "coletivojuntas", "correiobraziliense", 
  "dailymail", "eldiario.es", "eleicoesantirracistas", "elpais", 
  "emdefesadofundoamazonia", "esquerdadiario", "esquerdaonline", 
  "estadao", "exame", "extra.globo", "folha", "g1.globo", 
  "gazetadopovo", "glo.bo", "huffpost", "huffpostbrasil", 
  "independent", "infomoney", "intercept", "istoedinheiro", "istoe", 
  "jacobin", "jovempan", "lemonde", "mblnews", "metropolenoticias", 
  "metropolitanoonline", "midianinja", "mises", "nexojornal", 
  "nytimes", "oantagonista", "observatoriodademocracia", 
  "observatoriodaimprensa", "observatoriodatelevisao", 
  "observatoriodoconhecimento", "observatoriog", "oglobo.globo", 
  "plenonews", "pleno.news", "poder360", "r7", "radiobandeirantes", 
  "radiocabiuna", "radiocacula", "radiocaxias", "radioclubfm.net", 
  "radiocomunitariaclubefm", "radioconvencao", "radiocorredor", 
  "radiocostaverdefm", "radiocruzdemalta", "radiofmz", "radiofolhabv", 
  "radiogeracao", "radioglobocampogrande", "radioguaratuba", 
  "radiohora", "radioiara", "radiointegracaoam1180", "radioipiranga", 
  "radiometropole", "radionereuramos", "radionovaprogresso", 
  "radiopanoramicafm", "radiopeaobrasil", "radioprata", "radiosanfm", 
  "radiosantacruz", "radiosaoluiz", "radiosaopedrense", 
  "radioschroederfm", "radiosoledade", "radiotaquara", "radioterena", 
  "radiotucunare", "radioturmalina", "radiouniversitariafm", 
  "radioveracruz", "radiowebcp", "renovamidia", "reuters", "romanews", 
  "sbt", "substack", "telegraph", "tercalivre", "terrabrasilnoticias", 
  "theguardian", "theintercept", "uol", "veja", "vejario", "vejasp", 
  "washingtonpost", "wikipedia", "wsj", "yahoo") %>%
  normalize_domain()


# -------------------------
# Domains observed in df_fb$domain
# -------------------------
domains_from_df_fb <- df_fb %>%
  dplyr::filter(!is.na(domain), domain != "") %>%
  dplyr::mutate(
    domain = normalize_domain(domain),
    domain_key = make_domain_key(domain)
  ) %>%
  dplyr::filter(domain != "", domain_key != "") %>%
  dplyr::count(domain, domain_key, name = "n_url_mentions") %>%
  dplyr::arrange(dplyr::desc(n_url_mentions), domain)


# -------------------------
# Domain list
# -------------------------
# Includes:
# 1. manually curated media/outlet names
# 2. every domain observed in df_fb$domain
# 3. excludes domains/terms listed in domains_to_exclude
# -------------------------

domains_list <- c(
  domains_list_manual,
  domains_from_df_fb$domain) %>%
  unique() %>%
  sort()

domains_list <- tibble::tibble(domain = domains_list) %>%
  dplyr::mutate(
    domain = normalize_domain(domain),
    domain_key = make_domain_key(domain)) %>%
  dplyr::filter(
    domain != "",
    domain_key != "",
    !domain %in% domains_to_exclude_lookup$excluded_domain,
    !domain_key %in% domains_to_exclude_lookup$excluded_domain_key
  ) %>%
  dplyr::distinct(domain_key, .keep_all = TRUE) %>%
  dplyr::arrange(domain) %>%
  dplyr::pull(domain)


# -------------------------
# Domain lookup
# -------------------------
domain_lookup <- tibble::tibble(domain = domains_list) %>%
  dplyr::mutate(
    domain_key = make_domain_key(domain),
    in_manual_list = domain %in% domains_list_manual,
    in_df_fb_domain = domain %in% domains_from_df_fb$domain
  ) %>%
  dplyr::filter(domain_key != "") %>%
  dplyr::distinct(domain_key, .keep_all = TRUE) %>%
  dplyr::left_join(
    domains_from_df_fb %>%
      dplyr::select(domain, n_url_mentions),
    by = "domain"
  ) %>%
  dplyr::mutate(
    n_url_mentions = dplyr::coalesce(n_url_mentions, 0L),
    domain_source = dplyr::case_when(
      in_manual_list & in_df_fb_domain ~ "manual_and_df_fb_domain",
      in_manual_list & !in_df_fb_domain ~ "manual_only",
      !in_manual_list & in_df_fb_domain ~ "df_fb_domain_only",
      TRUE ~ "unknown"
    )
  ) %>%
  dplyr::arrange(domain_source, dplyr::desc(n_url_mentions), domain)
```

```{r}
# Inspect domain list
# Summary of final domain sources
domain_lookup %>%
  dplyr::count(domain_source, name = "n_domains")

# Full inspection object
domain_lookup_inspection <- domain_lookup %>%
  dplyr::select(
    domain,
    domain_key,
    domain_source,
    in_manual_list,
    in_df_fb_domain,
    n_url_mentions
  ) %>%
  dplyr::arrange(
    dplyr::desc(in_df_fb_domain),
    dplyr::desc(n_url_mentions),
    domain
  )

domain_lookup_inspection %>%
  print(n = 100)

# Optional
# View(domain_lookup_inspection)


# -------------------------
# Inspect exclusions
# -------------------------
excluded_domains_found_in_df_fb <- domains_from_df_fb %>%
  dplyr::semi_join(
    domains_to_exclude_lookup,
    by = c("domain_key" = "excluded_domain_key")
  ) %>%
  dplyr::arrange(dplyr::desc(n_url_mentions), domain)

excluded_domains_found_in_df_fb


excluded_domains_still_in_lookup <- domain_lookup %>%
  dplyr::semi_join(
    domains_to_exclude_lookup,
    by = c("domain_key" = "excluded_domain_key")
  )

excluded_domains_still_in_lookup

nrow(excluded_domains_still_in_lookup)
```

```{r}
# ============================================================
# Domain aliases for textual detection
# ============================================================
# Important:
# domain_lookup can include all observed URL domains.
# domain_aliases should be narrower, because these terms are searched directly
# in post text. Otherwise, every linked domain becomes a possible textual match.

# -------------------------
# Domains eligible for text detection
# -------------------------
# Restrict text matching to manually curated media/outlet domains.
# This prevents thousands of observed URL domains from becoming text aliases.

domains_for_text_detection <- domain_lookup %>%
  dplyr::filter(in_manual_list) %>%
  dplyr::select(domain, domain_key) %>%
  dplyr::distinct()


# -------------------------
# Automatic aliases for curated domains only
# -------------------------
# Examples:
# "g1.globo"   -> "g1.globo", "g1 globo", "g1globo"
# "pleno.news" -> "pleno.news", "pleno news", "plenonews"
# "folha"      -> "folha"

domain_aliases_auto <- domains_for_text_detection %>%
  dplyr::mutate(
    alias_exact = domain,
    alias_spaced = domain %>%
      stringr::str_replace_all("[\\._\\-]+", " ") %>%
      stringr::str_squish(),
    alias_compact = make_domain_key(domain)
  ) %>%
  tidyr::pivot_longer(
    cols = dplyr::starts_with("alias_"),
    names_to = "alias_type",
    values_to = "alias"
  ) %>%
  dplyr::mutate(
    alias = alias %>%
      stringi::stri_trans_general(id = "Latin-ASCII") %>%
      stringr::str_to_lower() %>%
      stringr::str_squish()
  ) %>%
  dplyr::filter(alias != "") %>%
  dplyr::distinct(domain, alias, .keep_all = TRUE)


# -------------------------
# Manual aliases
# -------------------------
# Add aliases for media names that commonly appear as phrases in text.

domain_aliases_manual <- tibble::tribble(
  ~domain,                  ~alias,

  "g1.globo",               "g1",
  "g1.globo",               "g1 globo",

  "oglobo.globo",           "o globo",
  "extra.globo",            "extra",

  "jovempan",               "jovem pan",
  "oantagonista",           "o antagonista",
  "cartacapital",           "carta capital",
  "cnnbrasil",              "cnn brasil",
  "theintercept",           "the intercept",
  "gazetadopovo",           "gazeta do povo",
  "pleno.news",             "pleno news",
  "correiobraziliense",     "correio braziliense",
  "brasilsemmedo",          "brasil sem medo",
  "tercalivre",             "terca livre",
  "terrabrasilnoticias",    "terra brasil noticias",
  "nexojornal",             "nexo jornal",
  "poder360",               "poder 360",
  "midianinja",             "midia ninja",
  "esquerdaonline",         "esquerda online",
  "esquerdadiario",         "esquerda diario",
  "istoedinheiro",          "isto e dinheiro",
  "dailymail",              "daily mail",
  "theguardian",            "the guardian",
  "washingtonpost",         "washington post",
  "nytimes",                "new york times",
  "wsj",                    "wall street journal"
) %>%
  dplyr::mutate(
    domain = normalize_domain(domain),
    alias = alias %>%
      stringi::stri_trans_general(id = "Latin-ASCII") %>%
      stringr::str_to_lower() %>%
      stringr::str_squish()
  )


# -------------------------
# Combined alias table
# -------------------------

domain_aliases <- dplyr::bind_rows(
  domain_aliases_auto %>%
    dplyr::select(domain, alias) %>%
    dplyr::mutate(alias_source = "automatic_curated"),

  domain_aliases_manual %>%
    dplyr::select(domain, alias) %>%
    dplyr::mutate(alias_source = "manual")
) %>%
  dplyr::filter(
    domain %in% domains_for_text_detection$domain,
    alias != ""
  ) %>%
  dplyr::mutate(
    alias = alias %>%
      stringi::stri_trans_general(id = "Latin-ASCII") %>%
      stringr::str_to_lower() %>%
      stringr::str_squish(),
    alias_nchar = nchar(alias),
    alias_key = make_domain_key(alias),
    alias_source = factor(
      alias_source,
      levels = c("manual", "automatic_curated")
    )
  ) %>%
  dplyr::filter(alias_key != "") %>%

  # Keep manual versions first, but preserve different aliases.
  # Do not distinct by alias_key here.
  dplyr::arrange(domain, alias_source, alias) %>%
  dplyr::distinct(domain, alias, .keep_all = TRUE)


# -------------------------
# Remove risky short aliases
# -------------------------

safe_short_aliases <- c(
  "g1", "r7", "cnn", "bbc", "uol", "sbt", "wsj"
)

domain_aliases <- domain_aliases %>%
  dplyr::filter(
    alias_nchar >= 4 |
      alias %in% safe_short_aliases |
      alias_source == "manual"
  ) %>%
  dplyr::arrange(domain, alias_source, alias)
```

# Practice Mapping
*Steps:*
*Create matrices* in which every row is a vector representing a specific politician. Every column is a vector representing a social media activity distribution across all politicians (e.g. hashtag usage). 
We will use sparse matrix, specifically, as it is a memory-efficient way to store these grids by only remembering the cells that aren't zero.

*Apply TF-IDF (Term Frequency-Inverse Document Frequency)*: This calculation changes the politician vectors so they point toward what makes them unique.

*Normalize*: row_l1_normalize(). The L1 Norm (or Manhattan distance) of a vector is the sum of the absolute values of its coordinates. This maps all politicians onto a normalized geometric space, allowing us to compare politicians across level of activities.


## Hashtag Vectors
```{r}
# Rows = politicians' accounts.
# Columns = hashtag dimensions.
# Values initially = number of times each account used each hashtag.
# Then we apply TF-IDF to emphasize hashtags that distinguish accounts.
hashtag_long <- df_fb %>%
  dplyr::select(author, hashtags) %>%
  dplyr::filter(!is.na(hashtags), hashtags != "") %>%
  tidyr::separate_rows(hashtags, sep = ",") %>%
  dplyr::mutate(
    hashtags = hashtags %>%
      stringi::stri_trans_general(id = "Latin-ASCII") %>%
      stringr::str_to_lower() %>%
      stringr::str_trim() %>%
      stringr::str_remove_all("^#") %>%
      stringr::str_replace_all("[^a-z0-9_]", "")
  ) %>%
  dplyr::filter(
    hashtags != "",
    nchar(hashtags) > 2,
    stringr::str_detect(hashtags, "[a-z]"),
    !hashtags %in% custom_stopwords
  ) %>%
  dplyr::anti_join(
    account_self_terms,
    by = c("author", "hashtags" = "term")
  ) %>%
  dplyr::mutate(
    feature = paste0("hashtag:", hashtags)
  ) %>%
  dplyr::count(author, feature, name = "n")


# Remove extremely rare hashtags, stopwords, and account-specific self terms.
# Keep only hashtags used by at least 3 different accounts.
hashtag_long_filtered_base <- hashtag_long %>%
  dplyr::mutate(
    hashtag_clean = feature %>%
      stringr::str_remove("^hashtag:") %>%
      stringi::stri_trans_general(id = "Latin-ASCII") %>%
      stringr::str_to_lower() %>%
      stringr::str_replace_all("[^a-z0-9]", "") %>%
      stringr::str_trim()
  ) %>%
  # Remove general stopwords
  dplyr::filter(!hashtag_clean %in% custom_stopwords) %>%
  # Remove hashtags that match self-terms for the same account
  dplyr::anti_join(
    account_self_terms,
    by = c("author", "hashtag_clean" = "term")
  )

# Identify hashtags used by at least 3 different accounts after filtering
hashtag_features_to_keep <- hashtag_long_filtered_base %>%
  dplyr::distinct(author, feature) %>%
  dplyr::count(feature, name = "n_accounts") %>%
  dplyr::filter(n_accounts >= 3) %>%
  dplyr::pull(feature)

hashtag_long_filtered <- hashtag_long_filtered_base %>%
  dplyr::filter(feature %in% hashtag_features_to_keep) %>%
  dplyr::select(-hashtag_clean)

#Matrix
X_hashtag_counts <- make_sparse_practice_matrix(
  data = hashtag_long_filtered,
  account_col = author,
  feature_col = feature,
  value_col = n
)
```

##### Compute TF-IDF
```{r}
# This downweights hashtags used by many accounts and upweights more distinctive hashtags.
X_hashtag_tfidf <- apply_tfidf_sparse(
  X_hashtag_counts,
  smooth = TRUE
)

# Optional L1 normalization: expresses each account's hashtag vector
# as a relative composition of distinctive hashtag practices.
# Pairwise volume-insensitive comparison is handled later by cosine similarity.
X_hashtag_norm <- row_l1_normalize(X_hashtag_tfidf)

# Inspect
dim(X_hashtag_counts)
dim(X_hashtag_tfidf)
summary(Matrix::rowSums(X_hashtag_norm))
```

## URL Vector
```{r}
# Rows = politicians' accounts.
# Columns = shared-URL dimensions.
# Values = number of times each account shared each cleaned URL.
# We use url_clean rather than the original URL field.

# Activity threshold 
min_url_links <- 2
min_unique_urls <- 2

bad_urls <- c(
  "https://www.instagram.com/accounts/login",
  "https://instagram.com",
  "https://www.youtube.com/null",
  "https://youtube.com/null"
)

url_long <- df_fb %>%
  dplyr::select(author, url_clean) %>%
  dplyr::filter(!is.na(url_clean), url_clean != "") %>%
  dplyr::mutate(
    url_clean = url_clean %>%
      stringr::str_to_lower() %>%
      stringr::str_trim() %>%
      stringr::str_remove("/+$")
  ) %>%
  dplyr::filter(
    url_clean != "",
    !url_clean %in% bad_urls,
    !stringr::str_detect(url_clean, "youtube\\.com/null")
  ) %>%
  dplyr::mutate(
    feature = paste0("url:", url_clean)
  ) %>%
  dplyr::count(author, feature, name = "n")


# Remove rare URLs.
# URL sharing is sparse, so we keep only URLs shared by at least 2 accounts.
url_features_to_keep <- url_long %>%
  dplyr::distinct(author, feature) %>%
  dplyr::count(feature, name = "n_accounts") %>%
  dplyr::filter(n_accounts >= 2) %>%
  dplyr::pull(feature)

url_long_filtered <- url_long %>%
  dplyr::filter(feature %in% url_features_to_keep)


# Keep URL layer only for accounts with enough URL-sharing evidence.
# Accounts below this threshold are retained in the full multimodal matrix,
# but receive a zero vector for the URL layer after alignment.
url_accounts_to_keep <- url_long_filtered %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    total_url_links = sum(n),
    n_unique_urls = dplyr::n_distinct(feature),
    .groups = "drop"
  ) %>%
  dplyr::filter(
    total_url_links >= min_url_links,
    n_unique_urls >= min_unique_urls
  ) %>%
  dplyr::pull(author)

url_long_filtered <- url_long_filtered %>%
  dplyr::filter(author %in% url_accounts_to_keep)


X_url <- make_sparse_practice_matrix(
  data = url_long_filtered,
  account_col = author,
  feature_col = feature,
  value_col = n
)

#Normalize
X_url_norm <- row_l1_normalize(X_url)

dim(X_url_norm)
summary(Matrix::rowSums(X_url_norm))
```

## Text Vector

```{r}
# library(reticulate)
# library(spacyr)
# Install spaCy into a dedicated conda environment
# conda_create("spacyr_pt", python_version = "3.10")
# conda_install(
#   envname = "spacyr_pt",
#   packages = "spacy",
#   pip = TRUE
# )
# 
# # Install the Portuguese spaCy model
# reticulate::conda_run2(
#   envname = "spacyr_pt",
#   cmd = "python",
#   args = c("-m", "spacy", "download", "pt_core_news_lg")
# )
```

```{r}
# Force R/spacyr to use the correct Python
py_spacyr <- "C:/Users/andre/AppData/Local/r-miniconda/envs/spacyr_pt/python.exe"

Sys.setenv(RETICULATE_PYTHON = py_spacyr)

library(reticulate)
library(spacyr)

reticulate::use_python(py_spacyr, required = TRUE)

# Inspect
  # system2(
  #   command = py_spacyr,
  #   args = c(
  #     "-c",
  #     shQuote(
  #     "import sys, spacy; print('Python:', sys.executable); print('spaCy:',              spacy.__version__); nlp = spacy.load('pt_core_news_lg'); print('Model              loaded:', nlp.meta['name'])"))
  #   )

# Initialize spaCy through spacyr using the Python executable
spacyr::spacy_initialize(
  model = "pt_core_news_lg",
  python_executable = py_spacyr
)

# Test
# test_parse <- spacyr::spacy_parse(
#   "o deputado apresentou um projeto importante",
#   lemma = TRUE,
#   pos = TRUE
# )
# 
# test_parse
```


```{r}
# Next, we: 
# - remove URL / hashtag / mention residues;
# - lemmatize the text;
# - keep only nouns, adjectives, and verbs;
# - remove party, geographic, and generic stopwords;
# Ultimately, we want to have rows = politicians' accounts;columns = TF-IDF textual practice dimensions.

# -------------------------
# Prepare post-level texts
# -------------------------
text_posts_for_spacy <- df_fb %>%
  dplyr::filter(!is.na(text_combined), text_combined != "") %>%
  dplyr::mutate(
    row_id = dplyr::row_number(),
    # Remove platform URL residues
    text_for_vector = text_combined %>%
      stringr::str_replace_all("\\bhttp\\S+\\b", " ") %>%
      stringr::str_replace_all("\\bwww\\S+\\b", " ") %>%
      stringr::str_replace_all("\\bfacebook\\S+\\b", " ") %>%
      stringr::str_replace_all("\\binstagram\\S+\\b", " ") %>%
      stringr::str_replace_all("\\btwitter\\S+\\b", " ") %>%
      stringr::str_replace_all("\\byoutube\\S+\\b", " ") %>%
      stringr::str_squish()
  ) %>%
  dplyr::filter(text_for_vector != "") %>%
  dplyr::select(row_id, author, hashtags, text_for_vector)

dplyr::glimpse(text_posts_for_spacy)
```
```{r}
# -------------------------
# Post-specific hashtag terms
# -------------------------
# Used to remove from the text vector only terms that were actually hashtags in that particular post.
post_hashtag_terms <- text_posts_for_spacy %>%
  dplyr::filter(
    !is.na(hashtags),
    hashtags != ""
  ) %>%
  dplyr::select(row_id, hashtags) %>%
  tidyr::separate_rows(hashtags, sep = ",") %>%
  dplyr::transmute(
    row_id,
    token_key = hashtags %>%
      stringi::stri_trans_general(id = "Latin-ASCII") %>%
      stringr::str_to_lower() %>%
      stringr::str_trim() %>%
      stringr::str_remove_all("^#") %>%
      stringr::str_replace_all("[^a-z0-9]", "")
  ) %>%
  dplyr::filter(token_key != "") %>%
  dplyr::distinct()

# drop hashtags from the large text object
text_posts_for_spacy <- text_posts_for_spacy %>%
  dplyr::select(-hashtags)
```


```{r}
# Parse post-level texts in batches
dir.create("_processed_data/spacy_batches", recursive = TRUE, showWarnings = FALSE)

batch_size <- 5000

text_posts_for_spacy <- text_posts_for_spacy %>%
  dplyr::mutate(
    batch_id = ceiling(dplyr::row_number() / batch_size)
  )

batch_ids <- sort(unique(text_posts_for_spacy$batch_id))

length(batch_ids)

# -------------------------
# Batch parsing with checkpoints
# -------------------------

for (b in batch_ids) {
  
  batch_file <- file.path(
    "_processed_data/spacy_batches",
    paste0("parsed_spacy_batch_", stringr::str_pad(b, width = 5, pad = "0"), ".rds")
  )
  
  if (file.exists(batch_file)) {
    message("Skipping batch ", b, " because it already exists.")
    next
  }
  
  message("Parsing batch ", b, " of ", length(batch_ids))
  
  batch_data <- text_posts_for_spacy %>%
    dplyr::filter(batch_id == b)
  
  parsed_batch <- spacyr::spacy_parse(
    batch_data$text_for_vector,
    lemma = TRUE,
    pos = TRUE,
    entity = FALSE,
    dependency = FALSE
  )
  
  # spacyr creates doc_id values like text1, text2, etc.
  # We map those back to the original post-level row_id and author.
  parsed_batch <- parsed_batch %>%
    dplyr::mutate(
      doc_id_numeric = as.integer(stringr::str_remove(doc_id, "text")),
      row_id = batch_data$row_id[doc_id_numeric],
      author = batch_data$author[doc_id_numeric],
      batch_id = b
    )
  
  readr::write_rds(parsed_batch, batch_file)
  
  rm(parsed_batch, batch_data)
  gc()
}
```

```{r}
#Load parsed batches & Remove stopwords
parsed_files <- list.files(
  "../_processed_data/spacy_batches",
  pattern = "^parsed_spacy_batch_.*\\.rds$",
  full.names = TRUE
)

parsed_text <- purrr::map_dfr(
  parsed_files,
  readr::read_rds
)

dplyr::glimpse(parsed_text)


# -------------------------
# Filter tokens and aggregate by account
# -------------------------
tokens_text_lemma <- parsed_text %>%
  # Keep substantive POS categories
  dplyr::filter(pos %in% c("NOUN", "ADJ", "VERB", "PROPN")) %>%
  # Create comparable surface-token and lemma forms.
  # Input text is already lowercase and ASCII-normalized.
  dplyr::mutate(token_key = stringr::str_replace_all(
      token, "[^a-z0-9]", ""),
    lemma = stringr::str_replace_all(
      lemma,"[^a-z0-9]","")
  ) %>%
  
  dplyr::filter(token_key != "", lemma != "",
                nchar(lemma) > 3, nchar(lemma) <= 25,
    # Require textual features to begin with a letter
    stringr::str_detect(lemma, "^[a-z]"),
    # Apply general stopwords to both the original token and the spaCy lemma.
    !token_key %in% custom_stopwords,
    !lemma %in% custom_stopwords,
    # Same for domain terms
    !token_key %in% domain_lookup$domain_key,
    !lemma %in% domain_lookup$domain_key,
    # Basic malformed-token filters
    !stringr::str_detect(lemma, "(.)\\1{2,}"),
    !stringr::str_detect(
      lemma, "^[bcdfghjklmnpqrstvwxyz]+$"),
    stringr::str_detect(lemma, "[aeiou]")
    ) %>%
  
  # Remove terms that were used as hashtags in the post.
  # Matching occurs against the ORIGINAL spaCy token,
  dplyr::anti_join(post_hashtag_terms, by = c("row_id", "token_key")) %>%
  
  # Remove self-references using the original surface form.
  # This catches cases where spaCy changes the lemma.
  dplyr::anti_join(account_self_terms, by = c("author", "token_key" = "term")
                   ) %>%
  
  # Keep lemma-level matching as safeguard.
  dplyr::anti_join(account_self_terms, by = c("author", "lemma" = "term")
                   ) %>%
  
  # Aggregate after exclusions
  dplyr::count(author, lemma, name = "n")

tokens_text_lemma %>%
  dplyr::group_by(lemma) %>%
  dplyr::summarise(
    total_n = sum(n),
    n_accounts = dplyr::n_distinct(author),
    .groups = "drop"
  ) %>%
  dplyr::arrange(desc(total_n)) %>%
  dplyr::slice_head(n = 100)
```

[*Matrix*] The data are still in long format: one row per author–lemma combination. The next steps convert the dataset into a wide sparse matrix. 
```{r}
# Create account-by-text matrix
X_text_counts <- make_sparse_practice_matrix(
  data = tokens_text_lemma %>%
    #add the prefix "text:" to every textual feature:
    dplyr::mutate(feature = paste0("text:", lemma)), 
  account_col = author,
  feature_col = feature,
  value_col = n
)
#Inspect
dim(X_text_counts)

# -------------------------
# Trim textual features
# -------------------------
term_docfreq <- Matrix::colSums(X_text_counts > 0)
n_accounts_text <- nrow(X_text_counts)

terms_to_keep <- names(term_docfreq)[
  term_docfreq >= 3 &
    term_docfreq <= 0.90 * n_accounts_text
]

X_text_counts_trimmed <- X_text_counts[, terms_to_keep, drop = FALSE]
```

##### Compute TF-IDF
Finally, we transform the raw count matrix into a TF-IDF-weighted matrix, thereby reducing the influence of very common words and increasing the influence of more distinctive words.

```{r}
X_text_tfidf <- apply_tfidf_sparse(
  X_text_counts_trimmed,
  smooth = TRUE
)

X_text_norm <- row_l1_normalize(X_text_tfidf)

dim(X_text_norm)
summary(Matrix::rowSums(X_text_norm))
```

## Domain Vector
```{r}
# Rows = politicians' accounts.
# Columns = linked-domain dimensions.
# Values initially = number of times each account shared or mentioned each domain.
# Apply TF-IDF to emphasize domains that distinguish accounts.

# -------------------------
# Domains from linked URLs / df_fb$domain
# -------------------------

domain_long_links <- df_fb %>%
  dplyr::select(author, domain) %>%
  dplyr::filter(!is.na(domain), domain != "") %>%
  dplyr::mutate(
    domain = normalize_domain(domain)
  ) %>%
  dplyr::filter(domain != "") %>%
  dplyr::count(author, domain, name = "n")


# -------------------------
# Domains mentioned in text
# -------------------------
# These are media/domain aliases that appear in text_for_vector.
# This is done before tokenization, so multi-word names such as
# "jovem pan", "o antagonista", "carta capital", and "cnn brasil"
# can be detected.
# -------------------------

# Prepare one regex pattern from the alias table.
# Longer aliases come first to reduce partial-match problems.
regex_escape <- function(x) {
  gsub(
    pattern = "([.\\^$|()\\[\\]{}*+?\\\\])",
    replacement = "\\\\\\1",
    x = x,
    perl = TRUE
  )
}

domain_alias_patterns <- domain_aliases %>%
  dplyr::mutate(
    alias_pattern = regex_escape(alias),
    alias_pattern = stringr::str_replace_all(
      alias_pattern,
      "\\s+",
      "\\\\s+"
    ),
    alias_pattern = paste0("\\b", alias_pattern, "\\b")
  ) %>%
  dplyr::arrange(dplyr::desc(nchar(alias)), alias)

domain_regex <- paste(domain_alias_patterns$alias_pattern, collapse = "|")


# Create a named lookup from matched alias_key to canonical domain.
# If the same alias maps to more than one domain, keep the first and inspect below.
alias_to_domain <- domain_alias_patterns %>%
  dplyr::select(alias_key, domain, alias) %>%
  dplyr::distinct(alias_key, .keep_all = TRUE)


# Inspection: aliases that point to multiple domains
ambiguous_aliases <- domain_alias_patterns %>%
  dplyr::group_by(alias_key, alias) %>%
  dplyr::summarise(
    n_domains = dplyr::n_distinct(domain),
    domains = paste(sort(unique(domain)), collapse = "; "),
    .groups = "drop"
  ) %>%
  dplyr::filter(n_domains > 1)

ambiguous_aliases


# Detect textual media/domain mentions.
text_domains_long <- text_posts_for_spacy %>%
  dplyr::mutate(
    text_for_domain_detection = text_for_vector %>%
      stringi::stri_trans_general(id = "Latin-ASCII") %>%
      stringr::str_to_lower() %>%
      stringr::str_squish(),

    matched_aliases = stringr::str_extract_all(
      text_for_domain_detection,
      stringr::regex(domain_regex, ignore_case = TRUE)
    )
  ) %>%
  dplyr::select(author, matched_aliases) %>%
  tidyr::unnest_longer(matched_aliases, values_to = "matched_alias") %>%
  dplyr::filter(!is.na(matched_alias), matched_alias != "") %>%
  dplyr::mutate(
    matched_alias = matched_alias %>%
      stringi::stri_trans_general(id = "Latin-ASCII") %>%
      stringr::str_to_lower() %>%
      stringr::str_squish(),
    alias_key = make_domain_key(matched_alias)
  ) %>%
  dplyr::left_join(
    alias_to_domain,
    by = "alias_key"
  ) %>%
  dplyr::filter(!is.na(domain), domain != "") %>%
  dplyr::count(author, domain, name = "n")


# -------------------------
# Inspect text-domain matches
# -------------------------
text_domains_long %>%
  dplyr::arrange(dplyr::desc(n)) %>%
  print(n = 100)

text_domains_long %>%
  dplyr::summarise(
    n_authors = dplyr::n_distinct(author),
    n_domains = dplyr::n_distinct(domain),
    total_text_domain_mentions = sum(n, na.rm = TRUE)
  )


# -------------------------
# Unified domain vector
# -------------------------
domain_long <- dplyr::bind_rows(
  domain_long_links,
  text_domains_long) %>%
  dplyr::group_by(author, domain) %>%
  dplyr::summarise(n = sum(n, na.rm = TRUE), .groups = "drop") %>%
  dplyr::mutate(feature = paste0("domain:", domain)) %>%
  dplyr::select(author, feature, n)


# -------------------------
# Activity threshold
# -------------------------
min_domain_links <- 3
min_unique_domains <- 5

domain_accounts_to_keep <- domain_long %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    total_domain_links = sum(n, na.rm = TRUE),
    n_unique_domains = dplyr::n_distinct(feature),
    .groups = "drop"
  ) %>%
  dplyr::filter(
    total_domain_links >= min_domain_links,
    n_unique_domains >= min_unique_domains
  ) %>%
  dplyr::pull(author)

domain_long_filtered <- domain_long %>%
  dplyr::filter(author %in% domain_accounts_to_keep)

rm(domain_accounts_to_keep, min_domain_links, min_unique_domains)


# -------------------------
# Create account-by-domain count matrix
# -------------------------
X_domain_counts <- make_sparse_practice_matrix(
  data = domain_long_filtered,
  account_col = author,
  feature_col = feature,
  value_col = n
)
```

##### Compute TF-IDF
```{r}
# Apply TF-IDF.
# This downweights domains shared by many accounts and upweights more distinctive source repertoires.
X_domain_tfidf <- apply_tfidf_sparse(
  X_domain_counts,
  smooth = TRUE)

# Optional L1 normalization: expresses each account's domain vector
# as a relative composition of distinctive domain-sharing practices.
# Pairwise volume-insensitive comparison is handled later by cosine similarity.
X_domain_norm <- row_l1_normalize(X_domain_tfidf)


# -------------------------
# Inspect
# -------------------------
dim(X_domain_counts)
dim(X_domain_tfidf)

summary(Matrix::rowSums(X_domain_norm))

sum(Matrix::rowSums(X_domain_norm) == 0)

domain_long %>%
  dplyr::distinct(author) %>%
  dplyr::summarise(n_accounts_with_domains = dplyr::n())

df_fb %>%
  dplyr::distinct(author) %>%
  dplyr::summarise(n_total_accounts = dplyr::n())
```


```{r}
# Exportable domain-count table by source

# Domains from linked URLs / df_fb$domain
domain_from_url <- domain_long_links %>%
  dplyr::mutate(source = "df_fb_domain_column") %>%
  dplyr::select(author, source, domain, n)

# Domains mentioned in text through alias/regex matching
domain_from_text <- text_domains_long %>%
  dplyr::mutate(source = "text_regex") %>%
  dplyr::select(author, source, domain, n)

# Combined exportable object
domain_counts_by_source <- dplyr::bind_rows(
  domain_from_url,
  domain_from_text) %>%
  dplyr::arrange(author, source, dplyr::desc(n), domain)


# -------------------------
# Inspect
# -------------------------
dplyr::glimpse(domain_counts_by_source)

domain_counts_by_source %>%
  dplyr::count(source, name = "n_author_domain_rows")

domain_counts_by_source %>%
  dplyr::group_by(source) %>%
  dplyr::summarise(
    n_authors = dplyr::n_distinct(author),
    n_domains = dplyr::n_distinct(domain),
    total_mentions = sum(n, na.rm = TRUE),
    .groups = "drop")


# Most frequent domains by source
domain_counts_by_source %>%
  dplyr::group_by(source, domain) %>%
  dplyr::summarise(
    total_mentions = sum(n, na.rm = TRUE),
    n_authors = dplyr::n_distinct(author),
    .groups = "drop"
  ) %>%
  dplyr::arrange(source, dplyr::desc(total_mentions)) %>%
  print(n = 100)
```

###Inspection
```{r}
table(domain_counts_by_source$source)
```
```{r}
wolves <- nodes_breakdown %>% 
  filter(is_wolf == 1) %>% 
  pull(author)

domain_inspection <- domain_long_filtered %>% 
  filter(feature == "domain:oantagonista", n >= 1) 

# % of wolves who referred to the domain
mean(wolves %in% domain_inspection$author) * 100

# % of all references to the domain that came from wolves
sum(domain_inspection$n[domain_inspection$author %in% wolves]) /
  sum(domain_inspection$n) * 100
```

##### Q1_2 domains
```{r}
q12_posts <- df_fb_election %>%
  dplyr::filter(Q1 == 1 | Q2 == 1) %>%
  dplyr::select(
    postID,
    author,
    timestamp,
    text_combined,
    domain,
    Q1,
    Q2
  )

dplyr::glimpse(q12_posts)

# -------------------------
# Store Q1/Q2 classification
# -------------------------
# A post classified as both Q1 and Q2 will appear once
# under each category.
q12_post_categories <- q12_posts %>%
  dplyr::select(postID, author, Q1, Q2) %>%
  tidyr::pivot_longer(
    cols = c(Q1, Q2),
    names_to = "category",
    values_to = "classified"
  ) %>%
  dplyr::filter(classified == 1) %>%
  dplyr::select(
    postID,
    author,
    category
  )


# -------------------------
# Domains from linked URLs
# -------------------------
q12_domain_links <- q12_posts %>%
  dplyr::select(postID, author, domain) %>%
  dplyr::filter(!is.na(domain), domain != "") %>%
  dplyr::mutate(domain = normalize_domain(domain)) %>%
  dplyr::filter(domain != "") %>%
  dplyr::mutate(source = "Linked URL")


# -------------------------
# Domains mentioned in text
# -------------------------
q12_text_domains <- q12_posts %>%
  dplyr::filter(!is.na(text_combined), text_combined != "") %>%
  dplyr::mutate(
    text_for_vector = text_combined %>%
      stringr::str_replace_all("\\bhttp\\S+\\b", " ") %>%
      stringr::str_replace_all("\\bwww\\S+\\b", " ") %>%
      stringr::str_replace_all("\\bfacebook\\S+\\b", " ") %>%
      stringr::str_replace_all("\\binstagram\\S+\\b", " ") %>%
      stringr::str_replace_all("\\btwitter\\S+\\b", " ") %>%
      stringr::str_replace_all("\\byoutube\\S+\\b", " ") %>%
      stringr::str_squish(),

    text_for_domain_detection = text_for_vector %>%
      stringi::stri_trans_general(id = "Latin-ASCII") %>%
      stringr::str_to_lower() %>%
      stringr::str_squish(),

    matched_aliases = stringr::str_extract_all(
      text_for_domain_detection,
      stringr::regex(domain_regex, ignore_case = TRUE))
    ) %>%
  dplyr::select(postID,author,matched_aliases) %>%
  tidyr::unnest_longer(matched_aliases, values_to = "matched_alias") %>%
  dplyr::filter(!is.na(matched_alias), matched_alias != "") %>%
  dplyr::mutate(
    matched_alias = matched_alias %>%
      stringi::stri_trans_general(id = "Latin-ASCII") %>%
      stringr::str_to_lower() %>%
      stringr::str_squish(),

    alias_key = make_domain_key(matched_alias)
  ) %>%
  dplyr::left_join(alias_to_domain, by = "alias_key") %>%
  dplyr::filter(!is.na(domain), domain != "") %>%
  dplyr::transmute(postID, author, domain, source = "Text mention")


# -------------------------
# Unified domain data
# -------------------------
q12_domains <- dplyr::bind_rows(q12_domain_links, q12_text_domains) %>%
  dplyr::left_join(q12_post_categories, by = c("postID", "author")) %>%
  dplyr::select(category, postID, author, domain, source)


# Inspect
q12_domains %>%
  dplyr::count(
    category,
    domain,
    sort = TRUE
  ) %>%
  print(n = 100)

# -------------------------
# Domain-level summary
# -------------------------
q12_domain_summary <- q12_domains %>%
  dplyr::group_by(category, domain) %>%
  dplyr::summarise(
    n_mentions = dplyr::n(),
    n_posts = dplyr::n_distinct(postID),
    n_authors = dplyr::n_distinct(author),
    n_linked = sum(source == "Linked URL"),
    n_text_mentions = sum(source == "Text mention"),
    .groups = "drop"
    ) %>%
  dplyr::arrange(
    category,
    dplyr::desc(n_posts),
    dplyr::desc(n_mentions)
  )


# Export
readr::write_csv(q12_domains,here::here("_processed_data", "q1_q2_domains.csv"))
```

```{r}
q2_domain_summary <- q12_domains %>%
  dplyr::filter(category == "Q2") %>%
  dplyr::group_by(domain) %>%
  dplyr::summarise(
    n_mentions = dplyr::n(),
    n_posts = dplyr::n_distinct(postID),
    n_authors = dplyr::n_distinct(author),
    linked = sum(source == "Linked URL"),
    textual = sum(source == "Text mention"),
    .groups = "drop"
  ) %>%
  dplyr::arrange(dplyr::desc(n_posts), dplyr::desc(n_mentions))

q2_domain_summary %>%
  dplyr::slice_head(n = 30) %>%
  print(n = 30)
```


## Metadata
```{r}
# Create account metadata for network analyses
first_non_missing <- function(x) {
  dplyr::first(x[!is.na(x)], default = NA)
}

account_metadata <- df_fb %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    page_name = first_non_missing(page_name),
    party = first_non_missing(party),
    state = first_non_missing(state),
    PEC135 = first_non_missing(PEC135),
    ideology_2021 = first_non_missing(ideology_2021),
    # Followership
    mean_page_followers = mean(page_followers, na.rm = TRUE),
    # Total activity
    total_posts = dplyr::n(),
    total_image_posts = sum(post_format == "Image", na.rm = TRUE),
    total_video_posts = sum(post_format == "Video", na.rm = TRUE),
    total_text_posts  = sum(post_format == "Text",  na.rm = TRUE),
    # Engagement
    total_engagement = sum(engagement, na.rm = TRUE),
    mean_engagement = mean(engagement, na.rm = TRUE),
    .groups = "drop"
  )

# -------------------------
# Q-post summary by account
# -------------------------
q_posts_by_author <- df_fb_election %>%
  dplyr::mutate(
    author = as.character(author),
    Q1 = as.integer(Q1),
    Q2 = as.integer(Q2),
    Q3 = as.integer(Q3),
    PEC135 = as.integer(PEC135)) %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    Q1 = sum(Q1 == 1, na.rm = TRUE),
    Q2 = sum(Q2 == 1, na.rm = TRUE),
    Q3 = sum(Q3 == 1, na.rm = TRUE),
    PEC135_election = dplyr::first(stats::na.omit(PEC135)),
    .groups = "drop") %>%
  dplyr::mutate(PEC135_election = dplyr::if_else(
      is.na(PEC135_election), 0L, PEC135_election),
    is_wolf = dplyr::case_when(
      Q2 >= 10 & PEC135_election == 1 ~ 1L,
      TRUE ~ 0L))
```

##### Export
```{r}
readr::write_rds(
  domain_counts_by_source,
  here::here("_processed_data", "domain_counts_by_source.rds"))

account_by_media_domain_counts <- dplyr::bind_rows(
  domain_long_links,
  text_domains_long) %>%
  dplyr::group_by(author, domain) %>%
  dplyr::summarise(
    n = sum(n, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  tidyr::pivot_wider(
    names_from = domain,
    values_from = n,
    values_fill = 0) %>%
  tibble::column_to_rownames("author") %>%
  as.matrix()

readr::write_rds(
  account_by_media_domain_counts,
  here::here("_processed_data", "account_by_media_domain_counts.rds"))

account_by_media_domain_counts_csv <- account_by_media_domain_counts %>%
  as.data.frame() %>%
  tibble::rownames_to_column("author")
readr::write_csv2(
  account_by_media_domain_counts_csv,
  here::here("_processed_data", "account_by_media_domain_counts.csv"))

# -------------------------------------------------------------------------
# Export Text Data
# -------------------------------------------------------------------------
# Map row IDs back to timestamps from df_fb
df_dates_mapping <- df_fb %>%
  dplyr::filter(!is.na(text_combined), text_combined != "") %>%
  dplyr::mutate(row_id = dplyr::row_number()) %>%
  dplyr::select(row_id, timestamp)

# Export a compressed, monthly-aggregated token dataframe
tokens_text_lemma_monthly <- parsed_text %>%
  dplyr::inner_join(df_dates_mapping, by = "row_id") %>%
  dplyr::filter(pos %in% c("NOUN", "ADJ", "VERB", "PROPN")) %>%
  dplyr::mutate(
    lemma = lemma %>%
      stringi::stri_trans_general(id = "Latin-ASCII") %>%
      stringr::str_to_lower() %>%
      stringr::str_replace_all("[^a-z0-9]", "") %>%
      stringr::str_trim(),
    # Drops hours/minutes/days down to the 1st of the month
    month = lubridate::floor_date(timestamp, "month")
  ) %>%
  dplyr::filter(
    lemma != "",
    nchar(lemma) > 3,
    nchar(lemma) <= 25,
    !lemma %in% custom_stopwords,
    !lemma %in% domain_lookup$domain_key,
    !stringr::str_detect(lemma, "(.)\\1{2,}"),
    !stringr::str_detect(lemma, "^[bcdfghjklmnpqrstvwxyz]+$"),
    stringr::str_detect(lemma, "[aeiou]")
  ) %>%
  dplyr::anti_join(
    account_self_terms,
    by = c("author", "lemma" = "term")
  ) %>%
  # Count occurrences per author, per month, per lemma
  dplyr::count(author, month, lemma, name = "n")

# Export the long monthly data
readr::write_rds(
  tokens_text_lemma_monthly,
  here::here("_processed_data", "practice_vectors", "tokens_text_lemma_monthly.rds"))

readr::write_rds(
  X_text_norm,
  here::here("_processed_data", "practice_vectors", "X_text_norm.rds")
)
# -------------------------
# Export other vectors
# -------------------------
readr::write_rds(
  X_hashtag_norm,
  here::here("..", "_processed_data", "practice_vectors", "X_hashtag_norm.rds")
)

readr::write_rds(
  X_domain_norm,
  here::here("..", "_processed_data", "practice_vectors", "X_domain_norm.rds")
)

readr::write_rds(
  X_url_norm,
  here::here("..", "_processed_data", "practice_vectors", "X_url_norm.rds")
)

readr::write_rds(
  account_metadata,
  here::here("..", "_processed_data", "practice_vectors", "account_metadata.rds")
)

# -------------------------
# Keep only objects needed from this point onward
# -------------------------
objects_to_keep <- c(
  # Normalized modality matrices
  "X_hashtag_norm", "X_domain_norm", "X_url_norm", "X_text_norm",
  # Metadata
  "account_metadata",
  # Helper functions
  "align_sparse_rows", "row_l2_normalize", "cosine_similarity", "get_top_features_account",
  # General objects/settings
  "output_path", "first_non_missing")

# objects_to_remove <- setdiff(ls(), objects_to_keep)
# rm(list = objects_to_remove)
```


# Multimodal Matrix
```{r}
# -------------------------
# Align all practice vectors by account
# -------------------------
# Each vector may include a slightly different set of accounts.
# We align rows so that cosine matrices are directly comparable.

all_accounts <- Reduce(
  union,
  list(
    rownames(X_hashtag_norm),
    rownames(X_domain_norm),
    # rownames(X_url_norm),
    rownames(X_text_norm)))

all_accounts <- sort(all_accounts)

X_hashtag_aligned <- align_sparse_rows(X_hashtag_norm, all_accounts)
X_domain_aligned  <- align_sparse_rows(X_domain_norm, all_accounts)
# X_url_aligned   <- align_sparse_rows(X_url_norm, all_accounts)
X_text_aligned    <- align_sparse_rows(X_text_norm, all_accounts)

# -------------------------
# Inspect aligned matrices
# -------------------------
dim(X_hashtag_aligned)
dim(X_domain_aligned)
# dim(X_url_aligned)
dim(X_text_aligned)
```
## Cosine Similarity
*Reasoning behind threshold for edges*: A low threshold (e.g. 0.10) may retain many weak similarities that are technically nonzero but substantively modest. A higher threshold focuses the analysis on accounts with stronger overlap. On the other hand, a higher threshold reduces computational burden after similarity estimation. Diagnostics, plotting, community detection, centrality measures, and exporting edge lists will all be faster if the network has fewer edges.

```{r}
# -------------------------
# Define modalities
# -------------------------
# No outset modality weights are used here.
# Each modality contributes equally to the unweighted total similarity.
modalities <- c("text", "hashtag", "domain")
n_modalities_available <- length(modalities)


# -------------------------
# Modality-specific cosine similarities
# -------------------------

S_text <- cosine_similarity(X_text_aligned)
S_hashtag <- cosine_similarity(X_hashtag_aligned)
# S_url <- cosine_similarity(X_url_aligned)
S_domain <- cosine_similarity(X_domain_aligned)

# -------------------------
# Inspect modality-specific matrices
# -------------------------
dim(S_text)
dim(S_hashtag)
# dim(S_url)
dim(S_domain)


# -------------------------
# Combined similarity matrix
# -------------------------
# similarity_total is the unweighted average of modality-specific cosine scores.
# It remains bounded between 0 and 1.
# The multimodal bonus is applied later at the edge-construction stage.

S_multimodal_practices <- (
  S_text +
    S_hashtag +
    # S_url +
    S_domain
  ) / n_modalities_available


# -------------------------
# Inspect combined matrix
# -------------------------
dim(S_multimodal_practices)
```

```{r}
# -------------------------
# Helper: convert similarity matrix to pairwise dataset
# -------------------------
# The purpose of this step is to inspect total similarity and
# modality-specific similarity for pairs of politicians.
matrix_to_pairwise <- function(mat, value_name) {
  as.data.frame(
    as.table(as.matrix(mat)),
    stringsAsFactors = FALSE
  ) %>%
    dplyr::rename(
      source = Var1,
      target = Var2,
      !!value_name := Freq
    ) %>%
    dplyr::mutate(
      source = as.character(source),
      target = as.character(target)
    ) %>%
    dplyr::filter(source < target)
}
```

```{r}
# -------------------------
# Pairwise similarities by modality
# -------------------------
similarity_values <- matrix_to_pairwise(
  S_multimodal_practices,
  "similarity_total") %>%
  dplyr::left_join(
    matrix_to_pairwise(S_text, "similarity_text"),
    by = c("source", "target")) %>%
  dplyr::left_join(
    matrix_to_pairwise(S_hashtag, "similarity_hashtag"),
    by = c("source", "target")
  ) %>%
  # dplyr::left_join(
  #   matrix_to_pairwise(S_url, "similarity_url"),
  #   by = c("source", "target")
  # ) %>%
  dplyr::left_join(
    matrix_to_pairwise(S_domain, "similarity_domain"),
    by = c("source", "target"))


# -------------------------
# Inspect
# -------------------------
dplyr::glimpse(similarity_values)
```
## Edge-construction 
```{r}
# Rules
# Minimum total similarity required to establish an edge.
similarity_threshold <- 0.15

# Minimum modality-specific similarity required for a modality
# to count as substantively active in the dyad.
# This is used only for the multimodal bonus.
modality_presence_threshold <- 0.15


# -------------------------
# Compute modality shares and multimodal bonus
# -------------------------
# We keep the edge if total similarity is high enough,
# AND increase the edge weight when similarity appears across
# multiple modalities.

similarity_values <- similarity_values %>%
  dplyr::mutate(
    # -------------------------
    # Unweighted modality contributions
    # -------------------------
    # These are diagnostic values. They are not outset weights.
    contribution_text = similarity_text,
    contribution_hashtag = similarity_hashtag,
    # contribution_url = similarity_url,
    contribution_domain = similarity_domain,

    contribution_total =
      contribution_text +
      contribution_hashtag +
      # contribution_url +
      contribution_domain,

    # -------------------------
    # Modality shares
    # -------------------------
    # These are retained for auditing.
    # They show how much of the raw similarity comes from each modality.
    # They are no longer used to exclude edges.

    text_share = dplyr::if_else(
      contribution_total > 0,
      contribution_text / contribution_total,
      0),

    hashtag_share = dplyr::if_else(
      contribution_total > 0,
      contribution_hashtag / contribution_total,
      0),

    # url_share = dplyr::if_else(
    #   contribution_total > 0,
    #   contribution_url / contribution_total,
    #   0),

    domain_share = dplyr::if_else(
      contribution_total > 0,
      contribution_domain / contribution_total,
      0),

    max_share = pmax(
      text_share,
      hashtag_share,
      # url_share,
      domain_share,
      na.rm = TRUE),


    # -------------------------
    # Active modality indicators
    # -------------------------
    # A modality is active if its modality-specific cosine similarity
    # meets or exceeds the modality-presence threshold.

    active_text = similarity_text >= modality_presence_threshold,
    active_hashtag = similarity_hashtag >= modality_presence_threshold,
    # active_url = similarity_url >= modality_presence_threshold,
    active_domain = similarity_domain >= modality_presence_threshold,

    # -------------------------
    # Number of modalities above threshold
    # -------------------------
    # This is the basis for the multimodal bonus.
    # One active modality  -> multiplier of 1
    # Two active modalities -> multiplier of 2
    # Three active modalities -> multiplier of 3

    n_modalities_above_threshold =
      as.integer(active_text) +
      as.integer(active_hashtag) +
      # as.integer(active_url) +
      as.integer(active_domain),

    # -------------------------
    # Alternative loose activity count
    # -------------------------
    # This preserves the earlier diagnostic logic.
    # It counts modalities that contribute at least 1% of the raw similarity.
    # This is useful for auditing but is not used to construct edges.

    n_active_modalities_loose =
      as.integer(text_share > 0.01) +
      as.integer(hashtag_share > 0.01) +
      # as.integer(url_share > 0.01) +
      as.integer(domain_share > 0.01),

    # -------------------------
    # Non-domain similarity
    # -------------------------
    # This recomputes similarity while excluding the domain modality.
    # It is retained only as a diagnostic variable.

    non_domain_similarity = (
      similarity_text +
        # similarity_url +
        similarity_hashtag) / 2,


    # -------------------------
    # Multimodal edge weights
    # -------------------------
    # similarity_total remains the unweighted cosine-style score.
    # weight_multimodal_bonus is the final edge weight.
    # It strengthens ties that are supported by more modalities.

    weight_base = similarity_total,

    multimodal_multiplier = dplyr::if_else(
      n_modalities_above_threshold > 0,
      n_modalities_above_threshold,
      1L),

    weight_multimodal_bonus =
      weight_base * multimodal_multiplier)
```

*_contribution* values are the weighted similarity scores from each modality; 
*_share* values indicate the proportion of the total multimodal similarity accounted for by each modality.
*non_domain_similarity* recomputes similarity while excluding the domain modality.


```{r}
# -------------------------
# Edge list
# -------------------------
# Edge eligibility:
# 1. The pair must meet the total similarity threshold.
# 2. The pair must have at least one modality above the modality threshold.
# There is no max-share exclusion.
# Single-modality ties can remain in the network, but they receive no bonus.

edges_multimodal_practices <- similarity_values %>%
  dplyr::filter(
    similarity_total >= similarity_threshold,
    n_modalities_above_threshold >= 1
  ) %>%
  dplyr::transmute(
    source,
    target,

    # Final edge weight:
    # total similarity multiplied by number of modalities above threshold.
    weight = weight_multimodal_bonus,

    # Base similarity score, bounded between 0 and 1.
    similarity_total,

    # Weight diagnostics.
    weight_base,
    multimodal_multiplier,
    weight_multimodal_bonus,

    # Modality-specific similarities.
    similarity_text,
    similarity_hashtag,
    # similarity_url,
    similarity_domain,

    # Active-modality indicators.
    active_text,
    active_hashtag,
    # active_url,
    active_domain,
    n_modalities_above_threshold,

    # Audit variables.
    text_share,
    hashtag_share,
    # url_share,
    domain_share,
    max_share,
    n_active_modalities_loose,
    non_domain_similarity) %>%
  dplyr::arrange(dplyr::desc(weight))


# -------------------------
# Inspect edge list
# -------------------------

dplyr::glimpse(edges_multimodal_practices)

edges_multimodal_practices %>%
  dplyr::slice_head(n = 30)
```
*Threshold diagnosis*
```{r}
threshold_grid <- c(
  0.05, 0.075, 0.10, 0.125, 0.15, 0.175, 0.20, 0.25, 0.30)

account_names <- rownames(S_multimodal_practices)


# -------------------------
# Diagnostic helper
# -------------------------
# For each threshold, we:
# 1. treat the threshold as the total similarity cutoff;
# 2. also use it as the modality-presence cutoff;
# 3. construct multimodality-adjusted edge weights.

get_threshold_diagnostics <- function(th, similarity_values, account_names) {

  edges_th <- similarity_values %>%
    dplyr::mutate(

      # Recompute active modalities for this threshold.
      active_text_th = similarity_text >= th,
      active_hashtag_th = similarity_hashtag >= th,
      # active_url_th = similarity_url >= th,
      active_domain_th = similarity_domain >= th,

      n_modalities_above_threshold_th =
        as.integer(active_text_th) +
        as.integer(active_hashtag_th) +
        # as.integer(active_url_th) +
        as.integer(active_domain_th),

      multimodal_multiplier_th = dplyr::if_else(
        n_modalities_above_threshold_th > 0,
        n_modalities_above_threshold_th,
        1L
      ),

      weight_th = similarity_total * multimodal_multiplier_th
    ) %>%
    dplyr::filter(
      similarity_total >= th,
      n_modalities_above_threshold_th >= 1
    ) %>%
    dplyr::transmute(
      source,
      target,
      weight = weight_th,
      similarity_total,
      n_modalities_above_threshold = n_modalities_above_threshold_th
    )

  vertices_th <- tibble::tibble(author = account_names)

  g_th <- igraph::graph_from_data_frame(
    d = edges_th,
    vertices = vertices_th,
    directed = FALSE
  )

  g_th <- igraph::simplify(
    g_th,
    remove.multiple = TRUE,
    remove.loops = TRUE,
    edge.attr.comb = list(weight = "mean", "ignore")
  )

  comp <- igraph::components(g_th)

  tibble::tibble(
    threshold = th,
    n_nodes = igraph::vcount(g_th),
    n_edges = igraph::ecount(g_th),

    # The proportion of all possible edges that are actually present.
    # Maximum possible edges = n_nodes * (n_nodes - 1) / 2.
    density = igraph::edge_density(g_th),

    n_isolates = sum(igraph::degree(g_th) == 0),

    # Set of nodes connected to one another directly or indirectly.
    n_components = comp$no,

    # Size of the largest connected part of the network.
    largest_component_size = max(comp$csize),
    largest_component_share = max(comp$csize) / igraph::vcount(g_th),

    mean_degree = mean(igraph::degree(g_th)),
    median_degree = median(igraph::degree(g_th)),
    max_degree = max(igraph::degree(g_th)),

    mean_weight = ifelse(
      igraph::ecount(g_th) > 0,
      mean(igraph::E(g_th)$weight),
      NA_real_
    ),

    median_weight = ifelse(
      igraph::ecount(g_th) > 0,
      median(igraph::E(g_th)$weight),
      NA_real_
    ),

    mean_modalities_above_threshold = ifelse(
      nrow(edges_th) > 0,
      mean(edges_th$n_modalities_above_threshold),
      NA_real_
    ),

    median_modalities_above_threshold = ifelse(
      nrow(edges_th) > 0,
      median(edges_th$n_modalities_above_threshold),
      NA_real_
    )
  )
}


threshold_diagnostics <- purrr::map_dfr(
  threshold_grid,
  get_threshold_diagnostics,
  similarity_values = similarity_values,
  account_names = account_names
)

threshold_diagnostics
```
*Summary*: The threshold was selected by inspecting how alternative cutoffs affected density, isolates, and the size of the largest connected component. Very low thresholds retained a large share of possible ties, producing dense networks in which weak similarities may obscure meaningful differences. Very high thresholds produced substantial fragmentation, excluding many politicians from the main relational structure. A threshold of 0.15 offered a balance between selectivity and inclusion: it reduced density to 0.12 while retaining 438 of 485 politicians in the largest component.


#### Inspection
```{r}
# -------------------------
# Accounts to inspect
# -------------------------
accounts_to_check <- c(
  "carlosjordyoficial",
  "biakicisoficial",
  "bolsonaro.enb",
  "depheliolopes",
  "tabataamaralSP")


# -------------------------
# Helper: top shared features explaining cosine similarity
# -------------------------
# This helper identifies which shared features contribute most to a dyad's
# modality-specific cosine similarity.

get_top_shared_features <- function(X, source, target, n = 10, prefix_to_remove = NULL) {
  
  if (!source %in% rownames(X) | !target %in% rownames(X)) {
    return(NA_character_)
  }
  
  x_source <- X[source, , drop = FALSE]
  x_target <- X[target, , drop = FALSE]
  
  norm_source <- sqrt(sum(x_source^2))
  norm_target <- sqrt(sum(x_target^2))
  
  if (norm_source == 0 | norm_target == 0) {
    return(NA_character_)
  }
  
  # L2-normalize rows so that feature contributions correspond
  # to their contribution to cosine similarity.
  x_source_norm <- x_source / norm_source
  x_target_norm <- x_target / norm_target
  
  # Element-wise product gives each feature's contribution
  # to the cosine similarity between the two accounts.
  feature_contrib <- as.numeric(x_source_norm * x_target_norm)
  
  if (all(feature_contrib == 0)) {
    return(NA_character_)
  }
  
  names(feature_contrib) <- colnames(X)
  
  top_features <- feature_contrib[feature_contrib > 0] %>%
    sort(decreasing = TRUE) %>%
    head(n)
  
  feature_names <- names(top_features)
  
  if (!is.null(prefix_to_remove)) {
    feature_names <- stringr::str_remove(feature_names, prefix_to_remove)
  }
  
  paste0(
    feature_names,
    " (",
    round(as.numeric(top_features), 4),
    ")"
  ) %>%
    paste(collapse = "; ")
}


# -------------------------
# Inspect selected dyads
# -------------------------
# Edge is established if:
# 1. total similarity meets the edge threshold;
# 2. at least one modality-specific similarity meets the modality threshold.

edges_accounts_to_check <- similarity_values %>%
  dplyr::filter(
    source %in% accounts_to_check,
    target %in% accounts_to_check
  ) %>%
  dplyr::mutate(
    pass_similarity_threshold =
      similarity_total >= similarity_threshold,
    
    pass_modality_presence =
      n_modalities_above_threshold >= 1,
    
    edge_established =
      pass_similarity_threshold & pass_modality_presence,
    
    edge_weight_if_established = dplyr::if_else(
      edge_established,
      weight_multimodal_bonus,
      NA_real_
    ),
    
    inferred_reason = dplyr::case_when(
      !pass_similarity_threshold ~ "Fails total similarity threshold",
      !pass_modality_presence ~ "Fails modality-presence threshold",
      TRUE ~ "Passes revised edge rules"
    )
  ) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(
    top_terms = get_top_shared_features(
      X = X_text_aligned,
      source = source,
      target = target,
      n = 15,
      prefix_to_remove = "^text:"
    ),
    
    top_hashtags = get_top_shared_features(
      X = X_hashtag_aligned,
      source = source,
      target = target,
      n = 15,
      prefix_to_remove = "^hashtag:"
    ),
    
    # top_urls = get_top_shared_features(
    #   X = X_url_aligned,
    #   source = source,
    #   target = target,
    #   n = 10,
    #   prefix_to_remove = "^url:"
    # ),
    
    top_domains = get_top_shared_features(
      X = X_domain_aligned,
      source = source,
      target = target,
      n = 15,
      prefix_to_remove = "^domain:"
    )
  ) %>%
  dplyr::ungroup() %>%
  dplyr::select(
    source,
    target,
    edge_established,
    inferred_reason,
    
    similarity_total,
    weight_base,
    multimodal_multiplier,
    weight_multimodal_bonus,
    edge_weight_if_established,
    
    similarity_text,
    similarity_hashtag,
    # similarity_url,
    similarity_domain,
    
    active_text,
    active_hashtag,
    # active_url,
    active_domain,
    n_modalities_above_threshold,
    n_active_modalities_loose,
    
    pass_similarity_threshold,
    pass_modality_presence,
    
    max_share,
    text_share,
    hashtag_share,
    # url_share,
    domain_share,
    non_domain_similarity,
    
    top_terms,
    top_hashtags,
    # top_urls,
    top_domains
  ) %>%
  dplyr::arrange(
    dplyr::desc(edge_established),
    dplyr::desc(weight_multimodal_bonus)
  )

edges_accounts_to_check
```

```{r}
# -------------------------
# Summarize why inspected dyads did or did not receive edges
# -------------------------
edges_accounts_to_check %>%
  dplyr::select(
    source,
    target,
    edge_established,
    inferred_reason,
    similarity_total,
    weight_multimodal_bonus,
    similarity_text,
    similarity_hashtag,
    similarity_domain,
    active_text,
    active_hashtag,
    active_domain,
    n_modalities_above_threshold,
    multimodal_multiplier,
    max_share,
    text_share,
    hashtag_share,
    domain_share
  )
```

```{r}
## Inspect one account across modalities
account_to_inspect <- "carlosjordyoficial"

top_text <- get_top_features_account(
  mat = X_text_aligned,
  account = account_to_inspect,
  n = 20) %>%
  dplyr::mutate(modality = "text")

top_domain <- get_top_features_account(
  mat = X_domain_aligned,
  account = account_to_inspect,
  n = 20) %>%
  dplyr::mutate(modality = "domain")

# top_url <- get_top_features_account(
#   mat = X_url_aligned,
#   account = account_to_inspect,
#   n = 20) %>%
#   dplyr::mutate(modality = "url")

top_hashtag <- get_top_features_account(
  mat = X_hashtag_aligned,
  account = account_to_inspect,
  n = 20) %>%
  dplyr::mutate(modality = "hashtag")

top_features_account <- dplyr::bind_rows(
  top_text,
  top_domain,
  # top_url,
  top_hashtag
) %>%
  dplyr::select(modality, account, feature_clean, value, feature)

top_features_account
```

# Network
```{r}
edges_network <- edges_multimodal_practices %>%
  dplyr::mutate(
    weight = as.numeric(weight),
    similarity_total = as.numeric(similarity_total),
    weight_base = as.numeric(weight_base),
    multimodal_multiplier = as.numeric(multimodal_multiplier),
    weight_multimodal_bonus = as.numeric(weight_multimodal_bonus),
    similarity_text = as.numeric(similarity_text),
    similarity_hashtag = as.numeric(similarity_hashtag),
    # similarity_url = as.numeric(similarity_url),
    similarity_domain = as.numeric(similarity_domain),
    n_modalities_above_threshold = as.integer(n_modalities_above_threshold),
    n_active_modalities_loose = as.integer(n_active_modalities_loose)
  )


# -------------------------
# Vertices
# -------------------------
vertices_multimodal <- tibble::tibble(
  author = rownames(S_multimodal_practices)
) %>%
  dplyr::left_join(
    account_metadata,
    by = "author"
  ) %>%
  dplyr::left_join(
    q_posts_by_author %>%
      dplyr::select(author, Q1, Q2, Q3, is_wolf),
    by = "author"
  ) %>%
  dplyr::mutate(
    page_name = dplyr::if_else(
      is.na(page_name) | page_name == "",
      author,
      page_name
    ),
    party = dplyr::if_else(
      is.na(party) | party == "",
      "NotAvailable",
      party
    ),
    state = dplyr::if_else(
      is.na(state) | state == "",
      "NotAvailable",
      state
    ),
    PEC135 = dplyr::if_else(is.na(PEC135), 0L, as.integer(PEC135)),
    ideology_2021 = as.numeric(ideology_2021),
    mean_page_followers = tidyr::replace_na(
      as.numeric(mean_page_followers),
      0
    ),
    total_posts = tidyr::replace_na(as.integer(total_posts), 0L),
    total_image_posts = tidyr::replace_na(as.integer(total_image_posts), 0L),
    total_video_posts = tidyr::replace_na(as.integer(total_video_posts), 0L),
    total_text_posts = tidyr::replace_na(as.integer(total_text_posts), 0L),
    total_engagement = tidyr::replace_na(as.numeric(total_engagement), 0),
    mean_engagement = dplyr::if_else(
      is.na(mean_engagement) | is.nan(mean_engagement),
      0,
      as.numeric(mean_engagement)
    ),
    Q1 = tidyr::replace_na(as.integer(Q1), 0L),
    Q2 = tidyr::replace_na(as.integer(Q2), 0L),
    Q3 = tidyr::replace_na(as.integer(Q3), 0L),
    is_wolf = tidyr::replace_na(as.integer(is_wolf), 0L)
  )


# -------------------------
# Weighted graph
# -------------------------
# The graph weight is now the multimodality-adjusted tie strength:
# weight = similarity_total * n_modalities_above_threshold.
#
# similarity_total remains available as the raw unweighted multimodal
# cosine-style score.

g_multimodal_practices <- igraph::graph_from_data_frame(
  d = edges_network,
  vertices = vertices_multimodal,
  directed = FALSE
)

g_multimodal_practices <- igraph::simplify(
  g_multimodal_practices,
  remove.multiple = TRUE,
  remove.loops = TRUE,
  edge.attr.comb = list(
    weight = "mean",
    similarity_total = "mean",
    weight_base = "mean",
    multimodal_multiplier = "mean",
    weight_multimodal_bonus = "mean",
    
    similarity_text = "mean",
    similarity_hashtag = "mean",
    # similarity_url = "mean",
    similarity_domain = "mean",
    
    active_text = "first",
    active_hashtag = "first",
    # active_url = "first",
    active_domain = "first",
    n_modalities_above_threshold = "mean",
    n_active_modalities_loose = "mean",
    
    text_share = "mean",
    hashtag_share = "mean",
    # url_share = "mean",
    domain_share = "mean",
    max_share = "mean",
    non_domain_similarity = "mean",
    
    "ignore"
  )
)


# -------------------------
# Network summary
# -------------------------
component_summary <- igraph::components(g_multimodal_practices)

edge_weights <- igraph::E(g_multimodal_practices)$weight
edge_similarity_total <- igraph::E(g_multimodal_practices)$similarity_total
edge_multipliers <- igraph::E(g_multimodal_practices)$multimodal_multiplier

network_summary <- tibble::tibble(
  similarity_threshold = similarity_threshold,
  modality_presence_threshold = modality_presence_threshold,
  n_nodes = igraph::vcount(g_multimodal_practices),
  n_edges = igraph::ecount(g_multimodal_practices),
  density = igraph::edge_density(g_multimodal_practices),
  n_isolates = sum(igraph::degree(g_multimodal_practices) == 0),
  n_components = component_summary$no,
  largest_component_size = max(component_summary$csize),
  largest_component_share =
    max(component_summary$csize) / igraph::vcount(g_multimodal_practices),
  mean_degree = mean(igraph::degree(g_multimodal_practices)),
  median_degree = median(igraph::degree(g_multimodal_practices)),
  max_degree = max(igraph::degree(g_multimodal_practices)),
  
  # Raw similarity among retained edges.
  mean_similarity_total = ifelse(
    igraph::ecount(g_multimodal_practices) > 0,
    mean(edge_similarity_total, na.rm = TRUE),
    NA_real_
  ),
  median_similarity_total = ifelse(
    igraph::ecount(g_multimodal_practices) > 0,
    median(edge_similarity_total, na.rm = TRUE),
    NA_real_
  ),
  
  # Multimodality-adjusted edge weight.
  mean_weight = ifelse(
    igraph::ecount(g_multimodal_practices) > 0,
    mean(edge_weights, na.rm = TRUE),
    NA_real_
  ),
  median_weight = ifelse(
    igraph::ecount(g_multimodal_practices) > 0,
    median(edge_weights, na.rm = TRUE),
    NA_real_
  ),
  
  # How multimodal the retained edge set is.
  mean_multimodal_multiplier = ifelse(
    igraph::ecount(g_multimodal_practices) > 0,
    mean(edge_multipliers, na.rm = TRUE),
    NA_real_
  ),
  median_multimodal_multiplier = ifelse(
    igraph::ecount(g_multimodal_practices) > 0,
    median(edge_multipliers, na.rm = TRUE),
    NA_real_
  ),
  
  mean_strength = mean(
    igraph::strength(
      g_multimodal_practices,
      weights = edge_weights
    )
  ),
  median_strength = median(
    igraph::strength(
      g_multimodal_practices,
      weights = edge_weights
    )
  )
)

network_summary
```

```{r}
# Weighted Louvain community detection
# ============================================================

# Louvain uses the revised graph weight:
# weight = multimodality-adjusted tie strength.
# This means that communities are shaped not only by similarity_total,
# but also by whether similarity is supported across multiple modalities.

set.seed(999)

louvain_comm <- igraph::cluster_louvain(
  g_multimodal_practices,
  weights = igraph::E(g_multimodal_practices)$weight
)

igraph::V(g_multimodal_practices)$louvain_community <- as.integer(
  igraph::membership(louvain_comm)
)

igraph::V(g_multimodal_practices)$community <- as.factor(
  igraph::V(g_multimodal_practices)$louvain_community
)

igraph::V(g_multimodal_practices)$degree <- igraph::degree(
  g_multimodal_practices
)

igraph::V(g_multimodal_practices)$strength <- igraph::strength(
  g_multimodal_practices,
  weights = igraph::E(g_multimodal_practices)$weight
)

modularity_louvain <- igraph::modularity(
  g_multimodal_practices,
  membership = igraph::membership(louvain_comm),
  weights = igraph::E(g_multimodal_practices)$weight
)

modularity_louvain
```

### Nodes breakdown

```{r}
# degree = number of edges incident to each account.
# strength = sum of multimodality-adjusted edge weights incident to each account.
nodes_breakdown <- tibble::tibble(
  author = igraph::V(g_multimodal_practices)$name,
  label = igraph::V(g_multimodal_practices)$page_name,
  party = igraph::V(g_multimodal_practices)$party,
  state = igraph::V(g_multimodal_practices)$state,
  PEC135 = igraph::V(g_multimodal_practices)$PEC135,
  ideology_2021 = igraph::V(g_multimodal_practices)$ideology_2021,
  mean_page_followers = igraph::V(g_multimodal_practices)$mean_page_followers,
  louvain_community = igraph::V(g_multimodal_practices)$louvain_community,
  degree = igraph::V(g_multimodal_practices)$degree,
  strength = igraph::V(g_multimodal_practices)$strength,
  total_posts = igraph::V(g_multimodal_practices)$total_posts,
  total_image_posts = igraph::V(g_multimodal_practices)$total_image_posts,
  total_video_posts = igraph::V(g_multimodal_practices)$total_video_posts,
  total_text_posts = igraph::V(g_multimodal_practices)$total_text_posts,
  total_engagement = igraph::V(g_multimodal_practices)$total_engagement,
  mean_engagement = igraph::V(g_multimodal_practices)$mean_engagement,
  Q1 = igraph::V(g_multimodal_practices)$Q1,
  Q2 = igraph::V(g_multimodal_practices)$Q2,
  Q3 = igraph::V(g_multimodal_practices)$Q3,
  is_wolf = igraph::V(g_multimodal_practices)$is_wolf
) %>%
  dplyr::mutate(
    label = dplyr::if_else(
      is.na(label) | label == "",
      author,
      label
    ),
    party = dplyr::if_else(
      is.na(party) | party == "",
      "NotAvailable",
      party
    ),
    state = dplyr::if_else(
      is.na(state) | state == "",
      "NotAvailable",
      state
    ),
    PEC135 = dplyr::if_else(is.na(PEC135), 0L, as.integer(PEC135)),
    ideology_2021 = as.numeric(ideology_2021),
    mean_page_followers = tidyr::replace_na(
      as.numeric(mean_page_followers),
      0
    ),
    degree = tidyr::replace_na(as.numeric(degree), 0),
    strength = tidyr::replace_na(as.numeric(strength), 0),
    total_posts = tidyr::replace_na(as.integer(total_posts), 0L),
    total_image_posts = tidyr::replace_na(as.integer(total_image_posts), 0L),
    total_video_posts = tidyr::replace_na(as.integer(total_video_posts), 0L),
    total_text_posts = tidyr::replace_na(as.integer(total_text_posts), 0L),
    total_engagement = tidyr::replace_na(as.numeric(total_engagement), 0),
    mean_engagement = dplyr::if_else(
      is.na(mean_engagement) | is.nan(mean_engagement),
      0,
      as.numeric(mean_engagement)
    ),
    Q1 = tidyr::replace_na(as.integer(Q1), 0L),
    Q2 = tidyr::replace_na(as.integer(Q2), 0L),
    Q3 = tidyr::replace_na(as.integer(Q3), 0L),
    is_wolf = tidyr::replace_na(as.integer(is_wolf), 0L)
  ) %>%
  dplyr::arrange(
    louvain_community,
    dplyr::desc(strength)
  )

# Inspect
dplyr::glimpse(nodes_breakdown)
```

###Community breakdown
```{r}
# -------------------------
# Helper functions
# -------------------------
collapse_top_features <- function(x, n = 30) {
  x %>%
    stringr::str_remove("^(domain|hashtag|text):") %>%
    unique() %>%
    head(n) %>%
    paste(collapse = "; ")
}

get_top_matrix_features <- function(X, members, n = 30) {
  
  members_present <- intersect(members, rownames(X))
  
  if (length(members_present) == 0) {
    return(NA_character_)
  }
  
  feature_scores <- Matrix::colSums(
    X[members_present, , drop = FALSE]
  )
  
  if (length(feature_scores) == 0 || all(feature_scores == 0)) {
    return(NA_character_)
  }
  
  names(feature_scores) <- colnames(X)
  
  names(sort(feature_scores, decreasing = TRUE)) %>%
    collapse_top_features(n = n)
}

get_total_matrix_weight <- function(X, members) {
  
  members_present <- intersect(members, rownames(X))
  
  if (length(members_present) == 0) {
    return(0)
  }
  
  sum(X[members_present, , drop = FALSE])
}
```


```{r}
# ============================================================
# Community sizes
# ============================================================
community_sizes <- nodes_breakdown %>%
  dplyr::count(louvain_community, name = "n_accounts") %>%
  dplyr::arrange(dplyr::desc(n_accounts))

# ============================================================
# Hashtag info
# ============================================================
hashtag_usage_by_author <- hashtag_long_filtered %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    total_hashtags_used = sum(n, na.rm = TRUE),
    .groups = "drop")

# ============================================================
# Community breakdown
# ============================================================
community_breakdown <- nodes_breakdown %>%
  
  # Add raw hashtag-use counts
  dplyr::left_join(
    hashtag_usage_by_author,
    by = "author"
  ) %>%
  
  # Politicians with no hashtags should have 0, not NA
  dplyr::mutate(
    total_hashtags_used = dplyr::coalesce(total_hashtags_used, 0L)
  ) %>%
  
  dplyr::group_by(louvain_community) %>%
  
  dplyr::summarise(
    community_number = dplyr::first(louvain_community),
    
    # Community composition
    n_members = dplyr::n_distinct(author),
    members = list(author),
    n_wolves = sum(is_wolf == 1, na.rm = TRUE),
    
    # Parties represented
    parties = paste(
      sort(unique(stats::na.omit(party))),
      collapse = "; "
    ),
    
    # Ideology and audience size
    mean_ideology_score = mean(ideology_2021, na.rm = TRUE),
    mean_page_followers = mean(mean_page_followers, na.rm = TRUE),
    
    # Posting activity
    n_posts = sum(total_posts, na.rm = TRUE),
    mean_posts_per_politician = mean(total_posts, na.rm = TRUE),
    
    # Hashtag activity
    total_hashtags_used = sum(total_hashtags_used, na.rm = TRUE),
    mean_hashtags_used = mean(total_hashtags_used, na.rm = TRUE),
    
    # Wolf indicators
    Q1_posts = sum(Q1, na.rm = TRUE),
    Q2_posts = sum(Q2, na.rm = TRUE),
    Q3_posts = sum(Q3, na.rm = TRUE),
    
    # Engagement
    total_engagement = sum(total_engagement, na.rm = TRUE),
    mean_engagement = dplyr::if_else(
      n_posts > 0,
      total_engagement / n_posts,
      0
    ),
    
    .groups = "drop"
  ) %>%
  
  dplyr::rowwise() %>%
  
  dplyr::mutate(
    
    top_domains = get_top_matrix_features(
      X = X_domain_aligned,
      members = members,
      n = 20
    ),
    
    n_domains = get_total_matrix_weight(
      X = X_domain_aligned,
      members = members
    ),
    
    top_hashtags = get_top_matrix_features(
      X = X_hashtag_aligned,
      members = members,
      n = 20
    ),
    
    n_hashtags = get_total_matrix_weight(
      X = X_hashtag_aligned,
      members = members
    ),
    
    # top_urls = get_top_matrix_features(
    #   X = X_url_aligned,
    #   members = members,
    #   n = 15
    # ),
    
    # n_urls = get_total_matrix_weight(
    #   X = X_url_aligned,
    #   members = members
    # ),
    
    top_terms = get_top_matrix_features(
      X = X_text_aligned,
      members = members,
      n = 40
    )
  ) %>%
  
  dplyr::ungroup() %>%
  
  dplyr::select(
    community_number,
    n_members,
    n_wolves,
    parties,
    mean_ideology_score,
    mean_page_followers,
    n_posts,
    mean_posts_per_politician,
    total_hashtags_used,
    mean_hashtags_used,
    Q1_posts, Q2_posts, Q3_posts,
    top_domains,
    n_domains,
    top_hashtags,
    n_hashtags,
    # top_urls, # n_urls,
    top_terms,
    total_engagement,
    mean_engagement
  )

  
community_sizes
community_breakdown
```

##### Inspection
```{r}
community_3 <- nodes_breakdown %>% 
  filter(louvain_community == 3) %>% 
  pull(author)

domain_inspection <- domain_long_filtered %>% 
  filter(feature == "domain:terrabrasilnoticias", n >= 1)

# % of wolves who referred to the domain
mean(wolves %in% domain_inspection$author) * 100

# % of Community 3's references to the domain that came from wolves
domain_inspection %>%
  filter(author %in% community_3) %>%
  summarise(
    pct_referrals_from_wolves =
      sum(n[author %in% wolves]) / sum(n) * 100
  )
```
```{r}
wolf_hashtags <- hashtag_long_filtered %>% 
  filter(author %in% wolves, n >= 1) %>% 
  group_by(feature) %>% 
  summarise(
    n_references = sum(n),
    n_wolves_using = n_distinct(author),
    pct_wolves_using = n_distinct(author) / length(wolves) * 100,
    .groups = "drop"
  ) %>% 
  arrange(desc(n_references))

wolf_hashtags %>% 
  slice_head(n = 20)
```

#### Party Vs. Wolves
```{r}
# Add politician attributes to edges
edges_attributes <- edges_multimodal_practices_threshold %>%
  dplyr::left_join(
    nodes_breakdown %>%
      dplyr::select(author, party, is_wolf),
    by = c("source" = "author")
  ) %>%
  dplyr::rename(
    source_party = party,
    source_wolf = is_wolf
  ) %>%
  
  dplyr::left_join(
    nodes_breakdown %>%
      dplyr::select(author, party, is_wolf),
    by = c("target" = "author")
  ) %>%
  dplyr::rename(
    target_party = party,
    target_wolf = is_wolf
  )

# PARTY
party_similarity <- dplyr::bind_rows(
  
  # Average within each party
  edges_attributes %>%
    dplyr::filter(
      !is.na(source_party),
      !is.na(target_party),
      source_party == target_party
    ) %>%
    dplyr::group_by(group = source_party) %>%
    dplyr::summarise(
      n_edges = dplyr::n(),
      mean_similarity = mean(weight_multimodal_bonus, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    dplyr::arrange(dplyr::desc(mean_similarity)),
  
  # Average across different parties
  edges_attributes %>%
    dplyr::filter(
      !is.na(source_party),
      !is.na(target_party),
      source_party != target_party
    ) %>%
    dplyr::summarise(
      group = "Across parties",
      n_edges = dplyr::n(),
      mean_similarity = mean(weight_multimodal_bonus, na.rm = TRUE)
    ),
  
  # Average across all within-party edges
  edges_attributes %>%
    dplyr::filter(
      !is.na(source_party),
      !is.na(target_party),
      source_party == target_party
    ) %>%
    dplyr::summarise(
      group = "All parties",
      n_edges = dplyr::n(),
      mean_similarity = mean(weight_multimodal_bonus, na.rm = TRUE)
    )
)

#WOLVES
wolf_similarity <- edges_attributes %>%
  dplyr::filter(
    !is.na(source_wolf),
    !is.na(target_wolf)
  ) %>%
  dplyr::mutate(
    group = dplyr::case_when(
      source_wolf == 1 & target_wolf == 1 ~ "Wolves",
      source_wolf == 0 & target_wolf == 0 ~ "Others",
      TRUE                                ~ "Wolf–Other"
    )
  ) %>%
  dplyr::group_by(group) %>%
  dplyr::summarise(
    n_edges = dplyr::n(),
    mean_similarity = mean(weight_multimodal_bonus, na.rm = TRUE),
    .groups = "drop"
  )

wolf_similarity
party_similarity
```


#### Gephi
```{r}
# Nodes and edges exported for Gephi.
# Edge Weight is now the multimodality-adjusted tie strength:
#   Weight = similarity_total * multimodal_multiplier
# similarity_total is the raw unweighted multimodal similarity.
# multimodal_multiplier indicates how many modalities exceeded the
# modality-specific threshold.

# -------------------------
# Nodes
# -------------------------
nodes_gephi <- nodes_breakdown %>%
  dplyr::transmute(
    Id = as.character(author),
    Label = as.character(label),
    author = as.character(author),
    party = as.character(party),
    state = as.character(state),
    PEC135 = as.integer(PEC135),
    ideology_2021 = as.numeric(ideology_2021),
    mean_page_followers = as.numeric(mean_page_followers),
    louvain_community = as.integer(louvain_community),

    # Network position
    degree = as.numeric(degree),

    # Strength is based on the revised multimodality-adjusted edge weight.
    strength = as.numeric(strength),

    # Activity and engagement
    total_posts = as.integer(total_posts),
    total_image_posts = as.integer(total_image_posts),
    total_video_posts = as.integer(total_video_posts),
    total_text_posts = as.integer(total_text_posts),
    total_engagement = as.numeric(total_engagement),
    mean_engagement = as.numeric(mean_engagement),

    # Case-study variables
    Q1 = as.integer(Q1),
    Q2 = as.integer(Q2),
    Q3 = as.integer(Q3),
    is_wolf = as.integer(is_wolf)
  ) %>%
  dplyr::filter(
    !is.na(Id),
    Id != ""
  ) %>%
  dplyr::distinct(Id, .keep_all = TRUE)


# -------------------------
# Edges
# -------------------------

edges_gephi <- edges_network %>%
  dplyr::transmute(
    Source = as.character(source),
    Target = as.character(target),
    Type = "Undirected",

    # Final edge weight used in the network.
    # This is the multimodality-adjusted tie strength.
    Weight = as.numeric(weight),

    # Raw unweighted multimodal similarity.
    similarity_total = as.numeric(similarity_total),

    # Weight diagnostics.
    weight_base = as.numeric(weight_base),
    multimodal_multiplier = as.numeric(multimodal_multiplier),
    weight_multimodal_bonus = as.numeric(weight_multimodal_bonus),

    # Modality-specific cosine similarities.
    similarity_text = as.numeric(similarity_text),
    similarity_hashtag = as.numeric(similarity_hashtag),
    # similarity_url = as.numeric(similarity_url),
    similarity_domain = as.numeric(similarity_domain),

    # Whether each modality exceeded the modality-presence threshold.
    active_text = as.integer(active_text),
    active_hashtag = as.integer(active_hashtag),
    # active_url = as.integer(active_url),
    active_domain = as.integer(active_domain),

    # Number of modalities above the modality-presence threshold.
    n_modalities_above_threshold = as.integer(n_modalities_above_threshold),

    # Share diagnostics.
    # These are retained for auditing but no longer determine edge inclusion.
    share_text = as.numeric(text_share),
    share_hashtag = as.numeric(hashtag_share),
    # share_url = as.numeric(url_share),
    share_domain = as.numeric(domain_share),
    max_share = as.numeric(max_share),

    # Diagnostic similarity excluding domains.
    non_domain_similarity = as.numeric(non_domain_similarity)
  ) %>%
  dplyr::filter(
    !is.na(Source), Source != "",
    !is.na(Target), Target != "",
    !is.na(Weight)
  )
```

#### Export
```{r}
# -------------------------
# Export as TSV for Gephi
# -------------------------
readr::write_tsv(
  nodes_gephi,
  here::here("_processed_data", "gephi_nodes_multimodal_practices.tsv"),
  na = "")

readr::write_tsv(
  edges_gephi,
  here::here("_processed_data", "gephi_edges_multimodal_practices.tsv"),
  na = "")

# -------------------------
# Export other objects
# -------------------------
readr::write_rds(
  edges_multimodal_practices,
  here::here("_processed_data", "edges_multimodal_practices_threshold.rds"))

readr::write_csv(
  edges_multimodal_practices,
  here::here("_processed_data", "edges_multimodal_practices_threshold.csv"))

readr::write_csv(
  community_breakdown,
  here::here("_processed_data", "community_breakdown.csv"))

readr::write_csv(
  nodes_breakdown,
  here::here("_processed_data", "nodes_breakdown.csv"))
```
