---
title: "_3_Wolves_Analysis"
author: "André K. Rodarte"
date: "2026-05-15"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(showtext)
library(here)
library(sysfonts)
library(scales)
library(broom)
library(lubridate)
library(car)
library(patchwork)
library(ggplot2)
font_add_google("EB Garamond", "EB Garamond")
showtext_auto()
```

# Data

```{r}
# Main datasets
df_fb <- read_rds(
  here("_processed_data", "df_fb_GPT.rds"))
df_fb_election <- read_rds(
  here("_processed_data", "df_fb_election.rds"))
nodes_breakdown <- read_csv(
  here("_processed_data", "nodes_breakdown.csv"))

# Text data
tokens_text_lemma_monthly <- readr::read_rds(
  here("_processed_data", "practice_vectors", "tokens_text_lemma_monthly.rds"))
```

# Set Up

```{r}
group_colors <- c(
  "All other parliamentarians" = "grey60",
  "Wolves" = "navyblue"
)

nodes_grouped <- nodes_breakdown %>%
  dplyr::mutate(
    wolf_group = dplyr::case_when(
      is_wolf == 1 ~ "Wolves",
      is_wolf == 0 ~ "All other parliamentarians",
      TRUE ~ NA_character_
    ),
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")
    )
  ) %>%
  dplyr::filter(!is.na(wolf_group))

# Use followership already in nodes_breakdown if available.
# Otherwise, compute it from df_fb.
if ("mean_page_followers" %in% names(nodes_grouped)) {
  
  anova_df <- nodes_grouped %>%
    dplyr::mutate(
      mean_followers = as.numeric(mean_page_followers)
    )
  
} else {
  
  followers_by_author <- df_fb %>%
    dplyr::group_by(author) %>%
    dplyr::summarise(
      mean_followers = mean(page_followers, na.rm = TRUE),
      .groups = "drop"
    )
  
  anova_df <- nodes_grouped %>%
    dplyr::left_join(
      followers_by_author,
      by = "author"
    )
}

anova_df <- anova_df %>%
  dplyr::filter(!is.na(wolf_group))

# ----------------------------
# Shared theme
# ----------------------------
theme_wolves <- function() {
  ggplot2::theme_minimal(
    base_family = "EB Garamond",
    base_size = 30
  ) +
    ggplot2::theme(
      text = ggplot2::element_text(family = "EB Garamond", size = 30),
      plot.title = ggplot2::element_text(face = "bold", size = 40),
      axis.title = ggplot2::element_text(size = 32),
      axis.text = ggplot2::element_text(size = 30),
      legend.title = ggplot2::element_text(size = 30),
      legend.text = ggplot2::element_text(size = 30),
      strip.text = ggplot2::element_text(size = 32, face = "bold")
    )
}

theme_wolf_distribution <- ggplot2::theme_minimal(
  base_family = "EB Garamond",
  base_size = 30
) +
  ggplot2::theme(
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.minor = ggplot2::element_blank(),
    plot.title = ggplot2::element_text(face = "bold", size = 40),
    plot.subtitle = ggplot2::element_text(size = 30),
    plot.caption = ggplot2::element_text(size = 20, hjust = 0),
    axis.title = ggplot2::element_text(face = "bold", size = 32),
    axis.text = ggplot2::element_text(size = 30),
    legend.position = "none"
  )

# ----------------------------
# P-value format
# ----------------------------
format_p_value <- function(p) {
  dplyr::case_when(
    is.na(p) ~ NA_character_,
    p < .001 ~ "< .001",
    TRUE ~ format(round(p, 4), nsmall = 4)
  )
}

# ----------------------------
# Dynamic axis labels with group sizes
# ----------------------------
group_n <- anova_df %>%
  dplyr::count(wolf_group)

axis_labels <- setNames(
  paste0(group_n$wolf_group, "\n(n=", group_n$n, ")"),
  group_n$wolf_group
)

# ----------------------------
# Output path
# ----------------------------

output_path <- here::here("_output")
```

### ANOVA Set up
```{r}
# ANOVA diagnostics
vars_interest <- c(
  "mean_engagement",
  "mean_followers",
  "total_posts")

var_labels <- c(
  mean_engagement = "Mean engagement",
  mean_followers = "Mean followership",
  total_posts = "Number of posts")

# Group-wise summary statistics
variance_summary <- anova_df %>%
  dplyr::select(wolf_group, dplyr::all_of(vars_interest)) %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(vars_interest),
    names_to = "variable",
    values_to = "value") %>%
  dplyr::filter(
    !is.na(wolf_group),
    !is.na(value)) %>%
  dplyr::mutate(
    variable = dplyr::recode(variable, !!!as.list(var_labels))) %>%
  dplyr::group_by(variable, wolf_group) %>%
  dplyr::summarise(
    n_politicians = dplyr::n(),
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    variance = var(value, na.rm = TRUE),
    median = median(value, na.rm = TRUE),
    iqr = IQR(value, na.rm = TRUE),
    .groups = "drop") %>%
  dplyr::mutate(
    dplyr::across(
      c(mean, sd, variance, median, iqr),
      ~ round(.x, 3)))

variance_summary

# ----------------------------
# Variance diagnostics: Fligner-Killeen tests
# ----------------------------

fligner_results <- anova_df %>%
  dplyr::select(wolf_group, dplyr::all_of(vars_interest)) %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(vars_interest),
    names_to = "variable",
    values_to = "value"
  ) %>%
  dplyr::filter(
    !is.na(wolf_group),
    !is.na(value)
  ) %>%
  dplyr::group_by(variable) %>%
  dplyr::group_modify(~ {
    
    fligner <- stats::fligner.test(value ~ wolf_group, data = .x)
    
    tibble::tibble(
      fligner_statistic = unname(fligner$statistic),
      fligner_p.value = fligner$p.value
    )
  }) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    variable = dplyr::recode(variable, !!!as.list(var_labels)),
    fligner_statistic = round(fligner_statistic, 3),
    fligner_p.value = round(fligner_p.value, 4)
  )

fligner_results
```
Before conducting group comparisons, we examined whether the assumptions of ordinary ANOVA were appropriate for the account-level outcomes. Descriptive statistics indicated substantial differences in dispersion between wolves and all other parliamentarians. The variance among wolves was considerably larger for mean engagement, mean followership, and number of posts. Because the variables were highly skewed and group sizes were unequal, we assessed variance heterogeneity using the Fligner-Killeen test, which is robust to departures from normality. The tests rejected the null hypothesis of equal variances for all three outcomes: mean engagement, χ² = 101.0, p < .001; mean followership, χ² = 52.4, p < .001; and number of posts, χ² = 13.6, p = .0002. Given these unequal variances and the imbalance in group sizes, we used Welch’s ANOVA rather than ordinary ANOVA for the main group comparisons.

```{r}
# Welch ANOVA helper functions
run_welch_anova <- function(data, outcome, label) {
  
  outcome <- rlang::ensym(outcome)
  
  test_df <- data %>%
    dplyr::select(wolf_group, value = !!outcome) %>%
    dplyr::filter(
      !is.na(wolf_group),
      !is.na(value))
  
  welch <- stats::oneway.test(
    value ~ wolf_group,
    data = test_df,
    var.equal = FALSE)
  
  group_means <- test_df %>%
    dplyr::group_by(wolf_group) %>%
    dplyr::summarise(
      n = dplyr::n(),
      mean = mean(value, na.rm = TRUE),
      sd = sd(value, na.rm = TRUE),
      .groups = "drop")
  
  group_means_wide <- group_means %>%
    dplyr::select(wolf_group, mean) %>%
    tidyr::pivot_wider(
      names_from = wolf_group,
      values_from = mean)
  
  tibble::tibble(
    test = label,
    method = "Welch ANOVA",
    df_num = unname(welch$parameter[1]),
    df_den = unname(welch$parameter[2]),
    statistic = unname(welch$statistic),
    p.value = welch$p.value) %>%
    dplyr::bind_cols(group_means_wide)
}

make_welch_subtitle <- function(result) {
  
  test_row <- result %>%
    dplyr::slice(1)
  
  paste0(
    "Welch ANOVA: F(",
    round(test_row$df_num, 1), ", ",
    round(test_row$df_den, 1), ") = ",
    round(test_row$statistic, 2), ", ",
    format_p_value(test_row$p.value))
}

plot_welch_distribution <- function(
    data,
    outcome,
    title,
    y_label,
    result,
    zoom_quantile = 0.98) 
  {
  outcome <- rlang::ensym(outcome)
  plot_df <- data %>%
    dplyr::filter(
      !is.na(wolf_group),
      !is.na(!!outcome))
  
  values <- dplyr::pull(plot_df, !!outcome)
  
  y_upper <- stats::quantile(
    values,
    probs = zoom_quantile,
    na.rm = TRUE
  )
  
  if (is.na(y_upper) || y_upper <= 0) {
    y_upper <- max(values, na.rm = TRUE)
  }
  
  n_out_of_frame <- sum(values > y_upper, na.rm = TRUE)
  
  ggplot2::ggplot(
    plot_df,
    ggplot2::aes(
      x = wolf_group,
      y = !!outcome,
      color = wolf_group,
      fill = wolf_group)) +
    ggplot2::geom_jitter(
      width = 0.25,
      height = 0,
      alpha = 0.3,
      size = 1.8) +
    ggplot2::geom_boxplot(
      width = 0.4,
      alpha = 0.5,
      color = "black",
      outlier.shape = NA) +
    ggplot2::stat_summary(
      fun = mean,
      geom = "point",
      shape = 18,
      size = 5,
      color = "black",
      fill = "black") +
    ggplot2::scale_color_manual(values = group_colors) +
    ggplot2::scale_fill_manual(values = group_colors) +
    ggplot2::scale_x_discrete(labels = axis_labels) +
    ggplot2::scale_y_continuous(labels = scales::comma_format()) +
    ggplot2::coord_cartesian(
      ylim = c(0, y_upper)) +
    ggplot2::labs(
      title = title,
      subtitle = make_welch_subtitle(result),
      caption = paste0(
        "Y-axis zoomed at the ",
        zoom_quantile * 100,
        "th percentile for readability; ",
        n_out_of_frame,
        " account(s) fall above the visible range. Welch ANOVA uses the full data."
      ),
      x = NULL,
      y = y_label) +
    theme_wolf_distribution
}
```

### Dataset set up
```{r}
# PEC135 summary table
pec135_summary_table <- nodes_breakdown %>%
  dplyr::filter(!is.na(PEC135)) %>%
  dplyr::mutate(
    pec135_group = dplyr::case_when(
      PEC135 == 1 ~ "Pro PEC135",
      PEC135 == 0 ~ "Against PEC135",
      TRUE ~ NA_character_
    ),
    pec135_group = factor(
      pec135_group,
      levels = c("Against PEC135", "Pro PEC135")
    )
  ) %>%
  dplyr::filter(!is.na(pec135_group)) %>%
  dplyr::group_by(pec135_group) %>%
  dplyr::summarise(
    n_politicians = dplyr::n_distinct(author),
    n_parties = dplyr::n_distinct(party, na.rm = TRUE),

    total_Q1_posts = sum(Q1, na.rm = TRUE),
    mean_Q1_posts_per_politician = mean(Q1, na.rm = TRUE),

    total_Q2_posts = sum(Q2, na.rm = TRUE),
    mean_Q2_posts_per_politician = mean(Q2, na.rm = TRUE),

    total_posts = sum(total_posts, na.rm = TRUE),
    mean_engagement = mean(mean_engagement, na.rm = TRUE),

    .groups = "drop"
  ) %>%
  dplyr::mutate(
    dplyr::across(
      c(
        mean_Q1_posts_per_politician,
        mean_Q2_posts_per_politician,
        mean_engagement
      ),
      ~ round(.x, 2)
    )
  )

pec135_summary_table
```

```{r}
# Plot Q1 posts
p_pec135_q1_posts <- ggplot(
  pec135_summary_table,
  aes(x = pec135_group, y = mean_Q1_posts_per_politician)) +
  geom_col(width = 0.6, fill = "grey60") +
  scale_y_continuous(labels = scales::comma_format(), limits = c(0, NA)) +
  labs(title = "Average Number of Posts about the Electoral System",
    subtitle = "Comparison between politicians who voted in favor or against PEC135",
    x = NULL, y = "") +
  theme_wolves() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.5),
    axis.ticks = element_line(color = "black", linewidth = 0.5)
  )

# Plot: Q1 and Q2 posts
p_pec135_q_posts <- ggplot(
  pec135_summary_table %>%
    dplyr::select(pec135_group, mean_Q1_posts_per_politician, mean_Q2_posts_per_politician) %>%
    tidyr::pivot_longer(
      cols = c(
        mean_Q1_posts_per_politician,
        mean_Q2_posts_per_politician),
      names_to = "post_type",
      values_to = "mean_posts"
    ) %>%
    dplyr::mutate(post_type = dplyr::recode(
        post_type,
        "mean_Q1_posts_per_politician" = "Q1 posts",
        "mean_Q2_posts_per_politician" = "Q2 posts"),
      post_type = factor(
        post_type,
        levels = c("Q1 posts", "Q2 posts"))),
  aes(x = pec135_group, y = mean_posts, fill = post_type)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  scale_fill_manual(
    values = c( "Q1 posts" = "grey60", "Q2 posts" = "black")) +
  scale_y_continuous(labels = scales::comma_format(),
    limits = c(0, NA)) +
  labs(title = "Average Number of Q1 and Q2 Posts",
    x = NULL,
    y = "Average number of posts per politician",
    fill = NULL) +
  theme_wolves() +
  theme(legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.5),
    axis.ticks = element_line(color = "black", linewidth = 0.5))

#Visualize
p_pec135_q1_posts
p_pec135_q_posts
```

```{r}
ggsave(
  filename = file.path(output_path, "pec135_q1_posts.png"),
  plot = p_pec135_q1_posts,
  width = 8, height = 5, dpi = 300)

ggsave(
  filename = file.path(output_path, "pec135_q1_q2_posts.png"),
  plot = p_pec135_q_posts,
  width = 8, height = 5, dpi = 300)
```

## Temporal analysis
```{r}
# Monthly evolution: Q1 counts
p_q1_evolution <- df_fb_election %>%
  dplyr::left_join(
    nodes_grouped %>%
      dplyr::select(author, wolf_group),
    by = "author") %>%
  dplyr::filter(!is.na(wolf_group),!is.na(timestamp)) %>%
  dplyr::mutate(
    month = lubridate::floor_date(timestamp, unit = "month"),
    Q1 = dplyr::if_else(is.na(Q1), 0L, Q1)
  ) %>%
  dplyr::group_by(month, wolf_group) %>%
  dplyr::summarise(
    total_posts = dplyr::n(),
    q1_posts = sum(Q1 == 1, na.rm = TRUE),
    .groups = "drop") %>%
  ggplot(aes(x = month, y = q1_posts, color = wolf_group, group = wolf_group)) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = group_colors) +
  scale_y_continuous(
    labels = scales::comma_format(),
    limits = c(0, NA)) +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y") +
  labs(
    title = "Evolution over time of posts discussing electoral integrity",
    x = NULL, y = " ", color = NULL) +
  theme_wolves() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1),
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.5),
    axis.ticks = element_line(color = "black", linewidth = 0.5)
  )

p_q1_evolution
```
```{r}
# Monthly evolution: Q2 counts
p_q2_evolution <- df_fb_election %>%
  dplyr::left_join(nodes_grouped %>%
      dplyr::select(author, wolf_group), by = "author") %>%
  dplyr::filter(
    !is.na(wolf_group),
    !is.na(timestamp)) %>%
  dplyr::mutate(
    month = lubridate::floor_date(timestamp, unit = "month"),
    Q2 = dplyr::if_else(is.na(Q2), 0L, Q2)) %>%
  dplyr::group_by(month, wolf_group) %>%
  dplyr::summarise(
    total_posts = dplyr::n(),
    q2_posts = sum(Q2 == 1, na.rm = TRUE),
    .groups = "drop") %>%
  ggplot(aes(x = month, y = q2_posts, color = wolf_group, group = wolf_group)) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = group_colors) +
  scale_y_continuous(
    labels = scales::comma_format(),
    limits = c(0, NA)
  ) +
  scale_x_date(date_breaks = "3 months",
    date_labels = "%b %Y") +
  labs(title = "Evolution over time of posts with election integrity propaganda",
    x = NULL,
    y = "Monthly number of Q2 posts",
    color = NULL) +
  theme_wolves() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.5),
    axis.ticks = element_line(color = "black", linewidth = 0.5)
  )

p_q2_evolution
```
```{r}
# Monthly evolution: Q1 and Q2 counts among Wolves only
p_q_wolves_only <- df_fb_election %>%
  dplyr::left_join(
    nodes_grouped %>%
      dplyr::select(author, wolf_group),
    by = "author"
  ) %>%
  dplyr::filter(
    wolf_group == "Wolves",
    !is.na(timestamp)
  ) %>%
  dplyr::mutate(
    month = lubridate::floor_date(timestamp, unit = "month"),
    Q1 = dplyr::if_else(is.na(Q1), 0L, Q1),
    Q2 = dplyr::if_else(is.na(Q2), 0L, Q2)
  ) %>%
  dplyr::group_by(month) %>%
  dplyr::summarise(
    total_posts = dplyr::n(),
    Q1 = sum(Q1 == 1, na.rm = TRUE),
    Q2 = sum(Q2 == 1, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  tidyr::pivot_longer(
    cols = c(Q1, Q2),
    names_to = "question",
    values_to = "n_posts"
  ) %>%
  dplyr::mutate(
    question = factor(
      question,
      levels = c("Q1", "Q2"),
      labels = c("Q1 posts", "Q2 posts")
    )
  ) %>%
  ggplot(aes(x = month, y = n_posts, color = question, group = question)) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = c(
      "Q1 posts" = "lightblue",
      "Q2 posts" = "darkblue")) +
  scale_y_continuous(
    labels = scales::comma_format(),
    limits = c(0, NA)) +
  scale_x_date(
    date_breaks = "3 months",
    date_labels = "%b %Y") +
  labs(title = "Evolution of Q1 and Q2 Posts Among Wolves",
    x = NULL,
    y = "Monthly number of posts",
    color = NULL) +
  theme_wolves() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.5),
    axis.ticks = element_line(color = "black", linewidth = 0.5)
  )

p_q_wolves_only
```
```{r}
ggsave(
  filename = file.path(output_path, "p_q1_evolution.png"),
  plot = p_q1_evolution,
  width = 8, height = 5, dpi = 300)

ggsave(
  filename = file.path(output_path, "p_q2_evolution.png"),
  plot = p_q2_evolution,
  width = 8, height = 5, dpi = 300)

ggsave(
  filename = file.path(output_path, "p_q_wolves_only.png"),
  plot = p_q_wolves_only,
  width = 8, height = 5, dpi = 300)
```


# Descriptive Analysis
## Engagement
```{r}
welch_engagement <- run_welch_anova(
  data = anova_df,
  outcome = mean_engagement,
  label = "Mean engagement"
)

p_mean_engagement <- plot_welch_distribution(
  data = anova_df,
  outcome = mean_engagement,
  title = "Mean Engagement by Group",
  y_label = "Mean engagement per account",
  result = welch_engagement
)

welch_engagement
p_mean_engagement
```
## Followership
```{r}
welch_followers <- run_welch_anova(
  data = anova_df,
  outcome = mean_followers,
  label = "Mean followership"
)

p_mean_followers <- plot_welch_distribution(
  data = anova_df,
  outcome = mean_followers,
  title = "Mean Followership by Group",
  y_label = "Mean followers per account",
  result = welch_followers
)

welch_followers
p_mean_followers
```
## Post activity
```{r}
welch_posts <- run_welch_anova(
  data = anova_df,
  outcome = total_posts,
  label = "Number of posts"
)

p_mean_posts <- plot_welch_distribution(
  data = anova_df,
  outcome = total_posts,
  title = "Post Activity by Group",
  y_label = "Number of posts per account",
  result = welch_posts
)

welch_posts
p_mean_posts
```
## Post Format
```{r}
post_format_author <- nodes_grouped %>%
  dplyr::select(
    author,
    wolf_group,
    total_posts,
    total_image_posts,
    total_video_posts,
    total_text_posts
  ) %>%
  tidyr::pivot_longer(
    cols = c(
      total_image_posts,
      total_video_posts,
      total_text_posts
    ),
    names_to = "post_format",
    values_to = "n_format"
  ) %>%
  dplyr::mutate(
    post_format = dplyr::recode(
      post_format,
      total_image_posts = "Image",
      total_video_posts = "Video",
      total_text_posts = "Text"
    ),
    n_format = tidyr::replace_na(as.integer(n_format), 0L),
    total_posts = tidyr::replace_na(as.integer(total_posts), 0L),
    prop_format = dplyr::if_else(
      total_posts > 0,
      n_format / total_posts,
      NA_real_
    ))

# ----------------------------
# Welch ANOVA for post format shares
# ----------------------------
welch_format_results <- post_format_author %>%
  dplyr::filter(!is.na(prop_format)) %>%
  dplyr::group_by(post_format) %>%
  dplyr::group_modify(~ {
    welch <- stats::oneway.test(
      prop_format ~ wolf_group,
      data = .x,
      var.equal = FALSE)
    
    group_means <- .x %>%
      dplyr::group_by(wolf_group) %>%
      dplyr::summarise(
        mean_share = 100 * mean(prop_format, na.rm = TRUE),
        .groups = "drop"
      ) %>%
      tidyr::pivot_wider(
        names_from = wolf_group,
        values_from = mean_share)
    
    tibble::tibble(
      method = "Welch ANOVA",
      df_num = unname(welch$parameter[1]),
      df_den = unname(welch$parameter[2]),
      statistic = unname(welch$statistic),
      p.value = welch$p.value
    ) %>%
      dplyr::bind_cols(group_means)
  }) %>%
  dplyr::ungroup()

welch_format_results_summary <- welch_format_results %>%
  dplyr::mutate(
    df_num = round(df_num, 3),
    df_den = round(df_den, 3),
    statistic = round(statistic, 3),
    p.value = round(p.value, 4),
    `All other parliamentarians` = round(`All other parliamentarians`, 2),
    Wolves = round(Wolves, 2)
  )

# ----------------------------
# Facet labels with Welch ANOVA results
# ----------------------------
format_facet_labels <- welch_format_results %>%
  dplyr::mutate(
    facet_label = paste0(
      post_format,
      "\nWelch ANOVA: F(",
      round(df_num, 1), ", ",
      round(df_den, 1), ") = ",
      round(statistic, 2), ", ",
      format_p_value(p.value)
    )
  ) %>%
  {setNames(.$facet_label, .$post_format)}

# ----------------------------
# Plot post format shares
# ----------------------------
format_y_upper <- stats::quantile(
  post_format_author$prop_format * 100,
  probs = 0.98,
  na.rm = TRUE
)

if (is.na(format_y_upper) || format_y_upper <= 0) {
  format_y_upper <- max(post_format_author$prop_format * 100, na.rm = TRUE)
}

n_format_out_of_frame <- sum(
  post_format_author$prop_format * 100 > format_y_upper,
  na.rm = TRUE
)

p_post_format <- ggplot2::ggplot(
  post_format_author %>%
    dplyr::filter(!is.na(prop_format)),
  ggplot2::aes(
    x = wolf_group,
    y = prop_format * 100,
    color = wolf_group,
    fill = wolf_group)) +
  ggplot2::geom_jitter(
    width = 0.25,
    height = 0,
    alpha = 0.3,
    size = 1.8) +
  ggplot2::geom_boxplot(
    width = 0.4,
    alpha = 0.5,
    color = "black",
    outlier.shape = NA) +
  ggplot2::stat_summary(
    fun = mean,
    geom = "point",
    shape = 18,
    size = 5,
    color = "black",
    fill = "black") +
  ggplot2::facet_wrap(
    ~ post_format,
    labeller = ggplot2::as_labeller(format_facet_labels)) +
  ggplot2::scale_color_manual(values = group_colors) +
  ggplot2::scale_fill_manual(values = group_colors) +
  ggplot2::scale_x_discrete(labels = axis_labels) +
  ggplot2::scale_y_continuous(labels = function(x) paste0(x, "%")) +
  ggplot2::coord_cartesian(
    ylim = c(0, format_y_upper)) +
  ggplot2::labs(
    title = "Post Formats by Group",
    caption = paste0(
      "Y-axis zoomed at the 98th percentile for readability; ",
      n_format_out_of_frame,
      " observation(s) fall above the visible range. Welch ANOVA uses the full data."
    ),
    x = NULL,
    y = "Share of posts"
  ) +
  theme_wolf_distribution +
  ggplot2::theme(
    strip.text = ggplot2::element_text(size = 24, face = "bold"),
    plot.caption = ggplot2::element_text(size = 20, hjust = 0))

welch_format_results_summary
welch_format_results
p_post_format
```

#### Summary
df_num = numerator degrees of freedom
df_den = denominator degrees of freedom.
statistic = the Welch F-statistic

```{r}
welch_main_results <- dplyr::bind_rows(
  welch_engagement,
  welch_followers,
  welch_posts
) %>%
  dplyr::mutate(
    df_num = round(df_num, 3),
    df_den = round(df_den, 3),
    statistic = round(statistic, 3),
    p.value = round(p.value, 4),
    `All other parliamentarians` = round(`All other parliamentarians`, 2),
    Wolves = round(Wolves, 2)
  )

welch_main_results
```
### Export
```{r}
welch_plots <- list(p_mean_engagement = p_mean_engagement,
  p_mean_followers  = p_mean_followers,
  p_mean_posts      = p_mean_posts)

purrr::iwalk(welch_plots,
  ~ ggsave(
    filename = file.path(output_path, paste0(.y, ".png")),
    plot = .x,
    width = 7,
    height = 4,
    dpi = 300))

# Faceted post-format Welch ANOVA plot
ggsave(
  filename = file.path(output_path, "p_post_format.png"),
  plot = p_post_format,
  width = 12,
  height = 7,
  dpi = 300
)
```

# Textual Analysis
**Vocabulary Diversity:** We first estimate the total number of words and the number of unique lemmas used by each politician. Because raw vocabulary size is strongly affected by corpus size, politicians who produce more text have more opportunities to use unique words. To account for this, we log-transform both total words and vocabulary size, then model vocabulary size while controlling for total word count. The main inferential test is therefore an ANCOVA predicting logged vocabulary size from logged total words and group membership. This allows us to assess whether groups differ in vocabulary size among politicians with comparable amounts of textual output.

**Entropy analysis** To assess the consistency or dispersion of politicians’ language over time, we estimate monthly Shannon entropy for each politician. Entropy is calculated from the distribution of lemmas within each politician’s monthly corpus, where higher values indicate that word usage is more dispersed across a wider range of terms and lower values indicate greater concentration around repeated terms. We then average monthly entropy scores for each politician and compare these averages across groups ([Reference 1](https://www.sciencedirect.com/topics/engineering/shannon-entropy)).

*Robusness check*: We also estimate residualized vocabulary diversity as a descriptive measure. This is calculated by regressing logged vocabulary size on logged total words and extracting the residuals. Positive residuals indicate that a politician uses more unique vocabulary than expected given their total word count, whereas negative residuals indicate a smaller vocabulary than expected. This measure helps describe vocabulary diversity adjusted for corpus size.

*Glossary*
*total_words:* Sum of token counts (n) per author across the entire corpus.
*vocab_size:* The count of distinct lemmas (n_distinct(lemma)) used by each politician, across their whole corpus. This is raw lexical diversity — how many unique word-forms (after lemmatization) they've used, with no adjustment for how much they wrote.
*vocab_residual:* log_vocab_size - expected_log_vocab. The leftover, unexplained portion of a politician's logged vocabulary size after accounting for their output volume. This is the key corpus-size-adjusted diversity measure (a positive result indicates richer vocabulary than expected for someone who wrote that much)
*vocab_observed_expected_ratio* vocab_residual is derived from  residuals of a linear model on logged variables, which make it a somewhat abstract scale. This variable is produced with exp(vocab_residual), which back-transforms the residual into a more interpretable ratio scale. E.g. A value of 1.15 means "15% more unique vocabulary than expected for this politician's word count,"


```{r}
# Panel A: raw scale
# Each point = one politician. We overlay a straight-line (OLS) fit
# and a flexible curve (loess) to verify a mismatch, which would require log transforming the continuous variables.

p_raw <- ggplot(df_text_analysis, aes(x = total_words, y = vocab_size)) +
  geom_point(alpha = 0.4, color = "grey30") +
  geom_smooth(method = "lm", se = FALSE,
              color = "firebrick", linewidth = 1) +
  geom_smooth(method = "loess", se = FALSE,
              color = "steelblue", linewidth = 1, linetype = "dashed") +
  scale_x_continuous(labels = label_number(big.mark = ",")) +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  labs(
    title = "Raw scale: straight line vs. actual curve",
    subtitle = "Red = linear fit (what ANCOVA assumes) | Blue dashed = actual pattern",
    x = "Total words",
    y = "Vocabulary size (unique lemmas)"
  ) +
  ggplot2::theme_minimal(
    base_family = "EB Garamond",
    base_size = 30
  )

# Panel B: log-log scale
p_log <- ggplot(df_text_analysis, aes(x = log_total_words, y = log_vocab_size)) +
  geom_point(alpha = 0.4, color = "grey30") +
  geom_smooth(method = "lm", se = FALSE,
              color = "firebrick", linewidth = 1) +
  geom_smooth(method = "loess", se = FALSE,
              color = "steelblue", linewidth = 1, linetype = "dashed") +
  labs(
    title = "Log-log scale",
    x = "log(Total words)",
    y = "log(Vocabulary size)"
  ) +
  ggplot2::theme_minimal(
    base_family = "EB Garamond",
    base_size = 30
  )

p_raw + p_log
```

```{r}
# Textual metrics by politician
df_text_metrics <- tokens_text_lemma_monthly %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    total_words = sum(n, na.rm = TRUE),
    vocab_size = dplyr::n_distinct(lemma),
    
    log_total_words = dplyr::if_else(
      total_words > 1,
      log(total_words),
      NA_real_),
    log_vocab_size = dplyr::if_else(
      vocab_size > 1,
      log(vocab_size),
      NA_real_),
    
    vocab_per_1000_words = dplyr::if_else(
      total_words > 0,
      1000 * vocab_size / total_words,
      NA_real_),
    .groups = "drop") %>%
  
  dplyr::left_join(
    tokens_text_lemma_monthly %>%
      dplyr::group_by(author, month) %>%
      dplyr::mutate(
        p = n / sum(n, na.rm = TRUE)) %>%
      dplyr::summarise(
        month_entropy = -sum(p * log(p), na.rm = TRUE),
        monthly_words = sum(n, na.rm = TRUE),
        .groups = "drop") %>%
      dplyr::group_by(author) %>%
      dplyr::summarise(
        avg_text_entropy = mean(month_entropy, na.rm = TRUE),
        avg_monthly_words = mean(monthly_words, na.rm = TRUE),
        .groups = "drop"), by = "author")

# Merge text metrics with metadata
# Retain accounts with at least 50 posts
df_text_analysis <- nodes_grouped %>%
  dplyr::mutate(
    louvain_community = as.character(louvain_community)) %>%
  dplyr::filter(
    !is.na(total_posts),
    total_posts >= 50) %>%
  dplyr::inner_join(df_text_metrics, by = "author") %>%
  dplyr::filter(
    !is.na(log_total_words),
    !is.na(log_vocab_size),
    total_words > 1,
    vocab_size > 1)

# Residualized vocabulary diversity
lexical_model <- stats::lm(
  log_vocab_size ~ log_total_words,
  data = df_text_analysis)

df_text_analysis <- df_text_analysis %>%
  dplyr::mutate(
    expected_log_vocab = stats::predict(lexical_model, newdata = .),
    vocab_residual = log_vocab_size - expected_log_vocab,
    vocab_observed_expected_ratio = exp(vocab_residual))
```

### Clusters

```{r}
# Set up: top 3 Louvain communities
top_3_communities <- nodes_grouped %>%
  dplyr::filter(!is.na(louvain_community)) %>%
  dplyr::mutate(louvain_community = as.character(louvain_community)) %>%
  dplyr::count(louvain_community, sort = TRUE) %>%
  dplyr::slice_head(n = 3) %>%
  dplyr::pull(louvain_community)

# Retain only top 3 Louvain communities
df_clusters <- df_text_analysis %>%
  dplyr::filter(louvain_community %in% top_3_communities) %>%
  dplyr::mutate(
    louvain_community = factor(
      louvain_community,
      levels = top_3_communities))

# Make cluster 2 the reference 
df_clusters <- df_clusters %>%
  dplyr::mutate(
    louvain_community = stats::relevel(
      louvain_community,
      ref = "2"
    ))
```

```{r}
# Normalized Vocabulary and Entropy
text_summary_vars <- c(
  "total_words",
  "vocab_size",
  "vocab_per_1000_words",
  "vocab_residual",
  "avg_monthly_words",
  "avg_text_entropy")

text_var_labels <- c(
  total_words = "Total words",
  vocab_size = "Vocabulary size",
  vocab_per_1000_words = "Vocabulary per 1,000 words",
  vocab_residual = "Vocabulary diversity adjusted for corpus size",
  avg_monthly_words = "Average monthly words",
  avg_text_entropy = "Average monthly entropy")

# Group-wise summary statistics
text_cluster_summary <- df_clusters %>%
  dplyr::select(louvain_community, dplyr::all_of(text_summary_vars)) %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(text_summary_vars),
    names_to = "variable",
    values_to = "value") %>%
  dplyr::mutate(
    variable = dplyr::recode(variable, !!!as.list(text_var_labels))) %>%
  dplyr::group_by(variable, louvain_community) %>%
  dplyr::summarise(
    n_politicians = sum(!is.na(value)),
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    variance = var(value, na.rm = TRUE),
    median = median(value, na.rm = TRUE),
    .groups = "drop") %>%
  dplyr::mutate(
    pct_above_expected = dplyr::if_else(
      variable == text_var_labels["vocab_residual"],
      (exp(mean) - 1) * 100,
      NA_real_
    ),
    dplyr::across(
      c(mean, sd, variance, median, pct_above_expected),
      ~ round(.x, 3)))

text_cluster_summary
```
*Summary*: Vocabulary diversity adjusted for corpus size (vocab_residual) is highest in Community 3 (M = 0.090), corresponding to approximately 9.4% more vocabulary than expected given its textual output. Community 4 follows (M = 0.036; ≈3.7% above expected), whereas Community 2 has the lowest adjusted vocabulary diversity (M = −0.041; ≈4.0% below expected).

Descriptive analyses show substantial differences in textual output across communities. Community 2 (n = 219) averages approximately 56,400 total words (SD = 40,008) and 1,191 words per month, compared with approximately 90,300 total words (SD = 74,570) and 1,934 words per month in Community 3 (n = 108), and 171,100 total words (SD = 105,876) and 3,583 words per month in Community 4 (n = 87). Thus, politicians in Community 4 are by far the most prolific, but Community 3 displays the greatest vocabulary diversity once differences in corpus size are taken into account.

With regards to entropy, the descriptive results show that politicians in cluster 4 display highest average montly entropy (M=6.535, SD=0.482), followed by those in cluster 3 (M=6.091, SD=0.669). Cluster two has the lowest scores in this regard (M=5.763, SD=0.554).

*Variance diagnostics (robustness check)*: the Fligner-Killeen test assesses whether the variance of an outcome is similar across groups. The null hypothesis is that the variance is equal across the Louvain communities. If this null hypothesis is rejected, there is evidence of heteroskedasticity, meaning that the groups differ not only in their average values but also in how dispersed those values are. 

```{r}
# Variance diagnostics: Fligner-Killeen
diagnostic_vars <- c("vocab_residual", "avg_text_entropy")

diagnostic_var_labels <- c(
  vocab_residual = "Vocabulary diversity adjusted for corpus size",
  avg_text_entropy = "Average monthly entropy"
)

text_variance_diagnostics <- df_clusters %>%
  dplyr::select(louvain_community, dplyr::all_of(diagnostic_vars)) %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(diagnostic_vars),
    names_to = "variable",
    values_to = "value"
  ) %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::group_by(variable) %>%
  dplyr::group_modify(~ {
    
    fligner <- stats::fligner.test(value ~ louvain_community, data = .x)
    
    tibble::tibble(
      fligner_statistic = unname(fligner$statistic),
      fligner_p.value = fligner$p.value
    )
  }) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    variable = dplyr::recode(variable, !!!as.list(diagnostic_var_labels)),
    fligner_statistic = round(fligner_statistic, 3),
    fligner_p.value = round(fligner_p.value, 4)
  )

text_variance_diagnostics
```
*Summary:* The Fligner-Killeen test found no evidence of unequal variances in average monthly entropy across the three Louvain communities, χ²(2) = 3.70, p = .157 — variances here are approximately homogeneous. 

Variance in vocabulary diversity adjusted for corpus size differed significantly across communities, χ²(2) = 26.4, p < .0001. This asymmetry means the two outcomes need different treatment: entropy comparisons can be conducted with a  Welch ANOVA, while comparisons involving vocab_residual should use variance-robust methods.

#### Variety
```{r}
# ANCOVA: vocabulary size controlling for total words
vocab_ancova <- stats::lm(log_vocab_size ~ 
                            log_total_words + louvain_community,
                          data = df_clusters)

vocab_ancova_table <- stats::anova(vocab_ancova) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("term") %>%
  dplyr::rename(
    df = Df,
    sumsq = `Sum Sq`,
    meansq = `Mean Sq`,
    statistic = `F value`,
    p.value = `Pr(>F)`) %>%
  dplyr::mutate(
    dplyr::across(
      c(sumsq, meansq, statistic, p.value),
      ~ round(.x, 4)))

# Improving readability
vocab_ancova_coefficients <- broom::tidy(
  vocab_ancova,
  conf.int = TRUE
) %>%
  dplyr::filter(
    stringr::str_detect(term, "^louvain_community")
  ) %>%
  dplyr::mutate(
    pct_diff = round((exp(estimate) - 1) * 100, 1),
    pct_ci_low = round((exp(conf.low) - 1) * 100, 1),
    pct_ci_high = round((exp(conf.high) - 1) * 100, 1)
  )

# Diagnostic: homogeneity of slopes
vocab_ancova_interaction <- stats::lm(
  log_vocab_size ~ log_total_words * louvain_community,
  data = df_clusters)

vocab_ancova_slope_test <- stats::anova(
  vocab_ancova,
  vocab_ancova_interaction) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("model") %>%
  dplyr::mutate(
    dplyr::across(where(is.numeric), ~ round(.x, 4)))


vocab_ancova_table
vocab_ancova_coefficients
vocab_ancova_slope_test
```
*Summary*: An ANCOVA predicting logged vocabulary size from logged total word count and Louvain community indicated significant differences across communities after accounting for textual output, F(2, 410) = 26.96, p < .001. Relative to Community 2, Community 3 had an estimated vocabulary size approximately 13.9% larger, while Community 4 had an estimated vocabulary size approximately 10.2% larger, controlling for total word count. These results indicate meaningful differences in vocabulary diversity across Louvain communities. The homogeneity-of-slopes test was also significant, F(2, 408) = 5.89, p = .003, indicating that the relationship between corpus size and vocabulary size varies somewhat across communities. Accordingly, the reported percentages are best interpreted as overall adjusted differences between communities rather than as differences that remain constant across all levels of textual output.


#### Entropy 
```{r}
# Welch ANOVA helper
run_cluster_welch <- function(data, outcome, label) {
  outcome <- rlang::ensym(outcome)
  test_df <- data %>%
    dplyr::select(louvain_community, value = !!outcome) %>%
    dplyr::filter(
      !is.na(louvain_community),
      !is.na(value))
  
  welch <- stats::oneway.test(
    value ~ louvain_community,
    data = test_df,
    var.equal = FALSE)
  
  group_means <- test_df %>%
    dplyr::group_by(louvain_community) %>%
    dplyr::summarise(
      mean = mean(value, na.rm = TRUE),
      .groups = "drop") %>%
    tidyr::pivot_wider(
      names_from = louvain_community,
      values_from = mean,
      names_prefix = "community_")
  
  tibble::tibble(
    test = label,
    method = "Welch ANOVA",
    df_num = unname(welch$parameter[1]),
    df_den = unname(welch$parameter[2]),
    statistic = unname(welch$statistic),
    p.value = welch$p.value) %>%
    dplyr::bind_cols(group_means)
}


# ----------------------------
# Welch ANOVA: Entropy
# ----------------------------
text_welch_results <- run_cluster_welch(
  df_clusters,
  avg_text_entropy,
  "Average monthly entropy") %>%
  dplyr::mutate(
    df_num = round(df_num, 3),
    df_den = round(df_den, 3),
    statistic = round(statistic, 3),
    p.value = round(p.value, 4),
    dplyr::across(
      dplyr::starts_with("community_"),
      ~ round(.x, 3)))

# ----------------------------
# Pairwise Welch post-hoc test: entropy
# ----------------------------
pairwise_entropy <- stats::pairwise.t.test(
  x = df_clusters$avg_text_entropy,
  g = df_clusters$louvain_community,
  p.adjust.method = "bonferroni",
  pool.sd = FALSE)

text_welch_results
broom::tidy(pairwise_entropy) %>%
  dplyr::rename(bonferroni_p = p.value)
```

A Welch ANOVA, paired with Bonferroni correction, indicated significant differences in average monthly textual entropy across Louvain communities, F(2, 201) = 73.40, p < .001. Community 4 displayed the highest average entropy (M = 6.54), followed by Community 3 (M = 6.09) and Community 2 (M = 5.76).


*Is the network architecture a strong predictor of both how many words they employ and how much they shift topics month-to-month?*

**Summary**: Welch ANOVAs indicated significant differences across the three largest Louvain communities in both normalized vocabulary diversity and average monthly entropy. For normalized vocabulary diversity, the differences were statistically significant, F(2, 203) = 11.30, p < .001. Community 2 had the highest average score (M = 0.832), followed by Community 1 (M = 0.825) and Community 3 (M = 0.817). Pairwise Welch tests with Bonferroni correction indicated that all three communities differed significantly from one another, although the absolute differences were modest. Differences were more pronounced for average monthly entropy, F(2, 193) = 43.80, p < .001. Community 3 displayed the highest entropy (M = 6.39), followed by Community 2 (M = 6.00) and Community 1 (M = 5.75), with all pairwise comparisons reaching statistical significance after Bonferroni adjustment. These results suggest that the communities differed not only in normalized lexical diversity but also, more strongly, in the consistency and concentration of their monthly textual repertoires.


### Wolves
```{r}
# Variables of interest
wolf_text_vars <- c(
  "total_words",
  "vocab_size",
  "vocab_per_1000_words",
  "vocab_residual",
  "avg_monthly_words",
  "avg_text_entropy")

wolf_text_var_labels <- c(
  total_words = "Total words",
  vocab_size = "Vocabulary size",
  vocab_per_1000_words = "Vocabulary per 1,000 words",
  vocab_residual = "Vocabulary diversity adjusted for corpus size",
  avg_monthly_words = "Average monthly words",
  avg_text_entropy = "Average monthly entropy")


df_wolf_text_analysis <- df_text_analysis %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::mutate(
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")))


# Descriptive statistics
wolf_text_summary <- df_text_analysis %>%
  dplyr::select(wolf_group, dplyr::all_of(wolf_text_vars)) %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(wolf_text_vars),
    names_to = "variable",
    values_to = "value") %>%
  dplyr::mutate(
    variable = dplyr::recode(variable, !!!as.list(wolf_text_var_labels))) %>%
  dplyr::group_by(variable, wolf_group) %>%
  dplyr::summarise(
    n_politicians = sum(!is.na(value)),
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    variance = var(value, na.rm = TRUE),
    median = median(value, na.rm = TRUE),
    .groups = "drop") %>%
  dplyr::mutate(
    pct_above_expected = dplyr::if_else(
      variable == wolf_text_var_labels["vocab_residual"],
      (exp(mean) - 1) * 100,
      NA_real_
    ),
    dplyr::across(
      c(mean, sd, variance, median, pct_above_expected),
      ~ round(.x, 3)))

wolf_text_summary
```
*Summary*: The results for vocabulary diversity adjusted for corpus size (vocab_residual, model-based) show that wolves (n = 39) display substantially greater vocabulary diversity relative to their output, with a mean residual of +0.174 (≈19.0% above expected vocabulary given their corpus size). By comparison, all other politicians (n = 443) have a mean residual of −0.015 (≈1.5% below expected). Thus, once differences in textual output are taken into account, wolves exhibit markedly greater vocabulary diversity.

Descriptive analyses also show that wolves produce substantially more text. Wolves average approximately 140,000 total words (SD = 81,100), compared with about 77,700 words (SD = 75,800) among all other politicians. This difference is also evident in their monthly output: wolves average approximately 2,950 words per month (SD = 1,700), compared with 1,640 (SD = 1,570) among other politicians. Their larger raw vocabulary size—approximately 17,900 distinct words versus 9,160 among other politicians—therefore partly reflects their greater textual output.

With regard to entropy, wolves also display greater average monthly textual entropy (M = 6.55, SD = 0.40) than all other politicians (M = 5.88, SD = 0.68). Taken together, the descriptive results suggest that wolves are not only more prolific communicators but also use a more diverse and evenly distributed vocabulary once differences in corpus size are accounted for.

#### Inspection
```{r}
# Variance diagnostics
wolf_diagnostic_vars <- c("vocab_residual", "avg_text_entropy")

wolf_diagnostic_var_labels <- c(
  vocab_residual = "Vocabulary diversity adjusted for corpus size",
  avg_text_entropy = "Average monthly entropy")

# Fligner-Killeen 
wolf_text_variance_diagnostics <- df_wolf_text_analysis %>%
  dplyr::select(wolf_group, dplyr::all_of(wolf_diagnostic_vars)) %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(wolf_diagnostic_vars),
    names_to = "variable",
    values_to = "value"
  ) %>%
  dplyr::filter(
    !is.na(wolf_group),
    !is.na(value)
  ) %>%
  dplyr::group_by(variable) %>%
  dplyr::group_modify(~ {
    
    fligner <- stats::fligner.test(value ~ wolf_group, data = .x)
    
    tibble::tibble(
      fligner_statistic = unname(fligner$statistic),
      fligner_p.value = fligner$p.value
    )
  }) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    variable = dplyr::recode(variable, !!!as.list(wolf_diagnostic_var_labels)),
    fligner_statistic = round(fligner_statistic, 3),
    fligner_p.value = round(fligner_p.value, 4)
  )

wolf_text_variance_diagnostics
```
The Fligner-Killeen tests indicates unequal variances between wolves and all other parliamentarians for both average monthly entropy, χ² = 8.33, p = .0039, and vocabulary diversity adjusted for corpus size, χ² = 10.6, p = .0011. These results support the use of variance-robust procedures: Welch ANOVA for entropy and heteroskedasticity-robust standard errors for the ANCOVA of vocabulary size.


#### Variety
```{r}
df_wolf_vocab_model <- df_wolf_text_analysis %>%
  dplyr::filter(
    !is.na(wolf_group),
    !is.na(log_vocab_size),
    !is.na(log_total_words)) %>%
  dplyr::mutate(
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")))

# ANCOVA: vocabulary size controlling for total words
wolf_vocab_ancova <- stats::lm(
  log_vocab_size ~ log_total_words + wolf_group,
  data = df_wolf_vocab_model)

# HC3 robust inference
wolf_vocab_ancova_robust <- lmtest::coeftest(
  wolf_vocab_ancova,
  vcov. = sandwich::vcovHC(wolf_vocab_ancova, type = "HC3"))

# Wolves vs. all others
wolf_vocab_effect <- broom::tidy(wolf_vocab_ancova_robust) %>%
  dplyr::filter(term == "wolf_groupWolves") %>%
  dplyr::mutate(
    percent_difference = 100 * (exp(estimate) - 1),
    p.value_fmt = format_p_value(p.value)) %>%
  dplyr::mutate(
    dplyr::across(
      c(estimate, std.error, statistic, percent_difference),
      ~ round(.x, 4)))

# Diagnostic: homogeneity of slopes
wolf_vocab_interaction <- stats::lm(
  log_vocab_size ~ log_total_words * wolf_group,
  data = df_wolf_vocab_model)

wolf_vocab_slope_test <- lmtest::coeftest(
  wolf_vocab_interaction,
  vcov. = sandwich::vcovHC(wolf_vocab_interaction, type = "HC3")) %>%
  broom::tidy() %>%
  dplyr::filter(term == "log_total_words:wolf_groupWolves") %>%
  dplyr::mutate(
    p.value_fmt = format_p_value(p.value),
    dplyr::across(
      c(estimate, std.error, statistic),
      ~ round(.x, 4)))

wolf_vocab_effect
wolf_vocab_slope_test
```
*Summary*: An ANCOVA with HC3 robust inference indicated that wolves have greater vocabulary diversity than other parliamentarians after accounting for textual output. Controlling for total word count, wolves had an estimated vocabulary size approximately 22.2% larger than that of all other parliamentarians (β = 0.201, robust SE = 0.041, t = 4.95, p < .001). The homogeneity-of-slopes test was not significant (β = 0.106, robust SE = 0.096, t = 1.10, p = .271), providing no evidence that the relationship between corpus size and vocabulary size differs between the two groups.

#### Entropy
```{r}
# Welch ANOVA helper: Wolves vs others
run_wolf_welch <- function(data, outcome, label) {
  outcome <- rlang::ensym(outcome)
  test_df <- data %>%
    dplyr::select(wolf_group, value = !!outcome) %>%
    dplyr::filter(
      !is.na(wolf_group),
      !is.na(value))
  
  welch <- stats::oneway.test(
    value ~ wolf_group,
    data = test_df,
    var.equal = FALSE)
  
  group_means <- test_df %>%
    dplyr::group_by(wolf_group) %>%
    dplyr::summarise(
      mean = mean(value, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    tidyr::pivot_wider(
      names_from = wolf_group,
      values_from = mean)
  
  tibble::tibble(
    test = label,
    method = "Welch ANOVA",
    df_num = unname(welch$parameter[1]),
    df_den = unname(welch$parameter[2]),
    statistic = unname(welch$statistic),
    p.value = welch$p.value
  ) %>%
    dplyr::bind_cols(group_means)
}


# Welch ANOVA: entropy
wolf_text_welch_results <- run_wolf_welch(
  df_wolf_text_analysis,
  avg_text_entropy,
  "Average monthly entropy") %>%
  dplyr::mutate(
    df_num = round(df_num, 3),
    df_den = round(df_den, 3),
    statistic = round(statistic, 3),
    p.value_fmt = format_p_value(p.value),
    `All other parliamentarians` = round(`All other parliamentarians`, 3),
    Wolves = round(Wolves, 3))

wolf_text_welch_results
```
Wolves have significantly higher average monthly entropy (Welch F(1, 59.3) = 88.2, p < .001). The test statistic is large (F = 88.2), indicating a strong difference between the group means. The results show that wolves’ monthly language is more lexically dispersed: their communication is less concentrated around a smaller set of repeated terms and appears more varied in the distribution of words used each month.


*Summary: Wolves produce more text, have larger raw vocabularies, and show higher vocabulary diversity after controlling for total word count. They also have significantly higher average monthly entropy.*
The ANCOVA results indicate that wolves use a significantly larger vocabulary than other parliamentarians even after accounting for differences in total word count. Controlling for differences in total word count, we found that group coefficient are positive and statistically significant: wolves had approximately 22.2% higher vocabulary size than other parliamentarians with comparable total word counts. 

Because variance diagnostics indicated heteroskedasticity, we inspected heteroskedasticity-robust standard errors. The wolves coefficient remained significant with HC3 robust standard errors, *b* = 0.201, robust SE = 0.041, *t* = 4.95, *p* < .001, with an approximate robust confidence interval corresponding to 12.9% to 32.4% higher vocabulary size. A homogeneity-of-slopes test was also significant, suggesting that the relationship between corpus size and vocabulary size differs modestly between groups. 

Welch ANOVA showed that wolves had significantly higher average monthly entropy than all other parliamentarians, Welch’s F(1, 59.3) = 88.2, p < .001. Wolves had a mean entropy score of 6.55, compared with 5.88 among other parliamentarians. This indicates that wolves’ monthly communication displays a more dispersed lexical distribution, suggesting greater textual variety or less concentration around a smaller set of repeated terms.


#### Plots
```{r}
# ----------------------------
# Plot-specific p-value format
# ----------------------------
plot_p <- function(p) {
  ifelse(
    p < .001,
    "p < .001",
    paste0("p = ", format_p_value(p))
  )
}

# ----------------------------
# Sample-specific axis labels
# ----------------------------

# Entropy sample
entropy_group_n <- df_wolf_text_analysis %>%
  dplyr::filter(
    !is.na(wolf_group),
    !is.na(avg_text_entropy)
  ) %>%
  dplyr::count(wolf_group)

entropy_axis_labels <- setNames(
  paste0(entropy_group_n$wolf_group, "\n(n=", entropy_group_n$n, ")"),
  entropy_group_n$wolf_group
)

# Vocabulary ANCOVA sample
vocab_group_n <- df_wolf_vocab_model %>%
  dplyr::count(wolf_group)

vocab_axis_labels <- setNames(
  paste0(vocab_group_n$wolf_group, "\n(n=", vocab_group_n$n, ")"),
  vocab_group_n$wolf_group
)

# ----------------------------
# Entropy: Welch ANOVA label
# ----------------------------
entropy_result <- wolf_text_welch_results %>%
  dplyr::filter(test == "Average monthly entropy") %>%
  dplyr::slice(1)

entropy_label <- paste0(
  "Welch ANOVA: F(",
  round(entropy_result$df_num, 0), ", ",
  round(entropy_result$df_den, 1), ") = ",
  round(entropy_result$statistic, 2), ", ",
  plot_p(entropy_result$p.value)
)

# ----------------------------
# Vocabulary: HC3 robust ANCOVA label
# ----------------------------
vocab_robust_F <- wolf_vocab_effect$statistic^2

vocab_percent_label <- paste0(
  ifelse(wolf_vocab_effect$percent_difference > 0, "+", ""),
  round(wolf_vocab_effect$percent_difference, 1),
  "%"
)

vocab_robust_label <- paste0(
  "HC3 robust ANCOVA: F(1, ",
  stats::df.residual(wolf_vocab_ancova), ") = ",
  round(vocab_robust_F, 2), ", ",
  plot_p(wolf_vocab_effect$p.value),
  "; wolves = ", vocab_percent_label
)
```

##### Residualized vocabulary diversity plot
*Directly corresponds to the descriptive measure of “vocabulary relative to expected vocabulary given output”*
```{r}
p_wolf_vocab_residual <- ggplot2::ggplot(
  df_wolf_text_analysis,
  ggplot2::aes(
    x = wolf_group,
    y = vocab_residual,
    fill = wolf_group
  )
) +
  ggplot2::geom_hline(
    yintercept = 0,
    linetype = "dashed",
    linewidth = 0.7
  ) +
  ggplot2::geom_jitter(
    ggplot2::aes(color = wolf_group),
    width = 0.14,
    alpha = 0.22,
    size = 2.6
  ) +
  ggplot2::geom_boxplot(
    width = 0.55,
    alpha = 0.65,
    outlier.shape = NA,
    linewidth = 1.1,
    color = "black"
  ) +
  ggplot2::stat_summary(
    fun = mean,
    geom = "point",
    shape = 18,
    size = 6,
    color = "black"
  ) +
  ggplot2::scale_x_discrete(labels = vocab_axis_labels) +
  ggplot2::scale_fill_manual(values = group_colors) +
  ggplot2::scale_color_manual(values = group_colors) +
  ggplot2::labs(
    title = "Residualized Vocabulary Diversity by Group",
    x = NULL,
    y = "Vocabulary residual",
    caption = paste0(
      "Positive values indicate a larger vocabulary than expected given total word count. ",
      "Inferential comparisons use HC3 robust ANCOVA."
    )
  ) +
  theme_wolf_distribution

p_wolf_vocab_residual
```
##### ANCOVA-adjusted vocabulary size plot
```{r}
# ----------------------------
# ANCOVA-adjusted vocabulary size
# Predictions at mean logged total word count
# ----------------------------

mean_log_total_words <- mean(
  df_wolf_vocab_model$log_total_words,
  na.rm = TRUE
)

ancova_pred_df <- tibble::tibble(
  wolf_group = factor(
    c("All other parliamentarians", "Wolves"),
    levels = c("All other parliamentarians", "Wolves")
  ),
  log_total_words = mean_log_total_words
)

ancova_pred <- stats::predict(
  wolf_vocab_ancova,
  newdata = ancova_pred_df
)

# HC3 robust covariance matrix
robust_vcov <- sandwich::vcovHC(
  wolf_vocab_ancova,
  type = "HC3"
)

X_pred <- stats::model.matrix(
  ~ log_total_words + wolf_group,
  data = ancova_pred_df
)

ancova_pred_se <- sqrt(
  diag(X_pred %*% robust_vcov %*% t(X_pred))
)

crit <- stats::qt(
  .975,
  df = stats::df.residual(wolf_vocab_ancova)
)

ancova_pred_df <- ancova_pred_df %>%
  dplyr::mutate(
    predicted_log_vocab = ancova_pred,
    se = ancova_pred_se,
    lower_log = predicted_log_vocab - crit * se,
    upper_log = predicted_log_vocab + crit * se,
    predicted_vocab_size = exp(predicted_log_vocab),
    lower_vocab_size = exp(lower_log),
    upper_vocab_size = exp(upper_log)
  )

#####################
p_wolf_vocab_ancova <- ggplot2::ggplot(
  ancova_pred_df,
  ggplot2::aes(
    x = wolf_group,
    y = predicted_vocab_size,
    fill = wolf_group
  )
) +
  ggplot2::geom_col(
    width = 0.6,
    alpha = 0.75,
    color = "black",
    linewidth = 1.1
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      ymin = lower_vocab_size,
      ymax = upper_vocab_size
    ),
    width = 0.12,
    linewidth = 1.1
  ) +
  ggplot2::scale_x_discrete(labels = vocab_axis_labels) +
  ggplot2::scale_y_continuous(labels = scales::comma) +
  ggplot2::scale_fill_manual(values = group_colors) +
  ggplot2::labs(
    title = "Vocabulary Size Adjusted for Textual Output",
    subtitle = vocab_robust_label,
    x = NULL,
    y = "Predicted vocabulary size",
    caption = paste0(
      "Predictions estimated at the mean logged total word count. ",
      "Error bars use HC3 robust standard errors."
    )
  ) +
  theme_wolf_distribution

p_wolf_vocab_ancova
```
##### Jittery adjusted vocabulary plot
```{r}
# ----------------------------
# Individual-level adjusted vocabulary values
# Useful given that common-slope ANCOVA is appropriate
# ----------------------------

mean_log_total_words <- mean(
  df_wolf_vocab_model$log_total_words,
  na.rm = TRUE
)

beta_log_total_words <- stats::coef(
  wolf_vocab_ancova
)[["log_total_words"]]

df_wolf_vocab_adjusted <- df_wolf_vocab_model %>%
  dplyr::mutate(
    adjusted_log_vocab_size =
      log_vocab_size -
      beta_log_total_words *
      (log_total_words - mean_log_total_words),
    adjusted_vocab_size = exp(adjusted_log_vocab_size)
  )

# Y-axis zoom
vocab_y_min <- 5000

vocab_y_max <- stats::quantile(
  df_wolf_vocab_adjusted$adjusted_vocab_size,
  probs = 0.98,
  na.rm = TRUE
)

n_vocab_above_visible <- sum(
  df_wolf_vocab_adjusted$adjusted_vocab_size > vocab_y_max,
  na.rm = TRUE
)

vocab_zoom_caption <- paste0(
  "Y-axis zoomed at the 98th percentile for readability; ",
  n_vocab_above_visible,
  " account(s) fall above the visible range. ",
  "HC3 robust ANCOVA uses the full sample."
)



####################
p_wolf_vocab_ancova_jittered <- ggplot2::ggplot(
  df_wolf_vocab_adjusted,
  ggplot2::aes(
    x = wolf_group,
    y = adjusted_vocab_size,
    fill = wolf_group
  )
) +
  ggplot2::geom_jitter(
    ggplot2::aes(color = wolf_group),
    width = 0.14,
    alpha = 0.22,
    size = 2.6
  ) +
  ggplot2::geom_boxplot(
    width = 0.55,
    alpha = 0.65,
    outlier.shape = NA,
    linewidth = 1.1,
    color = "black"
  ) +
  ggplot2::stat_summary(
    fun = mean,
    geom = "point",
    shape = 18,
    size = 6,
    color = "black"
  ) +
  ggplot2::scale_x_discrete(labels = vocab_axis_labels) +
  ggplot2::scale_y_continuous(labels = scales::comma) +
  ggplot2::scale_fill_manual(values = group_colors) +
  ggplot2::scale_color_manual(values = group_colors) +
  ggplot2::coord_cartesian(
    ylim = c(vocab_y_min, vocab_y_max)
  ) +
  ggplot2::labs(
    title = "Vocabulary Size by Group, Adjusted for Total Words",
    subtitle = vocab_robust_label,
    x = NULL,
    y = "Adjusted vocabulary size",
    caption = vocab_zoom_caption
  ) +
  theme_wolf_distribution

p_wolf_vocab_ancova_jittered
```


##### Entropy plot
```{r}
p_wolf_entropy <- ggplot2::ggplot(
  df_wolf_text_analysis %>%
    dplyr::filter(
      !is.na(wolf_group),
      !is.na(avg_text_entropy)
    ),
  ggplot2::aes(
    x = wolf_group,
    y = avg_text_entropy,
    fill = wolf_group
  )
) +
  ggplot2::geom_jitter(
    ggplot2::aes(color = wolf_group),
    width = 0.14,
    alpha = 0.22,
    size = 2.6
  ) +
  ggplot2::geom_boxplot(
    width = 0.55,
    alpha = 0.65,
    outlier.shape = NA,
    linewidth = 1.1,
    color = "black"
  ) +
  ggplot2::stat_summary(
    fun = mean,
    geom = "point",
    shape = 18,
    size = 6,
    color = "black"
  ) +
  ggplot2::scale_x_discrete(labels = entropy_axis_labels) +
  ggplot2::scale_fill_manual(values = group_colors) +
  ggplot2::scale_color_manual(values = group_colors) +
  ggplot2::labs(
    title = "Average Monthly Entropy by Group",
    subtitle = entropy_label,
    x = NULL,
    y = "Average monthly entropy"
  ) +
  theme_wolf_distribution

p_wolf_entropy
```




```{r}
ggplot2::ggsave(
  filename = file.path(output_path, "wolf_vocab_residual.png"),
  plot = p_wolf_vocab_residual,
  width = 14,
  height = 9,
  dpi = 300)

ggplot2::ggsave(
  filename = file.path(output_path, "wolf_vocab_ancova_jittered.png"),
  plot = p_wolf_vocab_ancova_jittered,
  width = 9,
  height = 6,
  dpi = 300)

ggplot2::ggsave(
  filename = file.path(output_path, "wolf_vocab_ancova_adjusted.png"),
  plot = p_wolf_vocab_ancova,
  width = 14,
  height = 9,
  dpi = 300)

ggplot2::ggsave(
  filename = file.path(output_path, "wolf_average_monthly_entropy.png"),
  plot = p_wolf_entropy,
  width = 14,
  height = 9,
  dpi = 300)
```


### Jaccard
This anlysis requires joining the tokens dataset with the group information, filter tokens rows, and then aggregate counts by month, author, and lemma.

#### Wolves
```{r}
# Token overlap: Monthly Jaccard scores
# library(data.table)
# library(Matrix)

# Parameters
top_k_tokens <- 300
min_accounts_per_group <- 2

# ----------------------------
# Prepare account group data
# ----------------------------
account_groups <- nodes_grouped %>%
  dplyr::select(author, wolf_group, is_wolf) %>%
  dplyr::distinct(author, .keep_all = TRUE) %>%
  dplyr::filter(!is.na(author), !is.na(wolf_group))

tokens_dt <- data.table::as.data.table(tokens_text_lemma_monthly)
groups_dt <- data.table::as.data.table(account_groups)

# ----------------------------
# Join group membership and aggregate early
# ----------------------------
tokens_grouped_dt <- tokens_dt[
  groups_dt,
  on = "author",
  nomatch = 0
][
  !is.na(month) & !is.na(lemma) & !is.na(wolf_group),
  .(
    n = sum(n, na.rm = TRUE)
  ),
  by = .(month, author, wolf_group, lemma)
]

# ----------------------------
# Keep top K lemmas per account-month
# ----------------------------
data.table::setorder(
  tokens_grouped_dt,
  month, author, -n, lemma)

top_tokens_monthly_dt <- tokens_grouped_dt[
  ,
  head(.SD, top_k_tokens),
  by = .(month, author)
]
```

```{r}
# Monthly pairwise Jaccard function
compute_monthly_jaccard_pairs <- function(month_dt) {
  
  month_dt <- data.table::as.data.table(month_dt)
  month_dt <- unique(month_dt[, .(author, wolf_group, lemma)])
  
  # If fewer than two accounts are present, no pairwise comparison is possible
  if (data.table::uniqueN(month_dt$author) < 2) {
    return(data.table(
      author_i = character(),
      author_j = character(),
      group_i = character(),
      group_j = character(),
      intersection = numeric(),
      union = numeric(),
      jaccard = numeric(),
      pair_type = character()
    ))
  }
  
  authors <- sort(unique(month_dt$author))
  lemmas  <- sort(unique(month_dt$lemma))
  
  group_lookup <- unique(month_dt[, .(author, wolf_group)])
  group_vec <- as.character(
    group_lookup$wolf_group[match(authors, group_lookup$author)]
  )
  
  # Sparse binary author-token matrix
  M <- Matrix::sparseMatrix(
    i = match(month_dt$author, authors),
    j = match(month_dt$lemma, lemmas),
    x = 1L,
    dims = c(length(authors), length(lemmas)),
    dimnames = list(authors, lemmas)
  )
  
  # Pairwise intersections
  intersections <- as.matrix(Matrix::tcrossprod(M))
  
  # Token set sizes
  set_sizes <- as.numeric(Matrix::rowSums(M))
  
  # Unique author pairs only
  idx <- which(upper.tri(intersections), arr.ind = TRUE)
  
  if (nrow(idx) == 0) {
    return(data.table(
      author_i = character(),
      author_j = character(),
      group_i = character(),
      group_j = character(),
      intersection = numeric(),
      union = numeric(),
      jaccard = numeric(),
      pair_type = character()
    ))
  }
  
  pair_dt <- data.table(
    author_i = authors[idx[, 1]],
    author_j = authors[idx[, 2]],
    group_i = group_vec[idx[, 1]],
    group_j = group_vec[idx[, 2]],
    intersection = intersections[idx],
    union = set_sizes[idx[, 1]] + set_sizes[idx[, 2]] - intersections[idx]
  )
  
  pair_dt[
    ,
    jaccard := intersection / union
  ]
  
  pair_dt[
    ,
    pair_type := data.table::fcase(
      group_i == "Wolves" &
        group_j == "Wolves",
      "Wolf-Wolf",
      
      group_i == "All other parliamentarians" &
        group_j == "All other parliamentarians",
      "Other-Other",
      
      default = "Wolf-Other"
    )
  ]
  
  pair_dt[]
}
```

```{r}
# Calculate monthly overlap
pair_jaccard_monthly_dt <- top_tokens_monthly_dt[
  ,
  compute_monthly_jaccard_pairs(.SD),
  by = month]

# Summarise monthly overlap
monthly_jaccard_summary <- pair_jaccard_monthly_dt %>%
  as_tibble() %>%
  group_by(month, pair_type) %>%
  summarise(
    n_pairs = n(),
    mean_jaccard = mean(jaccard, na.rm = TRUE),
    median_jaccard = median(jaccard, na.rm = TRUE),
    sd_jaccard = sd(jaccard, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    pair_type = factor(
      pair_type,
      levels = c("Other-Other", "Wolf-Other", "Wolf-Wolf")
    )
  ) %>%
  arrange(month, pair_type)

monthly_jaccard_summary
```

```{r}
# Average monthly Jaccard scores across full period
jaccard_period_summary <- monthly_jaccard_summary %>%
  group_by(pair_type) %>%
  summarise(
    n_months = n(),
    mean_monthly_jaccard = mean(mean_jaccard, na.rm = TRUE),
    median_monthly_jaccard = median(mean_jaccard, na.rm = TRUE),
    sd_monthly_jaccard = sd(mean_jaccard, na.rm = TRUE),
    se_monthly_jaccard = sd_monthly_jaccard / sqrt(n_months),
    ci_low = mean_monthly_jaccard - 1.96 * se_monthly_jaccard,
    ci_high = mean_monthly_jaccard + 1.96 * se_monthly_jaccard,
    weighted_mean_jaccard = weighted.mean(
      mean_jaccard,
      w = n_pairs,
      na.rm = TRUE
    ),
    .groups = "drop"
  )

jaccard_period_summary
```

```{r}
# ----------------------------
# Diagnostic 1: account-month token selection
# ----------------------------
account_month_token_counts <- top_tokens_monthly_dt[
  ,
  .(
    tokens_kept = .N
  ),
  by = .(month, author, wolf_group)
]

token_selection_diagnostics <- account_month_token_counts[
  ,
  .(
    n_account_months = .N,
    n_authors = data.table::uniqueN(author),
    n_months = data.table::uniqueN(month),
    max_tokens_per_account_month = max(tokens_kept, na.rm = TRUE),
    mean_tokens_per_account_month = mean(tokens_kept, na.rm = TRUE),
    n_account_months_below_top_k = sum(tokens_kept < top_k_tokens, na.rm = TRUE),
    pct_account_months_below_top_k = 100 * mean(tokens_kept < top_k_tokens, na.rm = TRUE)
  )
]

token_selection_diagnostics

# ----------------------------
# Diagnostic 2: monthly group availability
# ----------------------------
monthly_author_diagnostics <- account_month_token_counts[
  ,
  .(
    n_authors = data.table::uniqueN(author),
    n_wolves = data.table::uniqueN(author[wolf_group == "Wolves"]),
    n_others = data.table::uniqueN(author[wolf_group == "All other parliamentarians"]),
    n_account_months = .N,
    mean_tokens_per_account_month = mean(tokens_kept, na.rm = TRUE),
    min_tokens_per_account_month = min(tokens_kept, na.rm = TRUE),
    max_tokens_per_account_month = max(tokens_kept, na.rm = TRUE)
  ),
  by = month
]

monthly_pair_diagnostics <- pair_jaccard_monthly_dt %>%
  as_tibble() %>%
  mutate(
    pair_type_id = dplyr::recode(
      pair_type,
      "Other-Other" = "other_other",
      "Wolf-Other" = "wolf_other",
      "Wolf-Wolf" = "wolf_wolf"
    )
  ) %>%
  count(month, pair_type_id, name = "n_pairs") %>%
  tidyr::pivot_wider(
    names_from = pair_type_id,
    values_from = n_pairs,
    values_fill = 0,
    names_prefix = "pairs_"
  )

monthly_diagnostics <- monthly_author_diagnostics %>%
  as_tibble() %>%
  left_join(
    monthly_pair_diagnostics,
    by = "month"
  ) %>%
  mutate(
    across(
      starts_with("pairs_"),
      ~ tidyr::replace_na(.x, 0)
    ),
    has_wolf_wolf_pairs = pairs_wolf_wolf > 0,
    has_other_other_pairs = pairs_other_other > 0,
    has_wolf_other_pairs = pairs_wolf_other > 0,
    
    enough_for_wolf_vs_other =
      has_wolf_wolf_pairs & has_other_other_pairs,
    
    enough_for_within_vs_between =
      has_wolf_wolf_pairs & has_other_other_pairs & has_wolf_other_pairs
  ) %>%
  arrange(month)

monthly_diagnostics

# ----------------------------
# Diagnostic 3: months with insufficient information
# ----------------------------
months_with_limited_information <- monthly_diagnostics %>%
  filter(
    !enough_for_wolf_vs_other |
      !enough_for_within_vs_between
  )

months_with_limited_information
```

```{r}
# ----------------------------
# Diagnostic 4: most widely shared top tokens
# ----------------------------
token_prevalence_monthly <- top_tokens_monthly_dt[
  ,
  .(
    n_accounts_using_token = data.table::uniqueN(author),
    total_token_count = sum(n, na.rm = TRUE)
  ),
  by = .(month, lemma)
][
  monthly_author_diagnostics[, .(month, n_authors)],
  on = "month"
][
  ,
  prop_accounts_using_token := n_accounts_using_token / n_authors
]

most_widely_shared_tokens <- token_prevalence_monthly[
  ,
  .(
    mean_prop_accounts_using_token = mean(prop_accounts_using_token, na.rm = TRUE),
    max_prop_accounts_using_token = max(prop_accounts_using_token, na.rm = TRUE),
    n_months_present = data.table::uniqueN(month),
    total_token_count = sum(total_token_count, na.rm = TRUE)
  ),
  by = lemma
][
  order(-mean_prop_accounts_using_token, -total_token_count)
][
  1:50
]

most_widely_shared_tokens
```

#### Clusters
```{r}
# ----------------------------
# Louvain token overlap: set up
# ----------------------------
cluster_groups <- df_clusters %>%
  dplyr::select(author, louvain_community) %>%
  dplyr::distinct(author, .keep_all = TRUE) %>%
  dplyr::filter(
    !is.na(author),
    !is.na(louvain_community)
  ) %>%
  dplyr::mutate(
    louvain_community = as.character(louvain_community)
  )

tokens_louvain_dt <- data.table::as.data.table(tokens_text_lemma_monthly)
cluster_groups_dt <- data.table::as.data.table(cluster_groups)

tokens_louvain_grouped_dt <- tokens_louvain_dt[
  cluster_groups_dt,
  on = "author",
  nomatch = 0
][
  !is.na(month) & !is.na(lemma) & !is.na(louvain_community),
  .(
    n = sum(n, na.rm = TRUE)
  ),
  by = .(month, author, louvain_community, lemma)
]

data.table::setorder(
  tokens_louvain_grouped_dt,
  month, author, -n, lemma
)

top_tokens_louvain_monthly_dt <- tokens_louvain_grouped_dt[
  ,
  head(.SD, top_k_tokens),
  by = .(month, author)
]
```

```{r}
# ----------------------------
# Monthly pairwise Jaccard function
# ----------------------------
compute_monthly_jaccard_pairs_louvain <- function(month_dt) {
  
  month_dt <- data.table::as.data.table(month_dt)
  
  month_dt <- unique(
    month_dt[
      ,
      .(author, louvain_community, lemma)
    ]
  )
  
  if (data.table::uniqueN(month_dt$author) < 2) {
    return(data.table::data.table(
      author_i = character(),
      author_j = character(),
      community_i = character(),
      community_j = character(),
      community_pair = character(),
      comparison_type = character(),
      intersection = numeric(),
      union = numeric(),
      jaccard = numeric()
    ))
  }
  
  authors <- sort(unique(month_dt$author))
  lemmas  <- sort(unique(month_dt$lemma))
  
  community_lookup <- unique(
    month_dt[
      ,
      .(author, louvain_community)
    ]
  )
  
  community_vec <- as.character(
    community_lookup$louvain_community[
      match(authors, community_lookup$author)
    ]
  )
  
  M <- Matrix::sparseMatrix(
    i = match(month_dt$author, authors),
    j = match(month_dt$lemma, lemmas),
    x = 1L,
    dims = c(length(authors), length(lemmas)),
    dimnames = list(authors, lemmas)
  )
  
  intersections <- as.matrix(Matrix::tcrossprod(M))
  set_sizes <- as.numeric(Matrix::rowSums(M))
  
  idx <- which(upper.tri(intersections), arr.ind = TRUE)
  
  if (nrow(idx) == 0) {
    return(data.table::data.table(
      author_i = character(),
      author_j = character(),
      community_i = character(),
      community_j = character(),
      community_pair = character(),
      comparison_type = character(),
      intersection = numeric(),
      union = numeric(),
      jaccard = numeric()
    ))
  }
  
  community_i_raw <- community_vec[idx[, 1]]
  community_j_raw <- community_vec[idx[, 2]]
  
  community_i_order <- match(community_i_raw, top_3_communities)
  community_j_order <- match(community_j_raw, top_3_communities)
  
  community_first <- ifelse(
    community_i_order <= community_j_order,
    community_i_raw,
    community_j_raw
  )
  
  community_second <- ifelse(
    community_i_order <= community_j_order,
    community_j_raw,
    community_i_raw
  )
  
  pair_dt <- data.table::data.table(
    author_i = authors[idx[, 1]],
    author_j = authors[idx[, 2]],
    community_i = community_i_raw,
    community_j = community_j_raw,
    community_pair = paste0(community_first, "-", community_second),
    intersection = intersections[idx],
    union = set_sizes[idx[, 1]] + set_sizes[idx[, 2]] - intersections[idx]
  )
  
  pair_dt[
    ,
    jaccard := intersection / union
  ]
  
  pair_dt[
    ,
    comparison_type := data.table::fifelse(
      community_i == community_j,
      "Within community",
      "Between communities"
    )
  ]
  
  pair_dt[]
}
```

```{r}
# Calculate monthly Louvain Jaccard scores
pair_jaccard_louvain_monthly_dt <- top_tokens_louvain_monthly_dt[
  ,
  compute_monthly_jaccard_pairs_louvain(.SD),
  by = month
]

# Pair-level monthly summary
community_pair_levels <- unlist(
  lapply(seq_along(top_3_communities), function(i) {
    paste0(
      top_3_communities[i],
      "-",
      top_3_communities[i:length(top_3_communities)])}))

monthly_jaccard_louvain_summary <- pair_jaccard_louvain_monthly_dt %>%
  as_tibble() %>%
  group_by(month, community_pair, comparison_type) %>%
  summarise(
    n_pairs = n(),
    mean_jaccard = mean(jaccard, na.rm = TRUE),
    median_jaccard = median(jaccard, na.rm = TRUE),
    sd_jaccard = sd(jaccard, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    community_pair = factor(
      community_pair,
      levels = community_pair_levels
    ),
    comparison_type = factor(
      comparison_type,
      levels = c("Within community", "Between communities"))) %>%
  arrange(month, community_pair)

monthly_jaccard_louvain_summary
```

```{r}
# ----------------------------
# Pair-level period summary
# ----------------------------
jaccard_louvain_period_summary <- monthly_jaccard_louvain_summary %>%
  group_by(community_pair, comparison_type) %>%
  summarise(
    n_months = n(),
    mean_monthly_jaccard = mean(mean_jaccard, na.rm = TRUE),
    median_monthly_jaccard = median(mean_jaccard, na.rm = TRUE),
    sd_monthly_jaccard = sd(mean_jaccard, na.rm = TRUE),
    se_monthly_jaccard = sd_monthly_jaccard / sqrt(n_months),
    ci_low = mean_monthly_jaccard - 1.96 * se_monthly_jaccard,
    ci_high = mean_monthly_jaccard + 1.96 * se_monthly_jaccard,
    weighted_mean_jaccard = weighted.mean(
      mean_jaccard,
      w = n_pairs,
      na.rm = TRUE
    ),
    .groups = "drop"
  )

jaccard_louvain_period_summary
```

```{r}
# ----------------------------
# Broad within/between monthly summary
# ----------------------------
monthly_louvain_within_between <- pair_jaccard_louvain_monthly_dt %>%
  as_tibble() %>%
  group_by(month, comparison_type) %>%
  summarise(
    n_pairs = n(),
    mean_jaccard = mean(jaccard, na.rm = TRUE),
    median_jaccard = median(jaccard, na.rm = TRUE),
    sd_jaccard = sd(jaccard, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    comparison_type = factor(
      comparison_type,
      levels = c("Within community", "Between communities")
    )
  ) %>%
  arrange(month, comparison_type)

monthly_louvain_within_between
```

```{r}
# ----------------------------
# Broad within/between period summary
# ----------------------------
louvain_within_between_period_summary <- monthly_louvain_within_between %>%
  group_by(comparison_type) %>%
  summarise(
    n_months = n(),
    mean_monthly_jaccard = mean(mean_jaccard, na.rm = TRUE),
    median_monthly_jaccard = median(mean_jaccard, na.rm = TRUE),
    sd_monthly_jaccard = sd(mean_jaccard, na.rm = TRUE),
    se_monthly_jaccard = sd_monthly_jaccard / sqrt(n_months),
    ci_low = mean_monthly_jaccard - 1.96 * se_monthly_jaccard,
    ci_high = mean_monthly_jaccard + 1.96 * se_monthly_jaccard,
    weighted_mean_jaccard = weighted.mean(
      mean_jaccard,
      w = n_pairs,
      na.rm = TRUE
    ),
    .groups = "drop"
  )

louvain_within_between_period_summary
```

```{r}
# ----------------------------
# Within-minus-between test
# ----------------------------
louvain_within_between_wide <- monthly_louvain_within_between %>%
  dplyr::select(month, comparison_type, mean_jaccard) %>%
  tidyr::pivot_wider(
    names_from = comparison_type,
    values_from = mean_jaccard
  ) %>%
  dplyr::mutate(
    within_minus_between =
      `Within community` - `Between communities`
  )

safe_one_sample_ttest_louvain <- function(x) {
  x <- x[!is.na(x)]
  
  if (length(x) < 2) {
    return(list(
      estimate = mean(x, na.rm = TRUE),
      p.value = NA_real_,
      n = length(x)
    ))
  }
  
  test <- stats::t.test(x, mu = 0)
  
  list(
    estimate = mean(x, na.rm = TRUE),
    p.value = test$p.value,
    n = length(x)
  )
}

louvain_within_between_test <- safe_one_sample_ttest_louvain(
  louvain_within_between_wide$within_minus_between
)

louvain_jaccard_test_results <- tibble::tibble(
  comparison = "Within-community minus between-community",
  estimate = louvain_within_between_test$estimate,
  n_months = louvain_within_between_test$n,
  p_value = louvain_within_between_test$p.value,
  p_formatted = format_p_value(p_value)
)

louvain_jaccard_test_results
```
```{r}
# ----------------------------
# Optional model: differences across community-pair types
# ----------------------------
louvain_pair_model <- stats::lm(
  mean_jaccard ~ community_pair + factor(month),
  data = monthly_jaccard_louvain_summary
)

louvain_pair_anova <- stats::anova(louvain_pair_model)

louvain_pair_anova
```


# =============
# DUMPSTER 


## Communication Style

```{r}
# Account-level style summary from df_fb
style_author <- df_fb %>%
  dplyr::mutate(
    programmatic_matches   = dplyr::coalesce(programmatic_matches, 0),
    parochial_matches      = dplyr::coalesce(parochial_matches, 0),
    propagandistic_matches = dplyr::coalesce(propagandistic_matches, 0)
  ) %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    # Number of posts by account
    n_posts = dplyr::n(),
    
    # Total dictionary matches by account
    parochial_matches = sum(parochial_matches, na.rm = TRUE),
    programmatic_matches = sum(programmatic_matches, na.rm = TRUE),
    propagandistic_matches = sum(propagandistic_matches, na.rm = TRUE),
    
    # Account-level number of posts by dominant style
    author_parochial_posts = sum(dominant_style == "Parochial", na.rm = TRUE),
    author_programmatic_posts = sum(dominant_style == "Programmatic", na.rm = TRUE),
    author_propagandistic_posts = sum(dominant_style == "Propagandistic", na.rm = TRUE),
    
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    # Account-level percentages using each account's own number of posts as baseline
    ratio_parochial_posts = 100 * author_parochial_posts / n_posts,
    ratio_programmatic_posts = 100 * author_programmatic_posts / n_posts,
    ratio_propagandistic_posts = 100 * author_propagandistic_posts / n_posts
  ) %>%
  dplyr::left_join(
    nodes_grouped %>%
      dplyr::select(author, wolf_group),
    by = "author"
  ) %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::mutate(
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")
    ))


# Group-level style summary
style_summary <- style_author %>%
  dplyr::group_by(wolf_group) %>%
  dplyr::summarise(
    # Group size and total activity
    n_members = dplyr::n(),
    n_posts = sum(n_posts, na.rm = TRUE),
    
    # Dictionary matches: means and SDs across accounts
    mean_parochial_matches = mean(parochial_matches, na.rm = TRUE),
    sd_parochial_matches = sd(parochial_matches, na.rm = TRUE),
    
    mean_programmatic_matches = mean(programmatic_matches, na.rm = TRUE),
    sd_programmatic_matches = sd(programmatic_matches, na.rm = TRUE),
    
    mean_propagandistic_matches = mean(propagandistic_matches, na.rm = TRUE),
    sd_propagandistic_matches = sd(propagandistic_matches, na.rm = TRUE),
    
    # Total number of posts classified into each dominant style
    count_parochial_posts = sum(author_parochial_posts, na.rm = TRUE),
    count_programmatic_posts = sum(author_programmatic_posts, na.rm = TRUE),
    count_propagandistic_posts = sum(author_propagandistic_posts, na.rm = TRUE),
    
    # Average number of dominant-style posts per account
    mean_parochial_posts = mean(author_parochial_posts, na.rm = TRUE),
    sd_parochial_posts = sd(author_parochial_posts, na.rm = TRUE),
    
    mean_programmatic_posts = mean(author_programmatic_posts, na.rm = TRUE),
    sd_programmatic_posts = sd(author_programmatic_posts, na.rm = TRUE),
    
    mean_propagandistic_posts = mean(author_propagandistic_posts, na.rm = TRUE),
    sd_propagandistic_posts = sd(author_propagandistic_posts, na.rm = TRUE),
    
    # Average share of each account's posts classified into each dominant style
    mean_ratio_parochial_posts = mean(ratio_parochial_posts, na.rm = TRUE),
    sd_ratio_parochial_posts = sd(ratio_parochial_posts, na.rm = TRUE),
    
    mean_ratio_programmatic_posts = mean(ratio_programmatic_posts, na.rm = TRUE),
    sd_ratio_programmatic_posts = sd(ratio_programmatic_posts, na.rm = TRUE),
    
    mean_ratio_propagandistic_posts = mean(ratio_propagandistic_posts, na.rm = TRUE),
    sd_ratio_propagandistic_posts = sd(ratio_propagandistic_posts, na.rm = TRUE),
    
    .groups = "drop"
  )


# Formatted version
style_summary_formatted <- style_summary %>%
  dplyr::mutate(
    dplyr::across(
      c(
        n_members,
        n_posts,
        count_parochial_posts,
        count_programmatic_posts,
        count_propagandistic_posts
      ),
      ~ round(.x, 0)
    ),
    dplyr::across(
      starts_with("mean_") | starts_with("sd_"),
      ~ round(.x, 2)))
```

#### Plots

```{r}
style_matches_plot_data <- style_summary %>%
  dplyr::select(
    wolf_group,
    mean_parochial_matches,
    sd_parochial_matches,
    mean_programmatic_matches,
    sd_programmatic_matches,
    mean_propagandistic_matches,
    sd_propagandistic_matches
  ) %>%
  tidyr::pivot_longer(
    cols = -wolf_group,
    names_to = c("stat", "style"),
    names_pattern = "(mean|sd)_(.*)_matches",
    values_to = "value"
  ) %>%
  tidyr::pivot_wider(
    names_from = stat,
    values_from = value
  ) %>%
  dplyr::mutate(
    style = dplyr::recode(
      style,
      parochial = "Parochial",
      programmatic = "Programmatic",
      propagandistic = "Propagandistic"
    ),
    style = factor(
      style,
      levels = c("Parochial", "Programmatic", "Propagandistic")))

p_style_matches <- ggplot(
  style_matches_plot_data,
  aes(x = style, y = mean, fill = wolf_group)
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7
  ) +
  geom_errorbar(
    aes(
      ymin = pmax(mean - sd, 0),
      ymax = mean + sd
    ),
    position = position_dodge(width = 0.8),
    width = 0.1,
    linewidth = 0.8
  ) +
  scale_fill_manual(values = group_colors) +
  scale_y_continuous(labels = comma) +
  labs(
    title = "Mean Number of Style Matches per Account, Separated by Group",
    x = NULL,
    y = "Mean number of matches per account",
    fill = NULL
  ) +
  theme_wolves() +
  theme(legend.position = "bottom")

p_style_matches
```

```{r}
style_dominant_plot_data <- style_summary %>%
  dplyr::select(
    wolf_group,
    mean_parochial_posts,
    sd_parochial_posts,
    mean_programmatic_posts,
    sd_programmatic_posts,
    mean_propagandistic_posts,
    sd_propagandistic_posts
  ) %>%
  tidyr::pivot_longer(
    cols = -wolf_group,
    names_to = c("stat", "style"),
    names_pattern = "(mean|sd)_(.*)_posts",
    values_to = "value"
  ) %>%
  tidyr::pivot_wider(
    names_from = stat,
    values_from = value
  ) %>%
  dplyr::mutate(
    style = dplyr::recode(
      style,
      parochial = "Parochial",
      programmatic = "Programmatic",
      propagandistic = "Propagandistic"
    ),
    style = factor(
      style,
      levels = c("Parochial", "Programmatic", "Propagandistic")
    )
  )

p_dominant_style_posts <- ggplot(
  style_dominant_plot_data,
  aes(x = style, y = mean, fill = wolf_group)
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7
  ) +
  geom_errorbar(
    aes(
      ymin = pmax(mean - sd, 0),
      ymax = mean + sd
    ),
    position = position_dodge(width = 0.8),
    width = 0.1,
    linewidth = 0.8
  ) +
  scale_fill_manual(values = group_colors) +
  scale_y_continuous(labels = comma) +
  labs(
    title = "Mean Number of Dominant-Style Posts by Group",
    x = NULL,
    y = "Mean number of posts per account",
    fill = NULL
  ) +
  theme_wolves() +
  theme(
    legend.position = "bottom"
  )

p_dominant_style_posts
```

```{r}
style_dominant_ratio_plot_data <- style_summary %>%
  dplyr::select(
    wolf_group,
    mean_ratio_parochial_posts,
    sd_ratio_parochial_posts,
    mean_ratio_programmatic_posts,
    sd_ratio_programmatic_posts,
    mean_ratio_propagandistic_posts,
    sd_ratio_propagandistic_posts
  ) %>%
  tidyr::pivot_longer(
    cols = -wolf_group,
    names_to = c("stat", "style"),
    names_pattern = "(mean|sd)_ratio_(.*)_posts",
    values_to = "value"
  ) %>%
  tidyr::pivot_wider(
    names_from = stat,
    values_from = value
  ) %>%
  dplyr::mutate(
    style = dplyr::recode(
      style,
      parochial = "Parochial",
      programmatic = "Programmatic",
      propagandistic = "Propagandistic"
    ),
    style = factor(
      style,
      levels = c("Parochial", "Programmatic", "Propagandistic")
    )
  )

p_dominant_style_ratios <- ggplot(
  style_dominant_ratio_plot_data,
  aes(x = style, y = mean, fill = wolf_group)
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7
  ) +
  geom_errorbar(
    aes(
      ymin = pmax(mean - sd, 0),
      ymax = mean + sd
    ),
    position = position_dodge(width = 0.8),
    width = 0.1,
    linewidth = 0.8
  ) +
  scale_fill_manual(values = group_colors) +
  scale_y_continuous(
    labels = function(x) paste0(x, "%")
  ) +
  labs(
    title = "Dominant Styles by Group",
    x = NULL,
    y = "Mean share of posts per account",
    fill = NULL
  ) +
  theme_wolves() +
  theme(
    legend.position = "bottom")

p_dominant_style_ratios
```

#### Negativity

```{r}
#  negativity_analysis <- readr::read_rds(
#   "C:/Users/andre/OneDrive/UT Austin/Dissertation [PhD UT]/Dissertation Articles/Lacracao Logic/_processed_data/fb_analysis.rds"
# )
#Inspect
# glimpse(negativity_analysis)

negativity_author <- negativity_analysis %>%
  dplyr::mutate(
    lacracao_matches = dplyr::coalesce(lacracao_matches, 0),
    compound_sentiment = as.numeric(compound_sentiment),
    
    # Negative intensity: post has compound sentiment below zero
    has_negative_intensity = compound_sentiment < 0,
    
    # Antagonistic post: post has at least one lacracao/antagonistic match
    has_antagonistic_match = lacracao_matches >= 1
  ) %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    # Total lacracao / antagonistic matches by account
    lacracao_matches = sum(lacracao_matches, na.rm = TRUE),
    
    # Mean compound sentiment by account
    mean_compound_sentiment_author = mean(compound_sentiment, na.rm = TRUE),
    
    # Count of posts with negative intensity by account
    count_negative_intensity_posts_author = sum(
      has_negative_intensity,
      na.rm = TRUE
    ),
    
    # Count of antagonistic posts by account
    count_antagonistic_posts_author = sum(
      has_antagonistic_match,
      na.rm = TRUE
    ),
    
    .groups = "drop"
  ) %>%
  dplyr::left_join(
    nodes_grouped %>%
      dplyr::select(author, wolf_group),
    by = "author"
  ) %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::mutate(
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")
    )
  )


# Group-level negativity/style summary
negativity_summary <- negativity_author %>%
  dplyr::group_by(wolf_group) %>%
  dplyr::summarise(
    # Lacracao / antagonistic matches
    mean_lacracao_matches = mean(lacracao_matches, na.rm = TRUE),
    sd_lacracao_matches = sd(lacracao_matches, na.rm = TRUE),
    
    # Compound sentiment
    mean_compound_sentiment = mean(
      mean_compound_sentiment_author,
      na.rm = TRUE
    ),
    sd_compound_sentiment = sd(
      mean_compound_sentiment_author,
      na.rm = TRUE
    ),
    
    # Posts with negative intensity
    count_negative_intensity_posts = sum(
      count_negative_intensity_posts_author,
      na.rm = TRUE
    ),
    mean_negative_intensity_posts = mean(
      count_negative_intensity_posts_author,
      na.rm = TRUE
    ),
    sd_negative_intensity_posts = sd(
      count_negative_intensity_posts_author,
      na.rm = TRUE
    ),
    
    # Antagonistic posts
    count_antagonistic_posts = sum(
      count_antagonistic_posts_author,
      na.rm = TRUE
    ),
    mean_antagonistic_posts = mean(
      count_antagonistic_posts_author,
      na.rm = TRUE
    ),
    sd_antagonistic_posts = sd(
      count_antagonistic_posts_author,
      na.rm = TRUE
    ),
    
    .groups = "drop"
  )


# Add negativity variables to style_summary
style_summary <- style_summary %>%
  dplyr::left_join(
    negativity_summary,
    by = "wolf_group"
  )


# Recreate formatted version after all variables have been added
style_summary_formatted <- style_summary %>%
  dplyr::mutate(
    dplyr::across(
      c(
        n_members,
        n_posts,
        count_parochial_posts,
        count_programmatic_posts,
        count_propagandistic_posts,
        count_negative_intensity_posts,
        count_antagonistic_posts
      ),
      ~ round(.x, 0)
    ),
    dplyr::across(
      starts_with("mean_") | starts_with("sd_"),
      ~ round(.x, 2)
    )
  )

# Inspect
style_summary
style_summary_formatted
```

```{r}
style_matches_plot_data <- style_summary %>%
  dplyr::select(
    wolf_group,
    mean_parochial_matches,
    sd_parochial_matches,
    mean_programmatic_matches,
    sd_programmatic_matches,
    mean_propagandistic_matches,
    sd_propagandistic_matches,
    mean_lacracao_matches,
    sd_lacracao_matches
  ) %>%
  tidyr::pivot_longer(
    cols = -wolf_group,
    names_to = c("stat", "style"),
    names_pattern = "(mean|sd)_(.*)_matches",
    values_to = "value"
  ) %>%
  tidyr::pivot_wider(
    names_from = stat,
    values_from = value
  ) %>%
  dplyr::mutate(
    style = dplyr::recode(
      style,
      parochial = "Parochial",
      programmatic = "Programmatic",
      propagandistic = "Propagandistic",
      lacracao = "Antagonistic"
    ),
    style = factor(
      style,
      levels = c(
        "Parochial",
        "Programmatic",
        "Propagandistic",
        "Antagonistic"
      )
    )
  )

p_style_matches <- ggplot(
  style_matches_plot_data,
  aes(x = style, y = mean, fill = wolf_group)
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7
  ) +
  geom_errorbar(
    aes(
      ymin = pmax(mean - sd, 0),
      ymax = mean + sd
    ),
    position = position_dodge(width = 0.8),
    width = 0.1,
    linewidth = 0.8
  ) +
  scale_fill_manual(values = group_colors) +
  scale_y_continuous(labels = comma) +
  labs(
    title = "Mean Dictionary Matches per Account by Group and Style",
    x = NULL,
    y = "Mean number of matches per account",
    fill = NULL
  ) +
  theme_wolves() +
  theme(
    legend.position = "bottom"
  )

p_style_matches
```

```{r}
compound_sentiment_plot_data <- style_summary %>%
  dplyr::select(
    wolf_group,
    mean_compound_sentiment,
    sd_compound_sentiment
  )

p_compound_sentiment <- ggplot(
  compound_sentiment_plot_data,
  aes(x = wolf_group, y = mean_compound_sentiment, fill = wolf_group)
) +
  geom_col(
    width = 0.65
  ) +
  geom_errorbar(
    aes(
      ymin = mean_compound_sentiment - sd_compound_sentiment,
      ymax = mean_compound_sentiment + sd_compound_sentiment
    ),
    width = 0.1,
    linewidth = 0.8
  ) +
  scale_fill_manual(values = group_colors) +
  labs(
    title = "Mean Compound Sentiment by Group",
    x = NULL,
    y = "Mean compound sentiment per account",
    fill = NULL
  ) +
  theme_wolves() +
  theme(
    legend.position = "none"
  )

p_compound_sentiment
```

```{r}
antagonistic_posts_summary <- negativity_analysis %>%
  dplyr::mutate(
    lacracao_matches = dplyr::coalesce(lacracao_matches, 0),
    has_antagonistic_match = lacracao_matches >= 1
  ) %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    count_antagonistic_posts_author = sum(has_antagonistic_match, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  dplyr::left_join(
    nodes_grouped %>%
      dplyr::select(author, wolf_group),
    by = "author"
  ) %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::group_by(wolf_group) %>%
  dplyr::summarise(
    count_antagonistic_posts = sum(count_antagonistic_posts_author, na.rm = TRUE),
    mean_antagonistic_posts = mean(count_antagonistic_posts_author, na.rm = TRUE),
    sd_antagonistic_posts = sd(count_antagonistic_posts_author, na.rm = TRUE),
    .groups = "drop"
  )

negative_antagonistic_plot_data <- style_summary %>%
  dplyr::select(
    wolf_group,
    mean_negative_intensity_posts,
    sd_negative_intensity_posts,
    mean_antagonistic_posts,
    sd_antagonistic_posts
  ) %>%
  tidyr::pivot_longer(
    cols = -wolf_group,
    names_to = c("stat", "post_type"),
    names_pattern = "(mean|sd)_(.*)_posts",
    values_to = "value"
  ) %>%
  tidyr::pivot_wider(
    names_from = stat,
    values_from = value
  ) %>%
  dplyr::mutate(
    post_type = dplyr::recode(
      post_type,
      negative_intensity = "Negative-intensity posts",
      antagonistic = "Antagonistic posts"
    ),
    post_type = factor(
      post_type,
      levels = c("Negative-intensity posts", "Antagonistic posts")
    )
  )

p_negative_antagonistic_posts <- ggplot(
  negative_antagonistic_plot_data,
  aes(
    x = wolf_group,
    y = mean,
    fill = post_type
  )
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7
  ) +
  geom_errorbar(
    aes(
      ymin = pmax(mean - sd, 0),
      ymax = mean + sd
    ),
    position = position_dodge(width = 0.8),
    width = 0.1,
    linewidth = 0.8
  ) +
  scale_fill_manual(
    values = c(
      "Negative-intensity posts" = "coral1",
      "Antagonistic posts" = "black"
    )
  ) +
  scale_y_continuous(labels = scales::comma) +
  labs(
    title = "Mean Number of Negative and Antagonistic Posts by Group",
    x = NULL,
    y = "Mean number of posts per account",
    fill = NULL
  ) +
  theme_wolves() +
  theme(
    legend.position = "bottom"
  )

p_negative_antagonistic_posts
```

```{r}
negative_antagonistic_plot_data <- style_summary %>%
  dplyr::select(
    wolf_group,
    mean_negative_intensity_posts,
    sd_negative_intensity_posts,
    mean_antagonistic_posts,
    sd_antagonistic_posts
  ) %>%
  tidyr::pivot_longer(
    cols = -wolf_group,
    names_to = c("stat", "post_type"),
    names_pattern = "(mean|sd)_(.*)_posts",
    values_to = "value"
  ) %>%
  tidyr::pivot_wider(
    names_from = stat,
    values_from = value
  ) %>%
  dplyr::mutate(
    post_type = dplyr::recode(
      post_type,
      negative_intensity = "Negative-intensity posts",
      antagonistic = "Antagonistic posts"
    ),
    post_type = factor(
      post_type,
      levels = c(
        "Negative-intensity posts",
        "Antagonistic posts"
      )
    )
  )


p_negative_antagonistic_posts <- ggplot(
  negative_antagonistic_plot_data,
  aes(
    x = wolf_group,
    y = mean,
    fill = wolf_group
  )
) +
  geom_col(
    width = 0.65
  ) +
  geom_errorbar(
    aes(
      ymin = pmax(mean - sd, 0),
      ymax = mean + sd
    ),
    width = 0.1,
    linewidth = 0.8
  ) +
  facet_wrap(
    ~ post_type,
    scales = "free_y"
  ) +
  scale_fill_manual(values = group_colors) +
  scale_y_continuous(labels = scales::comma) +
  labs(
    title = "Mean Number of Negative and Antagonistic Posts by Group",
    x = NULL,
    y = "Mean number of posts per account",
    fill = NULL
  ) +
  theme_wolves() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 20, hjust = 1)
  )

p_negative_antagonistic_posts
```

###### ANOVA

```{r}
# Account-level dataset for ANOVA
negative_antagonistic_anova_data <- negativity_analysis %>%
  dplyr::mutate(
    lacracao_matches = dplyr::coalesce(lacracao_matches, 0),
    compound_sentiment = as.numeric(compound_sentiment),
    
    has_negative_intensity = compound_sentiment < 0,
    has_antagonistic_match = lacracao_matches >= 1
  ) %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    n_posts = dplyr::n(),
    
    count_negative_intensity_posts = sum(has_negative_intensity, na.rm = TRUE),
    count_antagonistic_posts = sum(has_antagonistic_match, na.rm = TRUE),
    
    ratio_negative_intensity_posts =
      100 * count_negative_intensity_posts / n_posts,
    ratio_antagonistic_posts =
      100 * count_antagonistic_posts / n_posts,
    
    .groups = "drop"
  ) %>%
  dplyr::left_join(
    nodes_grouped %>%
      dplyr::select(author, wolf_group),
    by = "author"
  ) %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::mutate(
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")
    )
  )
```

```{r}
anova_negative_intensity_posts <- aov(
  count_negative_intensity_posts ~ wolf_group,
  data = negative_antagonistic_anova_data
)

anova_antagonistic_posts <- aov(
  count_antagonistic_posts ~ wolf_group,
  data = negative_antagonistic_anova_data
)

# Tidy results
anova_negative_intensity_posts_tidy <- broom::tidy(anova_negative_intensity_posts)
anova_antagonistic_posts_tidy <- broom::tidy(anova_antagonistic_posts)

# Eta squared
anova_negative_intensity_posts_eta <- eta_squared_from_aov(anova_negative_intensity_posts)
anova_antagonistic_posts_eta <- eta_squared_from_aov(anova_antagonistic_posts)

# Inspect
summary(anova_negative_intensity_posts)
anova_negative_intensity_posts_tidy
anova_negative_intensity_posts_eta

summary(anova_antagonistic_posts)
anova_antagonistic_posts_tidy
anova_antagonistic_posts_eta
```


```{r}
# Plot domain category usage
p_domain_usage <- ggplot(
  domain_usage_plot_data,
  aes(
    x = measure,
    y = value,
    fill = wolf_group
  )
) +
  geom_col(
    position = position_dodge(width = 0.75),
    width = 0.65
  ) +
  facet_wrap(
    ~ measure,
    scales = "free_y",
    nrow = 1
  ) +
  scale_fill_manual(values = group_colors) +
  scale_y_continuous(
    labels = function(x) {
      dplyr::case_when(
        max(x, na.rm = TRUE) <= 100 ~ paste0(round(x, 1), "%"),
        TRUE ~ scales::comma(x)
      )
    },
    expand = expansion(mult = c(0, 0.08))
  ) +
  labs(
    title = "Media Domain Usage by Group",
    subtitle = "Mainstream and hyper-partisan values use each group’s total domain references as the baseline",
    x = NULL,
    y = NULL,
    fill = NULL
  ) +
  theme_wolves() +
  theme(
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text = element_text(size = 28, face = "bold"),
    plot.title = element_text(size = 34, face = "bold"),
    plot.subtitle = element_text(size = 28)
  )

p_domain_usage
```

```{r}
ggsave(
  filename = file.path(output_path, "domain_usage_by_group.png"),
  plot = p_domain_usage,
  width = 7,
  height = 4,
  units = "in",
  dpi = 300,
  bg = "white"
)
```

###Ideology

```{r}
# ----------------------------
# Media ideological scores
# ----------------------------
media_ideology_scores <- tibble::tribble(
  ~news_outlet, ~domain_key, ~ideological_score, ~audience_leaning,
  "Diário do Centro do Mundo", "diariodocentrodomundo", -0.20, "left",
  "Brasil 247", "brasil247", -0.18, "left",
  "Folha de S. Paulo", "folha", -0.09, "left",
  "Fórum", "forum", -0.09, "left",
  "Brasil de Fato", "brasildefato", -0.08, "left",
  "BBC Brasil", "bbc", -0.05, "not_partisan",
  "G1", "g1globo", -0.04, "not_partisan",
  "Globo", "globo", -0.02, "not_partisan",
  "O Povo", "opovo", -0.02, "not_partisan",
  "O Globo", "ogloboglobo", -0.02, "not_partisan",
  "UOL", "uol", -0.01, "not_partisan",
  "O Estado de S. Paulo", "estadao", -0.01, "not_partisan",
  "Metrópoles", "metropoles", -0.01, "not_partisan",
  "CNN Brasil", "cnnbrasil", 0.00, "not_partisan",
  "Poder 360", "poder360", 0.03, "not_partisan",
  "Band", "band", 0.04, "not_partisan",
  "SBT", "sbt", 0.06, "not_partisan",
  "R7", "r7", 0.07, "not_partisan",
  "Record TV", "recordtv", 0.11, "not_partisan",
  "Jovem Pan", "jovempan", 0.16, "right",
  "Gazeta do Povo", "gazetadopovo", 0.18, "right",
  "Oeste", "revistaoeste", 0.22, "right",
  "O Antagonista", "oantagonista", 0.23, "right",
  "Jornal da Cidade Online", "jornaldacidadeonline", 0.39, "right"
) %>%
  dplyr::mutate(
    domain_key = clean_domain_key(domain_key),
    audience_leaning = factor(
      audience_leaning,
      levels = c("left", "not_partisan", "right")
    )
  )

media_ideology_scores
```

```{r}
# ----------------------------
# Prepare account-domain long data
# ----------------------------
domain_ideology_long <- account_by_media_domain_counts %>%
  tidyr::pivot_longer(
    cols = -author,
    names_to = "domain",
    values_to = "n"
  ) %>%
  dplyr::mutate(
    domain_key = clean_domain_key(domain)
  ) %>%
  dplyr::inner_join(
    media_ideology_scores %>%
      dplyr::distinct(domain_key, .keep_all = TRUE),
    by = "domain_key"
  ) %>%
  dplyr::left_join(
    nodes_grouped %>%
      dplyr::select(author, wolf_group),
    by = "author"
  ) %>%
  dplyr::filter(!is.na(wolf_group))

# ----------------------------
# Account-level ideology summary
# ----------------------------
domain_ideology_author_summary <- domain_ideology_long %>%
  dplyr::group_by(author, wolf_group) %>%
  dplyr::summarise(
    total_domain_mentions = sum(n, na.rm = TRUE),
    
    left_mentions = sum(n[audience_leaning == "left"], na.rm = TRUE),
    not_partisan_mentions = sum(n[audience_leaning == "not_partisan"], na.rm = TRUE),
    right_mentions = sum(n[audience_leaning == "right"], na.rm = TRUE),
    
    weighted_ideological_score = dplyr::if_else(
      total_domain_mentions > 0,
      sum(ideological_score * n, na.rm = TRUE) / total_domain_mentions,
      NA_real_
    ),
    
    share_left = dplyr::if_else(
      total_domain_mentions > 0,
      left_mentions / total_domain_mentions,
      NA_real_
    ),
    share_not_partisan = dplyr::if_else(
      total_domain_mentions > 0,
      not_partisan_mentions / total_domain_mentions,
      NA_real_
    ),
    share_right = dplyr::if_else(
      total_domain_mentions > 0,
      right_mentions / total_domain_mentions,
      NA_real_
    ),
    
    .groups = "drop"
  )

# ----------------------------
# Group-level ideology summary
# ----------------------------
domain_ideology_summary <- domain_ideology_author_summary %>%
  dplyr::group_by(wolf_group) %>%
  dplyr::summarise(
    n_accounts = dplyr::n_distinct(author),
    n_accounts_with_matched_domains = sum(total_domain_mentions > 0, na.rm = TRUE),
    
    # Total number of matched domain mentions in media_ideology_scores
    total_domain_mentions = sum(total_domain_mentions, na.rm = TRUE),
    
    # Raw category totals
    left_mentions = sum(left_mentions, na.rm = TRUE),
    not_partisan_mentions = sum(not_partisan_mentions, na.rm = TRUE),
    right_mentions = sum(right_mentions, na.rm = TRUE),
    
    # Group-level weighted ideological score:
    # sum(score * mentions) / total matched mentions in the group
    average_ideological_score = sum(
      weighted_ideological_score * total_domain_mentions,
      na.rm = TRUE
    ) / total_domain_mentions,
    
    # SD of account-level weighted ideological scores
    sd_ideological_score = sd(
      weighted_ideological_score,
      na.rm = TRUE
    ),
    
    # Category averages using total group mentions as baseline
    average_left = left_mentions / total_domain_mentions,
    average_not_partisan = not_partisan_mentions / total_domain_mentions,
    average_right = right_mentions / total_domain_mentions,
    
    # SDs of account-level category shares
    sd_left = sd(share_left, na.rm = TRUE),
    sd_not_partisan = sd(share_not_partisan, na.rm = TRUE),
    sd_right = sd(share_right, na.rm = TRUE),
    
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    dplyr::across(
      c(
        average_left,
        average_not_partisan,
        average_right,
        sd_left,
        sd_not_partisan,
        sd_right
      ),
      ~ 100 * .x
    )
  )

domain_ideology_summary
```

### Plot ideological domain usage by group

```{r}
# ----------------------------
# Summarise domain mentions by group and outlet
# ----------------------------

domain_ideology_plot_summary <- domain_ideology_long %>%
  dplyr::group_by(
    wolf_group,
    news_outlet,
    domain_key,
    ideological_score,
    audience_leaning
  ) %>%
  dplyr::summarise(
    domain_mentions = sum(n, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  dplyr::group_by(wolf_group) %>%
  dplyr::mutate(
    total_domain_mentions_group = sum(domain_mentions, na.rm = TRUE),
    share_of_group_mentions = domain_mentions / total_domain_mentions_group,
    pct_of_group_mentions = 100 * share_of_group_mentions
  ) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(ideological_score) %>%
  dplyr::mutate(
    news_outlet_ordered = factor(
      news_outlet,
      levels = media_ideology_scores %>%
        dplyr::arrange(ideological_score) %>%
        dplyr::pull(news_outlet)
    )
  )

# Inspect summary object
domain_ideology_plot_summary

# ----------------------------
# Plot
# ----------------------------

p_domain_ideology_baseline <- ggplot(
  domain_ideology_plot_summary,
  aes(
    x = news_outlet_ordered,
    y = pct_of_group_mentions,
    fill = audience_leaning
  )
) +
  geom_col(width = 0.75) +
  facet_wrap(
    ~ wolf_group,
    ncol = 1,
    scales = "free_y"
  ) +
  scale_fill_manual(
    values = c(
      "left" = "darkred",
      "not_partisan" = "grey60",
      "right" = "navyblue"
    ),
    labels = c(
      "left" = "Left",
      "not_partisan" = "Not partisan",
      "right" = "Right"
    )
  ) +
  scale_x_discrete(
    labels = function(x) stringr::str_wrap(x, width = 12)
  ) +
  scale_y_continuous(
    labels = function(x) paste0(round(x, 1), "%"),
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(
    title = "Use of Media Domains by Audience Ideological Leaning",
    subtitle = "Each outlet's value is calculated as a share of all matched domain mentions within each group",
    x = "Media outlet, ordered by audience ideological score",
    y = "Share of group's matched domain mentions",
    fill = NULL
  ) +
  theme_wolves() +
  theme(
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.text.x = element_text(
      angle = 45,
      hjust = 1,
      size = 18
    ),
    axis.text.y = element_text(size = 24),
    axis.title.x = element_text(size = 26),
    axis.title.y = element_text(size = 26),
    plot.title = element_text(size = 34, face = "bold"),
    plot.subtitle = element_text(size = 22),
    strip.text = element_text(size = 28, face = "bold")
  )

p_domain_ideology_baseline
```

```{r}
ggsave(
  filename = file.path(output_path, "media_domain_ideology_by_group.png"),
  plot = p_domain_ideology_baseline,
  width = 10,
  height = 7,
  units = "in",
  dpi = 300,
  bg = "white"
)
```


## Domain Analysis

```{r}
mainstream_domains <- c("aosfatos", "band", "bbc", "bbccouk", "bbcin", "buzzfeed", "clarin", "cnn", "cnnbrasil", "correiobraziliense", "dailymailcouk", "eldiarioes", "elpais", "elpaiscomuy", "estadao", "exame", "extraglobo", "folha", "folha1", "g1globo", "gazetadopovo", "globo", "globo", "huffpost", "huffpostbrasil", "independentcouk", "infomoney", "istoedinheiro", "istoe", "lemondefr", "metropolenoticias", "nexojornal", "noticiasuol", "nytimes", "ogloboglobo", "poder360", "r7", "reuters", "sbt", "sbtinterior", "sbtnews", "telegraphcouk", "terra", "theguardian", "uol", "valor", "washingtonpost", "wsj", "yahoo")

hyper_partisan_domains <- c("agoranoticiasbrasil", "aliadosbrasil", "brasilsemmedo", "capixabaempregos", "cartacapital", "esquerdadiario", "esquerdaonline", "financasbrasil", "intercept", "jacobin", "jornaldacidadeonline", "jovempan", "mbl", "mblnews", "midianinja", "mises", "noticiasdebrasilia", "novaiguacu24h", "oantagonismo", "oantagonista", "opiniaoes", "pensandodireita", "plenonews", "renovamidia", "revistaonline", "revistaoeste", "romanews", "tercalivre", "terrabrasilnoticias", "theintercept", "veja", "vejario", "vejasp")

party_domains <- c("cstpsol", "democratas", "mulheresrepublicanas10", "novo", "novonacamara", "pcdob", "pcdobba", "pcdobnacamara", "pdt", "pdtnacamara", "pl22", "podemos", "pps", "prb10", "prb10rj", "prb10sp", "prbmg10", "prbmulher10", "prbnacamara", "progressistas", "pros", "pros90", "prosnacamara", "psb40", "psb40bahia", "psbnacamara", "psc", "psd", "psdmg", "psdb", "psdbnacamara", "psdcamara", "pslsp", "psol", "psol50", "psol50sp", "psolbemviver", "psolcamarasp", "psolcarioca", "psolnacamara", "psolniteroi", "psolsaude", "psolsemente", "pt", "ptalagoas", "ptassembleiasp", "ptbahia", "ptb", "ptbnacamara", "ptcarioca", "ptceara", "ptmt", "ptnaalep", "ptnacamara", "ptnosenado", "ptpaulista", "ptpr", "ptsaopaulo", "ptsc", "ptsul", "pv", "republicanos10", "republicanos1010", "republicanos10mg", "republicanos10nacamara", "republicanos10riopreto", "republicanos10sp", "solidariedaderj")

radio_domains <- c("94fm", "anchorfm", "bandnewsfm", "bandnewsfmcuritiba", "bandnewsfmrio", "cbncaruaru", "cbncuritiba", "cbnlondrina", "cbnmaringa", "cbnrecife", "cbnvitoria", "metropolitanoonline", "radiobandeirantes", "radiocabiuna", "radiocacula", "radiocaxias", "radioclubfmnet", "radiocomunitariaclubefm", "radioconvencao", "radiocorredor", "radiocostaverdefm", "radiocruzdemalta", "radiofmz", "radiofolhabv", "radiogeracao", "radioglobocampogrande", "radioguaratuba", "radiohora", "radioiara", "radiointegracaoam1180", "radioipiranga", "radiometropole", "radionereuramos", "radionovaprogresso", "radiopanoramicafm", "radiopeaobrasil", "radioprata", "radiosanfm", "radiosantacruz", "radiosaoluiz", "radiosaopedrense", "radioschroederfm", "radiosoledade", "radiotaquara", "radioterena", "radiotucunare", "radioturmalina", "radiouniversitariafm", "radioveracruz", "radiowebcp")

clean_domain_key <- function(x) {
  x %>%
    stringi::stri_trans_general(id = "Latin-ASCII") %>%
    stringr::str_to_lower() %>%
    stringr::str_replace_all("^https?://", "") %>%
    stringr::str_replace_all("^www\\.", "") %>%
    stringr::str_replace_all("[^a-z0-9]", "") %>%
    stringr::str_trim()
}

classify_domain <- function(domain) {
  domain_key <- clean_domain_key(domain)
  dplyr::case_when(
    domain_key %in% mainstream_domains ~ "Mainstream",
    domain_key %in% hyper_partisan_domains ~ "Hyper-partisan",
    domain_key %in% party_domains ~ "Party domains",
    domain_key %in% radio_domains ~ "Radio",
    TRUE ~ "Others"
  )
}
```

```{r}
# Domain usage summaries by account and wolf status
# Convert account_by_media_domain_counts into long format
account_domain_long_for_usage <- account_by_media_domain_counts %>%
  as.data.frame(check.names = FALSE) %>%
  tidyr::pivot_longer(
    cols = -author,
    names_to = "domain",
    values_to = "n_domain_references"
  ) %>%
  dplyr::filter(n_domain_references > 0) %>%
  dplyr::mutate(
    domain_category = classify_domain(domain)
  )

# Account-level post counts from df_fb
account_post_counts <- df_fb %>%
  dplyr::count(author, name = "n_posts")


# Account-level domain usage table
domain_usage_author <- nodes_breakdown %>%
  dplyr::select(author, is_wolf) %>%
  dplyr::left_join(account_post_counts, by = "author") %>%
  dplyr::left_join(
    account_domain_long_for_usage %>%
      dplyr::group_by(author) %>%
      dplyr::summarise(
        n_domains_references = sum(n_domain_references, na.rm = TRUE),
        n_unique_domain_references = dplyr::n_distinct(domain),
        mainstream_domains = sum(
          n_domain_references[domain_category == "Mainstream"],
          na.rm = TRUE
        ),
        hyper_partisan_domains = sum(
          n_domain_references[domain_category == "Hyper-partisan"],
          na.rm = TRUE
        ),
        party_domains = sum(
          n_domain_references[domain_category == "Party domains"],
          na.rm = TRUE
        ),
        .groups = "drop"
      ),
    by = "author"
  ) %>%
  dplyr::mutate(
    dplyr::across(
      c(
        n_posts,
        n_domains_references,
        n_unique_domain_references,
        mainstream_domains,
        hyper_partisan_domains,
        party_domains
      ),
      ~ dplyr::coalesce(.x, 0)
    ),
    ratio_domains_references = 100 * n_domains_references / n_posts,
    ratio_mainstream = 100 * mainstream_domains / n_posts,
    ratio_hyper_partisan = 100 * hyper_partisan_domains / n_posts,
    ratio_party_domains = 100 * party_domains / n_posts
  )

# Inspect
glimpse(domain_usage_author)
```

#### Group Comparison

```{r}
domain_usage_group <- domain_usage_author %>%
  dplyr::mutate(
    wolf_group = dplyr::case_when(
      is_wolf == 1 ~ "Wolves",
      is_wolf == 0 ~ "All other parliamentarians",
      TRUE ~ NA_character_
    )
  ) %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::group_by(wolf_group) %>%
  dplyr::summarise(
    n_members = dplyr::n(),
    # Posts
    total_posts = sum(n_posts, na.rm = TRUE),
    mean_posts = mean(n_posts, na.rm = TRUE),
    sd_posts = sd(n_posts, na.rm = TRUE),
    # Domain references
    total_domain_references = sum(n_domains_references, na.rm = TRUE),
    mean_domain_references = mean(n_domains_references, na.rm = TRUE),
    sd_domain_references = sd(n_domains_references, na.rm = TRUE),
    # Unique domains
    total_unique_domain_references = sum(n_unique_domain_references, na.rm = TRUE),
    # Domain references per 100 posts
    ratio_domain_references = 100 * total_domain_references / total_posts,
    
    # Account-level average of the ratio
    mean_ratio_domain_references = mean(
      ratio_domains_references, na.rm = TRUE),
    sd_ratio_domain_references = sd(ratio_domains_references, na.rm = TRUE),
    .groups = "drop") %>%
  tidyr::pivot_longer(
    cols = -wolf_group,
    names_to = "measure",
    values_to = "value"
  ) %>%
  tidyr::pivot_wider(
    names_from = wolf_group,
    values_from = value
  )

# Format
domain_usage_group_formatted <- domain_usage_group %>%
  dplyr::mutate(
    dplyr::across(
      c(`All other parliamentarians`, Wolves),
      ~ dplyr::case_when(
        # Count variables: no decimals
        measure %in% c(
          "n_members",
          "total_posts",
          "total_domain_references",
          "total_unique_domain_references"
        ) ~ round(.x, 0),

        # Means, SDs, and ratios: two decimals
        TRUE ~ round(.x, 2)
      )
    )
  )

# Inspect
domain_usage_group_formatted
```

#### Category Comparison

```{r}
# Create account-level post counts with no linked domain
posts_no_domains_author <- df_fb %>%
  dplyr::mutate(
    has_linked_domain = !is.na(domain) & domain != ""
  ) %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    n_posts_no_domains = sum(!has_linked_domain, na.rm = TRUE),
    .groups = "drop"
  )

# Group-level comparison
domain_category_counts <- domain_usage_author %>%
  dplyr::left_join(
    posts_no_domains_author,
    by = "author"
  ) %>%
  dplyr::mutate(
    n_posts_no_domains = dplyr::coalesce(n_posts_no_domains, 0),
    
    ratio_posts_no_domains = 100 * n_posts_no_domains / n_posts,
    
    wolf_group = dplyr::case_when(
      is_wolf == 1 ~ "Wolves",
      is_wolf == 0 ~ "All other parliamentarians",
      TRUE ~ NA_character_
    )
  ) %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::group_by(wolf_group) %>%
  dplyr::summarise(
    # Group size and activity
    n_members = dplyr::n(),
    total_posts = sum(n_posts, na.rm = TRUE),
    mean_posts = mean(n_posts, na.rm = TRUE),
    sd_posts = sd(n_posts, na.rm = TRUE),
    
    # Hyper-partisan domains
    mean_hyperpartisan_references = mean(hyper_partisan_domains, na.rm = TRUE),
    ratio_hyperpartisan_references =
      100 * sum(hyper_partisan_domains, na.rm = TRUE) / sum(n_posts, na.rm = TRUE),
    mean_ratio_hyperpartisan_references =
      mean(ratio_hyper_partisan, na.rm = TRUE),
    
    # Mainstream domains
    mean_mainstream_references = mean(mainstream_domains, na.rm = TRUE),
    ratio_mainstream_references =
      100 * sum(mainstream_domains, na.rm = TRUE) / sum(n_posts, na.rm = TRUE),
    mean_ratio_mainstream_references =
      mean(ratio_mainstream, na.rm = TRUE),
    
    # Party domains
    mean_partydomains_references = mean(party_domains, na.rm = TRUE),
    ratio_partydomains_references =
      100 * sum(party_domains, na.rm = TRUE) / sum(n_posts, na.rm = TRUE),
    mean_ratio_partydomains_references =
      mean(ratio_party_domains, na.rm = TRUE),
    
    # Posts with no linked domain
    mean_posts_no_domains = mean(n_posts_no_domains, na.rm = TRUE),
    ratio_posts_no_domains =
      100 * sum(n_posts_no_domains, na.rm = TRUE) / sum(n_posts, na.rm = TRUE),
    mean_ratio_posts_no_domains =
      mean(ratio_posts_no_domains, na.rm = TRUE),
    
    .groups = "drop"
  ) %>%
  tidyr::pivot_longer(
    cols = -wolf_group,
    names_to = "measure",
    values_to = "value"
  ) %>%
  tidyr::pivot_wider(
    names_from = wolf_group,
    values_from = value
  ) %>%
  dplyr::mutate(
    dplyr::across(
      c(`All other parliamentarians`, Wolves),
      ~ dplyr::case_when(
        measure %in% c(
          "n_members",
          "total_posts"
        ) ~ round(.x, 0),
        TRUE ~ round(.x, 2)
      )
    )
  )

# Inspect
domain_category_counts
```

##### ANOVA

```{r}
# ANOVAs: DOMAIN REFERENCES BY GROUP
eta_squared_from_aov <- function(model) {
  effectsize::eta_squared(model, partial = FALSE)
}

# Prepare data
domain_usage_anova <- domain_usage_author %>%
  mutate(
    wolf_group = case_when(
      is_wolf == 1 ~ "Wolves",
      is_wolf == 0 ~ "All other parliamentarians",
      TRUE ~ NA_character_
    ),
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")
    )
  ) %>%
  filter(!is.na(wolf_group))


############################################
#### A. Mean domain references by group  ####
############################################
# Raw count of domain references
anova_domain_references <- aov(
  n_domains_references ~ wolf_group,
  data = domain_usage_anova
)

anova_domain_references_tidy <- broom::tidy(anova_domain_references)
anova_domain_references_eta <- eta_squared_from_aov(anova_domain_references)

# Results
summary(anova_domain_references)
anova_domain_references_tidy
anova_domain_references_eta


# Optional: use the rate per 100 posts instead of raw counts
# anova_ratio_domain_references <- aov(
#   ratio_domains_references ~ wolf_group,
#   data = domain_usage_anova
# )
# 
# anova_ratio_domain_references_tidy <- broom::tidy(anova_ratio_domain_references)
# anova_ratio_domain_references_eta <- eta_squared_from_aov(anova_ratio_domain_references)
# 
# # Results
# summary(anova_ratio_domain_references)
# anova_ratio_domain_references_tidy
# anova_ratio_domain_references_eta
```

```{r}
# Mean domain references by category and group 
domain_category_anova_long <- domain_usage_anova %>%
  select(
    author,
    wolf_group,
    mainstream_domains,
    hyper_partisan_domains,
    ratio_mainstream,
    ratio_hyper_partisan
  ) %>%
  pivot_longer(
    cols = c(mainstream_domains, hyper_partisan_domains),
    names_to = "domain_category",
    values_to = "n_category_references"
  ) %>%
  mutate(
    domain_category = recode(
      domain_category,
      mainstream_domains = "Mainstream media",
      hyper_partisan_domains = "Hyper-partisan media"
    ),
    domain_category = factor(
      domain_category,
      levels = c("Mainstream media", "Hyper-partisan media")))

# Two-way ANOVA:
# - Does usage differ by group?
# - Does usage differ by category?
# - Does the category difference vary by group?
anova_category_group <- aov(
  n_category_references ~ wolf_group * domain_category,
  data = domain_category_anova_long)

anova_category_group_tidy <- broom::tidy(anova_category_group)
anova_category_group_eta <- eta_squared_from_aov(anova_category_group)

# Results
summary(anova_category_group)
anova_category_group_tidy
anova_category_group_eta
```

##### Plots

```{r}
domain_references_summary <- domain_usage_author %>%
  dplyr::mutate(
    wolf_group = dplyr::case_when(
      is_wolf == 1 ~ "Wolves",
      is_wolf == 0 ~ "All other parliamentarians",
      TRUE ~ NA_character_
    ),
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")
    )
  ) %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::group_by(wolf_group) %>%
  dplyr::summarise(
    group_mean_domain_references = mean(n_domains_references, na.rm = TRUE),
    group_sd_domain_references = sd(n_domains_references, na.rm = TRUE),
    .groups = "drop"
  )

p_mean_domain_references <- ggplot(
  domain_references_summary,
  aes(
    x = wolf_group,
    y = group_mean_domain_references,
    fill = wolf_group
  )
) +
  geom_col(width = 0.65) +
  geom_errorbar(
    aes(
      ymin = pmax(group_mean_domain_references - group_sd_domain_references, 0),
      ymax = group_mean_domain_references + group_sd_domain_references
    ),
    width = 0.1,
    linewidth = 0.8
  ) +
  scale_fill_manual(values = group_colors) +
  scale_y_continuous(labels = scales::comma) +
  labs(
    title = "Mean Number of Domain References by Group",
    x = NULL,
    y = ""
  ) +
  theme_wolves() +
  theme(
    legend.position = "none"
  )

p_mean_domain_references
```

```{r}
#### Plot: Mean domain references by category and group
domain_category_summary <- domain_usage_author %>%
  dplyr::mutate(
    wolf_group = dplyr::case_when(
      is_wolf == 1 ~ "Wolves",
      is_wolf == 0 ~ "All other parliamentarians",
      TRUE ~ NA_character_
    ),
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")
    )
  ) %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::select(
    author,
    wolf_group,
    mainstream_domains,
    hyper_partisan_domains,
  ) %>%
  tidyr::pivot_longer(
    cols = c(
      mainstream_domains,
      hyper_partisan_domains,
    ),
    names_to = "domain_category",
    values_to = "n_references"
  ) %>%
  dplyr::mutate(
    domain_category = dplyr::recode(
      domain_category,
      mainstream_domains = "Mainstream media",
      hyper_partisan_domains = "Hyper-partisan media"
    ),
    domain_category = factor(
      domain_category,
      levels = c(
        "Mainstream media",
        "Hyper-partisan media"))) %>%
  dplyr::group_by(wolf_group, domain_category) %>%
  dplyr::summarise(
    group_mean_references = mean(n_references, na.rm = TRUE),
    group_sd_references = sd(n_references, na.rm = TRUE),
    .groups = "drop")

p_mean_domain_categories <- ggplot(
  domain_category_summary,
  aes(
    x = domain_category,
    y = group_mean_references,
    fill = wolf_group)) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.65
  ) +
  geom_errorbar(
    aes(
      ymin = pmax(group_mean_references - group_sd_references, 0),
      ymax = group_mean_references + group_sd_references
    ),
    position = position_dodge(width = 0.8),
    width = 0.1,
    linewidth = 0.8
  ) +
  scale_fill_manual(values = group_colors) +
  scale_y_continuous(labels = scales::comma) +
  labs(
    title = "Mean Number of Domain References by Category",
    x = NULL,
    y = "",
    fill = NULL
  ) +
  theme_wolves()

p_mean_domain_categories
```

```{r}
#### Save plots as PNG
dir.create(output_path, recursive = TRUE, showWarnings = FALSE)

ggplot2::ggsave(
  filename = file.path(output_path, "mean_domain_references_by_group.png"),
  plot = p_mean_domain_references,
  width = 8,
  height = 6,
  dpi = 300
)

ggplot2::ggsave(
  filename = file.path(output_path, "mean_domain_references_by_category.png"),
  plot = p_mean_domain_categories,
  width = 8,
  height = 5,
  dpi = 300
)
```
