---
title: "News and Domain Sharing Analysis"
subtitle: "Mapping Ideological Domains and the Factional Right-Wing Split"
output: 
  html_document:
    toc: true
    toc_depth: 3
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 7)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggrepel)
library(forcats)
library(tidyverse)
library(here)
library(ggalluvial)
library(igraph)
library(tibble)
library(sysfonts)
library(showtext)
library(ggalluvial)
font_add_google("EB Garamond", "EB Garamond")
showtext_auto()
```

# Data

```{r}
# Information about politicians
nodes_breakdown <- read_csv(
  here("_processed_data", "nodes_breakdown.csv"))

# Domain data
account_by_media_domain_counts <- read_rds(
  here("_processed_data", "account_by_media_domain_counts.rds"))

# Filtered dataset + GPT analysis
df_fb_election <- read_rds(
  here("_processed_data", "df_fb_election.rds"))

q12_domains  <- read_csv(
  here("_processed_data", "q1_q2_domains.csv"))
```

## 1. Introduction and Methodological Rationale
This document establishes the pipeline for evaluating the media sharing behavior of the Brazilian parliament. Rather than relying on individual-level averages—which obscure highly concentrated alternative networks—this approach maps the ecosystem structurally.

We evaluate domains across two dimensions:

Ideological Center of Gravity: The weighted average ideology of the legislators sharing the domain.

Exclusivity (Echo-Chamber Index): The standard deviation of those ideological scores. Lower variance indicates a highly isolated, exclusive user base.

Subsequently, we isolate the political right to evaluate a specific structural fracture: the divergence between the populist "wolves" and the institutional "non-wolves right." By calculating relative Attention Share budgets, we normalize for extreme group-size asymmetries and hyper-poster distortions, revealing a two-tiered media landscape.

## 2. Data Preparation and Hygiene
Before any statistical modeling, we must transform the wide sharing matrix into a long format. Crucially, we apply strict data hygiene filters. Social media APIs frequently log peer-to-peer retweets or shares of institutional pages as "domains." Failing to remove these conflates intra-parliamentary homophily with actual journalistic media consumption.

We apply an automated filter to remove active parliamentarians and a hardcoded list to remove URL shorteners, party handles, and mismatched legacy URLs.

```{r domain ideology}
# 1. Convert the wide matrix into a long dataframe
domain_long <- account_by_media_domain_counts %>%
  as.data.frame() %>%
  # Move the row names (the account handles) into a proper column
  rownames_to_column(var = "author") %>%
  # Pivot all domain columns into two columns: 'domain' and 'share_count'
  pivot_longer(
    cols = -author, 
    names_to = "domain", 
    values_to = "share_count"
  ) %>%
  # Filter out the zeroes immediately to save memory and processing time
  filter(share_count > 0)

# 2. Merge with legislator data and calculate ideological metrics
domain_ideology_summary <- domain_long %>%
  # Join only the necessary columns from nodes_breakdown
  inner_join(
    nodes_breakdown %>% select(author, party, ideology_2021), 
    by = "author"
  ) %>%
  group_by(domain) %>%
  summarise(
    total_shares = sum(share_count, na.rm = TRUE),
    
    # Weighted Mean
    weighted_mean_ideology = sum(share_count * ideology_2021, na.rm = TRUE) / total_shares,
    
    # Weighted Variance and Standard Deviation
    weighted_variance = sum(share_count * (ideology_2021 - weighted_mean_ideology)^2, na.rm = TRUE) / total_shares,
    weighted_sd_ideology = sqrt(weighted_variance),
    
    .groups = "drop"
  ) %>%
  # Filter out low-frequency domains to avoid artificial 0 standard deviations
  filter(total_shares >= 10) %>%
  # Sort by total shares descending for readability
  arrange(desc(total_shares))
```

```{r}
# 1. Define the dynamic exclusion list from known authors (lowercased for strict matching)
politician_handles <- tolower(unique(nodes_breakdown$author))

# 2. Hardcoded exclusion vector for mismatched handles, URL shorteners, and institutional pages
manual_exclusions <- c(
  "lpbraganca", "pedrolupion", "sandersonfederal", "gurgelrj", "marcelvanhattem", 
  "franciscojr", "deputadohugoleal", "evairdemelo", "charliesevangelista", "christinoaureo", 
  "jaquelinecassol", "osiresdamaso", "renataabreuoficial", "domingossavio", "leandre", 
  "joaoroma", "nereucrispim", "adrianaventura", "bilacpinto", "em", "capitaoaugusto",
  # "agriculturarsgovbr", "portaltanosite", 
  "blogdomarcosjunior", "gdia", "bitly", 
  # "republicanos10", "democratas", 
  "freianastacio"
)

# 3. Pivot and clean the base data
domain_long_clean <- account_by_media_domain_counts %>%
  as.data.frame() %>%
  rownames_to_column(var = "author") %>%
  pivot_longer(
    cols = -author, 
    names_to = "domain", 
    values_to = "share_count"
  ) %>%
  filter(share_count > 0) %>%
  # Automated filter
  filter(!tolower(domain) %in% politician_handles) %>%
  # Manual filter
  filter(!domain %in% manual_exclusions)
```

## 3. The 1D Baseline: Ideology, Frequency, and Dispersion
We first establish the ideological baseline for all shared domains across the entire parliament. We join the cleaned domain list with the nodes_breakdown metadata to calculate weighted means and standard deviations.

```{r}
domain_ideology_summary <- domain_long_clean %>%
  inner_join(
    nodes_breakdown %>% select(author, party, ideology_2021), 
    by = "author"
  ) %>%
  group_by(domain) %>%
  summarise(
    total_shares = sum(share_count, na.rm = TRUE),
    
    # Weighted Mean
    weighted_mean_ideology = sum(share_count * ideology_2021, na.rm = TRUE) / total_shares,
    
    # Weighted Variance and Standard Deviation
    weighted_variance = sum(share_count * (ideology_2021 - weighted_mean_ideology)^2, na.rm = TRUE) / total_shares,
    weighted_sd_ideology = sqrt(weighted_variance),
    
    .groups = "drop"
  ) %>%
  filter(total_shares >= 10) %>%
  arrange(desc(total_shares))
```

We visualize this distribution, utilizing horizontal jitter to expose density and highlighting domains with low standard deviation (high exclusivity).

```{r}
# Filter out low-N noise to prevent false variance signals
filtered_summary <- domain_ideology_summary %>%
  filter(total_shares >= 50)

# Isolate the top domains for clean labeling
top_domains <- filtered_summary %>%
  slice_max(order_by = total_shares, n = 50)

plot_1d_baseline <- ggplot(filtered_summary, aes(x = weighted_mean_ideology, y = total_shares)) +
  
  # Use position_jitter with a strict seed for reproducible point placement
  geom_point(
    aes(color = weighted_sd_ideology), 
    position = position_jitter(width = 0.03, height = 0, seed = 42),
    alpha = 0.8, size = 2.5
  ) +
  scale_y_log10(labels = scales::comma) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.4) +
  
  geom_text_repel(
  data = top_domains,
  aes(label = domain),
  family = "EB Garamond",
  size = 10,
  box.padding = 0.8,
  point.padding = 0.3,
  max.overlaps = Inf, 
  seed = 42) +
  
  scale_color_viridis_c(
    option = "plasma", 
    name = "Ideological Dispersion (SD)\nLow = Exclusive\nHigh = Cross-Partisan"
  ) +
  
  labs(
    title = "Media Domain Mapping: Ideology, Frequency, and Dispersion",
    subtitle = "Filtered for domains with ≥ 50 shares; top 50 most shared domains labeled.",
    x = "Ideological Center of Gravity (Left < 0 > Right)",
    y = "Total Shares (Log Scale)"
  ) +
  theme_minimal(base_family = "EB Garamond", base_size = 30) +
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = "gray30", margin = margin(b = 10)),
    legend.position = "right",
    panel.grid.minor = element_blank(),
    plot.background = element_rect(fill = "white", color = NA) # Ensure non-transparent background
  )

# Export in high definition
ggsave("figure1_domain_ideology_baseline.png", plot = plot_1d_baseline, width = 11, height = 8, dpi = 300)
print(plot_1d_baseline)
```

## 4. The Right-Wing Split: Attention Share & Media Diet Space
To test whether the populist "wolves" utilize a distinct alternative media infrastructure compared to the "non-wolves right," we subset the data.Because the non-wolves right is a much larger group, raw share counts and user prevalence metrics are statistically compromised by the base-rate fallacy. We resolve this by computing the Relative Attention Share. We treat each faction's total output as a "Media Diet Budget" ($B_f$) and calculate the percentage allocated to domain $d$:
$$ \text{Attention Share}_{d, f} = \frac{\text{Shares of } d \text{ by Faction } f}{B_f} \times 100 $$

```{r}
# Isolate the right wing
right_nodes <- nodes_breakdown %>% filter(ideology_2021 > 0)
right_shares_clean <- domain_long_clean %>%
  inner_join(right_nodes %>% select(author, is_wolf), by = "author")

# Calculate Total Media Output (The Denominators)
group_budgets <- right_shares_clean %>%
  group_by(is_wolf) %>%
  summarise(total_faction_shares = sum(share_count), .groups = "drop")

total_w_shares <- group_budgets %>% filter(is_wolf == 1) %>% pull(total_faction_shares)
total_nw_shares <- group_budgets %>% filter(is_wolf == 0) %>% pull(total_faction_shares)

# Compute Attention Share per Domain
media_diet_base <- right_shares_clean %>%
  group_by(is_wolf, domain) %>%
  summarise(domain_faction_shares = sum(share_count), .groups = "drop") %>%
  pivot_wider(names_from = is_wolf, values_from = domain_faction_shares, values_fill = 0, names_prefix = "shares_") %>%
  rename(nw_shares = shares_0, w_shares = shares_1) %>%
  mutate(
    pct_of_wolf_diet = (w_shares / total_w_shares) * 100,
    pct_of_nonwolf_diet = (nw_shares / total_nw_shares) * 100,
    total_volume = w_shares + nw_shares,
    diet_ratio = (pct_of_wolf_diet + 0.001) / (pct_of_nonwolf_diet + 0.001)
  ) %>%
  filter(total_volume >= 20)

# Inject Domain-Level Ideology and Exclusivity Metadata
media_diet_enriched <- media_diet_base %>%
  left_join(
    domain_ideology_summary %>% 
      select(domain, weighted_mean_ideology, weighted_sd_ideology),
    by = "domain"
  )
```

```{r}
media_diet_enriched %>%
  summarise(
    n_domains = n(),
    zero_wolf = sum(pct_of_wolf_diet == 0),
    zero_nonwolf = sum(pct_of_nonwolf_diet == 0),
    zero_either = sum(
      pct_of_wolf_diet == 0 |
      pct_of_nonwolf_diet == 0
    ),
    positive_both = sum(
      pct_of_wolf_diet > 0 &
      pct_of_nonwolf_diet > 0
    )
  )
```

Final Visualization: The Two-Tiered Media Landscape
We plot the media diet space, rendering the domains as points colored by their underlying ideological score and adjusted for transparency based on exclusivity.

```{r}
positive_attention <- c(
  media_diet_enriched$pct_of_wolf_diet[
    media_diet_enriched$pct_of_wolf_diet > 0
  ],
  media_diet_enriched$pct_of_nonwolf_diet[
    media_diet_enriched$pct_of_nonwolf_diet > 0
  ]
)

summary(positive_attention)

quantile(
  positive_attention,
  probs = c(0, .01, .05, .10, .25, .50, .75, .90, .95, .99, 1)
)

sigma = 0.0003
```
```{r}
plot_diet_space <- ggplot(
  media_diet_enriched,
  aes(x = pct_of_nonwolf_diet, y = pct_of_wolf_diet)
) +
  
  # 45-degree identity line (Equal structural attention)
  geom_abline(
    intercept = 0,
    slope = 1,
    linetype = "dashed",
    color = "gray60"
  ) +
  
  geom_point(
    aes(
      color = weighted_mean_ideology,
      size = total_volume,
      alpha = 1 - weighted_sd_ideology
    )
  ) +
  
  scale_x_log10(labels = function(x) paste0(x, "%")) +
  scale_y_log10(labels = function(x) paste0(x, "%")) +
  
  scale_color_gradient2(
    low = "steelblue", 
    mid = "gray90", 
    high = "darkred", 
    midpoint = 0,
    name = "Domain Ideology\nScore"
  ) +
  
  scale_alpha_continuous(
    name = "Domain Exclusivity\n(1 - SD)",
    range = c(0.4, 1)
  ) +
  
  scale_size_continuous(
    name = "Total Combined Shares",
    labels = scales::comma
  ) +
  
  geom_text_repel(
    data = media_diet_enriched %>%
      filter(
        diet_ratio > 3.5 |
        diet_ratio < 0.25 |
        total_volume > 1500
      ),
    aes(label = domain),
    family = "EB Garamond",
    size = 10,
    box.padding = 0.4,
    max.overlaps = 25,
    seed = 42
  ) +
  
  labs(
    title = "The Ideological Geography of the Right-Wing Media Diet",
    subtitle = "Color maps the underlying domain ideology; transparency highlights echo-chamber exclusivity.",
    x = "Share of Non-Wolves Right Media Diet (Log Scale)",
    y = "Share of Wolf Media Diet (Log Scale)"
  ) +
  
  theme_minimal(base_family = "EB Garamond", base_size = 30) +
  
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    plot.background = element_rect(
      fill = "white",
      color = NA
    )
  )

# Export in high definition
ggsave("figure2_rightwing_diet_split.png", plot = plot_diet_space, width = 11, height = 8, dpi = 300)
print(plot_diet_space)
```

### Analytical Interpretation

* **Tier 1 (The Mainstream Anchor):** Legacy media outlets (globo, folha, cnn) trace the diagonal dashed line. Because both the wolves and the non-wolves right allocate significant structural attention to these mainstream domains, an individual's average ideological diet score is anchored heavily toward the center.

* **Tier 2 (Parallel Echo Chambers):** When departing from the mainstream, the right bifurcates. Both factions retreat into deeply exclusive, intensely right-wing (dark red) sanctuaries, rendering tests for variance or exclusivity non-significant. However, their targets are mutually exclusive: the institutional non-wolves right relies heavily on mblnews (lower-right quadrant), while the populist wolves rely on a dense alternative network led by plenonews and revistaoeste (upper-left quadrant).


```{r}
# ==============================================================================
# STEP 5: Categorical Typologies for Domain Profiling
# ==============================================================================

# Define your thresholds based on the empirical distribution of your data
ideology_buffer <- 0.25      # Bandwidth for 'Center/Neutral' (-0.25 to +0.25)
sd_threshold <- 0.45         # Below this SD is considered 'Exclusive'
salience_threshold <- 100    # Minimum shares to be considered 'Core'

domain_typologies <- domain_ideology_summary %>%
  mutate(
    # 1. Partisanship (Left, Center, Right)
    cat_partisanship = case_when(
      weighted_mean_ideology < -ideology_buffer ~ "Left",
      weighted_mean_ideology > ideology_buffer ~ "Right",
      TRUE ~ "Center"
    ),
    
    # 2. Dispersion (Exclusive vs. Cross-Partisan)
    # Note: NA values in SD happen if a domain is shared by only 1 person. 
    # We default those to 'Exclusive'.
    cat_dispersion = case_when(
      weighted_sd_ideology < sd_threshold | is.na(weighted_sd_ideology) ~ "Exclusive",
      TRUE ~ "Cross-Partisan"
    ),
    
    # 3. Salience (Core vs. Niche)
    cat_salience = case_when(
      total_shares >= salience_threshold ~ "Core",
      TRUE ~ "Niche"
    ),
    
    # 4. Synthesize the final structural profile
    media_profile = paste(cat_partisanship, cat_dispersion, cat_salience, sep = " | ")
  )

# Generate a summary table of the ecosystem architecture
typology_summary <- domain_typologies %>%
  group_by(media_profile) %>%
  summarise(
    domain_count = n(),
    total_shares_in_profile = sum(total_shares),
    .groups = "drop"
  ) %>%
  arrange(desc(total_shares_in_profile))

# Print the summary table (useful for your markdown output)
knitr::kable(
  typology_summary, 
  caption = "Distribution of Media Profiles across the Information Ecosystem",
  format.args = list(big.mark = ",")
)
```

```{r}
# ==============================================================================
# APPENDIX TABLE: Distribution of Media Profiles
# ==============================================================================

# Generate a summary table of the ecosystem architecture
typology_summary <- domain_typologies %>%
  group_by(
    cat_partisanship,
    cat_dispersion,
    cat_salience,
    media_profile
  ) %>%
  summarise(
    domain_count = n(),
    total_shares_in_profile = sum(total_shares, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(total_shares_in_profile))

# Print the summary table for the RMarkdown output
knitr::kable(
  typology_summary, 
  caption = "Distribution of Media Profiles across the Information Ecosystem",
  format.args = list(big.mark = ",")
)
```
### Structural Asymmetry: The Absence of a Cross-Partisan Right

The cross-tabulation of Partisanship, Dispersion, and Salience yields 11 distinct media profiles out of a mathematically possible 12. The missing 12th category is not a data artifact; it is a critical empirical finding: **There are zero domains in the dataset that qualify as "Right | Cross-Partisan | Core."**

Structurally, the left and the center both maintain high-volume media spaces that successfully cross partisan boundaries (e.g., `Left | Cross-Partisan | Core` accounts for over 40,000 shares). Conversely, the right-wing media ecosystem operates as a rigidly isolated silo at its highest tier of volume. Every single high-salience right-wing domain is mathematically locked into the `Right | Exclusive | Core` category. 

This structural asymmetry proves that the institutional right and the far-right do not possess a shared, cross-cutting media vanguard comparable to the left. Instead, high-volume right-wing media consumption is fundamentally predicated on exclusivity.

```{r}
# ==============================================================================
# Alluvial Flow of the Media Ecosystem
# ==============================================================================
ggplot(typology_summary, aes(axis1 = cat_partisanship, 
                             axis2 = cat_dispersion, 
                             axis3 = cat_salience, 
                             y = total_shares_in_profile)) +
  
  # Set the flow colors based on partisanship to track where the left/right goes
  geom_alluvium(aes(fill = cat_partisanship), alpha = 0.7, width = 0.2) +
  
  # Draw the categorical pillars
  geom_stratum(width = 0.2, fill = "gray20", color = "white") +
  
  # Label the pillars
  geom_text(stat = "stratum", aes(label = after_stat(stratum)), color = "white", size = 3) +
  
  scale_fill_manual(values = c("Left" = "steelblue", "Center" = "gray70", "Right" = "darkred")) +
  scale_x_discrete(limits = c("Partisanship", "Dispersion", "Salience"), expand = c(0.15, 0.05)) +
  
  labs(
    title = "Structural Flow of Information: Ecosystem Typologies",
    subtitle = "Ribbon width represents total absolute shares.",
    y = "Total Shares",
    fill = "Partisan Origin"
  ) +
  theme_minimal(base_family = "EB Garamond", base_size = 30) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )
```
```{r}
# ==============================================================================
# 3-Tier Factional Diet Composition 
# (Left/Center vs. Non-Wolves Right vs. Wolves)
# ==============================================================================

# 1. Create the overarching 3-tier grouping for the entire parliament
parliament_nodes <- nodes_breakdown %>%
  mutate(
    faction_3tier = case_when(
      is_wolf == 1 ~ "Wolves",
      ideology_2021 > 0 & is_wolf == 0 ~ "Non-Wolves Right",
      TRUE ~ "Left & Center" # Captures everyone else (ideology <= 0 or NA)
    ),
    # Set the factor levels so the chart reads logically from Left to Far-Right
    faction_3tier = factor(faction_3tier, levels = c("Left & Center", "Non-Wolves Right", "Wolves"))
  )

# 2. Join the overarching groups to the cleanly filtered domain list
all_shares_clean <- domain_long_clean %>%
  inner_join(parliament_nodes %>% select(author, faction_3tier), by = "author")

# 3. Calculate Total Media Output (Denominators) per group
group_budgets_3tier <- all_shares_clean %>%
  group_by(faction_3tier) %>%
  summarise(total_faction_shares = sum(share_count), .groups = "drop")

# 4. Calculate attention shares and merge with our typologies
faction_diet_profiles_3tier <- all_shares_clean %>%
  group_by(faction_3tier, domain) %>%
  summarise(domain_faction_shares = sum(share_count), .groups = "drop") %>%
  
  # Bring in the total budgets to calculate percentages
  inner_join(group_budgets_3tier, by = "faction_3tier") %>%
  mutate(pct_of_diet = (domain_faction_shares / total_faction_shares) * 100) %>%
  
  # Join the structural typologies we created in the previous step
  left_join(domain_typologies %>% select(domain, media_profile), by = "domain") %>%
  filter(!is.na(media_profile)) %>% # Drop any extreme low-N noise that missed the typology cut
  
  # Aggregate the percentages by profile and faction
  group_by(faction_3tier, media_profile) %>%
  summarise(total_diet_percentage = sum(pct_of_diet), .groups = "drop") %>%
  
  # Filter out structural noise (profiles making up less than 2% of a group's diet)
  mutate(total_diet_percentage = if_else(total_diet_percentage < 2, NA_real_, total_diet_percentage)) %>%
  drop_na()

# 5. Plot the 3-column progression
media_diet_plot <- ggplot(
  faction_diet_profiles_3tier, aes(x = faction_3tier, y = total_diet_percentage, fill = media_profile)) +
  geom_col(position = "fill", alpha = 0.9, color = "white") +
  
  # Format Y-axis as percentages
  scale_y_continuous(labels = scales::percent_format()) +
  
  # Use a distinct categorical palette
  scale_fill_brewer(palette = "Set3", name = "Media Typology Profile") +
  
  labs(
    title = "The Architecture of Polarization: Media Diet by Parliamentary Bloc",
    subtitle = "Tracks the allocation of attention from the mainstream baseline to the populist fringe.",
    x = "Parliamentary Faction",
    y = "Proportion of Total Media Diet"
  ) +
  theme_minimal(base_family = "EB Garamond", base_size = 40) +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "right",
    panel.grid.major.x = element_blank()
  )

ggsave("Media_Diet_Composition.png", 
       plot = media_diet_plot, width = 7, height = 5, dpi = 300)

media_diet_plot
```
*Figure. Media Diet Composition of Wolves and Other Right-Wing Parliamentarians by Media Profile.* Note. Bars show the distribution of domains shared by wolves and non-wolf right-wing parliamentarians across media profiles defined by ideological orientation (weighted mean ideology: left < −0.25; center = −0.25 to 0.25; right > 0.25), dispersion (weighted ideological SD: exclusive < 0.45; cross-partisan ≥ 0.45), and salience (niche < 100 shares; core ≥ 100 shares). Profiles accounting for less than 2% of a group’s media diet are omitted; bars are rescaled to 100% across the remaining profiles.

```{r}
# ==============================================================================
# Connective Faction Test via Partisan-Exclusive Filtering
# ==============================================================================

# 1. Identify the domains that represent the partisan, exclusive network
partisan_exclusive_domains <- domain_typologies %>%
  filter(cat_dispersion == "Exclusive" & cat_partisanship != "Center") %>%
  pull(domain)

# 2. Reconstruct a clean matrix using ONLY these radical/partisan domains
filtered_matrix_df <- domain_long_clean %>%
  filter(domain %in% partisan_exclusive_domains) %>%
  pivot_wider(names_from = domain, values_from = share_count, values_fill = 0) %>%
  column_to_rownames("author")

# Convert to matrix form
mat_filtered <- as.matrix(filtered_matrix_df)

# Check if any authors were dropped entirely because they ONLY shared mainstream news
# We must keep track of who is actually in this sub-network
active_authors <- rownames(mat_filtered)

# 3. Calculate Cosine Similarity to normalize for posting volume
mat_norm_filtered <- mat_filtered / sqrt(rowSums(mat_filtered^2))
# Replace NaNs with 0 (occurs if an author's row sum is 0 after filtering)
mat_norm_filtered[is.na(mat_norm_filtered)] <- 0 
sim_matrix_filtered <- mat_norm_filtered %*% t(mat_norm_filtered)

# 4. Network Construction
# Remove self-loops
diag(sim_matrix_filtered) <- 0

# Apply a stricter threshold since we are dealing with hyper-specific partisan ties
threshold_partisan <- 0.15
sim_matrix_filtered[sim_matrix_filtered < threshold_partisan] <- 0

# Build the undirected, weighted igraph object
g_partisan <- graph_from_adjacency_matrix(
  sim_matrix_filtered, 
  mode = "undirected", 
  weighted = TRUE, 
  diag = FALSE
)

# Optional: Remove isolated nodes (politicians with no ties in this specific sub-network)
g_partisan <- delete_vertices(g_partisan, degree(g_partisan) == 0)

# 5. Unsupervised Community Detection (Louvain)
set.seed(42)
louvain_comm_partisan <- cluster_louvain(g_partisan)

# 6. Extract the emergent communities
community_df_partisan <- data.frame(
  author = V(g_partisan)$name,
  emergent_community = as.factor(louvain_comm_partisan$membership)
)

# 7. Validate against the theoretical "Wolf" faction
validation_df_partisan <- community_df_partisan %>%
  inner_join(
    nodes_breakdown %>% select(author, is_wolf, party, ideology_2021), 
    by = "author"
  )

# Generate the cross-tabulation table
cross_tab_partisan <- table(
  Emergent_Community = validation_df_partisan$emergent_community, 
  Is_Wolf = validation_df_partisan$is_wolf
)

print("Results of Connective Faction Clustering (Exclusive Partisan Media Only):")
print(cross_tab_partisan)
```
## 5. Domains in Election Propaganda
Analysis of media domains and profiles in wolves' Q2 posts
```{r}
wolf_lookup <- nodes_breakdown %>%
  dplyr::select(author, is_wolf) %>%
  dplyr::distinct(author, .keep_all = TRUE)

# -------------------------
# 2. Domains appearing in wolves' Q2 posts
# -------------------------
q2_wolf_domains <- q12_domains %>%
  dplyr::filter(category == "Q2") %>%
  dplyr::left_join(wolf_lookup, by = "author") %>%
  dplyr::filter(is_wolf == 1) %>%
  dplyr::left_join(
    domain_typologies %>%
      dplyr::select(domain, media_profile, cat_partisanship, cat_dispersion,
        cat_salience), by = "domain") %>%
  dplyr::mutate(
    media_profile = dplyr::coalesce(media_profile,"Unclassified"))
```

```{r}
# -------------------------
# Domain composition of wolves' Q2 posts
# -------------------------
q2_wolf_domain_summary <- q2_wolf_domains %>%
  dplyr::group_by(
    domain,
    media_profile,
    cat_partisanship,
    cat_dispersion,
    cat_salience
  ) %>%
  dplyr::summarise(
    domain_appearances = dplyr::n(),
    n_posts = dplyr::n_distinct(postID),
    n_authors = dplyr::n_distinct(author),
    linked = sum(source == "Linked URL"),
    textual = sum(source == "Text mention"),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    pct_domain_appearances =
      domain_appearances / sum(domain_appearances) * 100
  ) %>%
  dplyr::arrange(
    dplyr::desc(n_posts),
    dplyr::desc(domain_appearances)
  )

q2_wolf_domain_summary %>%
  dplyr::slice_head(n = 30) %>%
  print(n = 30)
```
```{r}
# -------------------------
#  Media-profile composition of wolves' Q2 posts
# -------------------------
q2_wolf_by_profile <- q2_wolf_domains %>%
  dplyr::group_by(
    media_profile,
    cat_partisanship,
    cat_dispersion,
    cat_salience
  ) %>%
  dplyr::summarise(
    domain_appearances = dplyr::n(),
    n_posts = dplyr::n_distinct(postID),
    n_authors = dplyr::n_distinct(author),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    pct_domain_appearances =
      domain_appearances / sum(domain_appearances) * 100
  ) %>%
  dplyr::arrange(
    dplyr::desc(pct_domain_appearances)
  )

q2_wolf_by_profile
```
```{r}
# -------------------------
# Media-profile composition of wolves' overall media diet
# -------------------------
wolf_overall_domains <- domain_long_clean %>%
  dplyr::left_join(wolf_lookup, by = "author") %>%
  dplyr::filter(is_wolf == 1) %>%
  dplyr::left_join(domain_typologies %>%
      dplyr::select(domain, media_profile, cat_partisanship, cat_dispersion,
        cat_salience), by = "domain") %>%
  dplyr::mutate(media_profile = dplyr::coalesce(media_profile,"Unclassified"))


wolf_overall_by_profile <- wolf_overall_domains %>%
  dplyr::group_by(media_profile, cat_partisanship, cat_dispersion, cat_salience)%>%
  dplyr::summarise(
    domain_appearances = sum(share_count, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    pct_domain_appearances =
      domain_appearances / sum(domain_appearances) * 100
  ) %>%
  dplyr::arrange(
    dplyr::desc(pct_domain_appearances)
  )

# -------------------------
# Compare Q2 media profile vs. wolves' overall media diet
# -------------------------
wolf_profile_comparison <- dplyr::bind_rows(
  q2_wolf_by_profile %>%
    dplyr::transmute(media_profile, sample = "Q2 posts", domain_appearances, pct_domain_appearances),

  wolf_overall_by_profile %>%
    dplyr::transmute(media_profile, sample = "Overall posting",
      domain_appearances, pct_domain_appearances))

wolf_profile_comparison_wide <- wolf_profile_comparison %>%
  dplyr::select(media_profile, sample, pct_domain_appearances) %>%
  tidyr::pivot_wider(
    names_from = sample,
    values_from = pct_domain_appearances,
    values_fill = 0) %>%
  dplyr::mutate(difference = `Q2 posts` - `Overall posting`) %>%
  dplyr::arrange(dplyr::desc(difference))

wolf_profile_comparison_wide
```
#### Plots
```{r}
# ==============================================================================
# MEDIA PROFILE COMPOSITION
# ==============================================================================
# Filter out unclassified domains before plotting
wolf_profile_comparison_filtered <- wolf_profile_comparison %>%
  filter(!media_profile %in% c("Unclassified", "unclassified", NA)) %>%
  mutate(
    sample = recode(sample,
      "Q2 posts" = "Propaganda against the electoral system",
      "Overall posting" = "Overall posting"
    )
  )

plot_q2_wolf_profiles <- ggplot(
  wolf_profile_comparison_filtered,
  aes(
    x = reorder(media_profile, pct_domain_appearances),
    y = pct_domain_appearances,
    fill = sample
  )
) +
  geom_col(position = "dodge", alpha = 0.9) +
  coord_flip() +
  scale_fill_manual(values = c(
    "Overall posting" = "darkgray",
    "Propaganda against the electoral system" = "coral"
  )) +
  scale_y_continuous(labels = function(x) paste0(round(x, 1), "%")) +
  labs(
    title = "Media Profiles in Wolves' Propaganda against the Electoral System",
    subtitle = "Distribution of domain appearances in wolves' propaganda compared with their overall media diet.",
    x = NULL,
    y = "Share of Domain Appearances",
    fill = NULL
  ) +
  theme_minimal(base_family = "EB Garamond", base_size = 40) +
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(margin = margin(b = 5)),
    plot.margin = margin(t = 5, r = 5, b = 5, l = 5),
    legend.position = "bottom"
  )

ggsave("plot_q2_wolf_profiles.png", plot = plot_q2_wolf_profiles, width = 10, height = 5, dpi = 300)
plot_q2_wolf_profiles
```

```{r}
# ==============================================================================
# TEMPORAL ANALYSIS OF MEDIA DOMAINS IN WOLVES' Q2 POSTS
# ==============================================================================
top_media_profiles <- c(
  "Right | Exclusive | Core",
  "Left | Cross-Partisan | Core",
  "Center | Cross-Partisan | Core"
)

temporal_q2_wolves <- q2_wolf_domains %>%
  
  # Add timestamp from the post-level data
  dplyr::left_join(
    q12_posts %>%
      dplyr::select(postID, author, timestamp) %>%
      dplyr::distinct(),
    by = c("postID", "author")
  ) %>%
  
  # Keep the three most recurrent media profiles
  dplyr::filter(
    media_profile %in% top_media_profiles
  ) %>%
  
  # Create weekly time unit
  dplyr::mutate(
    post_week = lubridate::floor_date(
      timestamp,
      unit = "week"
    ),
    media_profile = factor(
      media_profile,
      levels = top_media_profiles
    )
  ) %>%
  
  # Count domain appearances by week and profile
  dplyr::count(
    post_week,
    media_profile,
    name = "domain_appearances"
  ) %>%
  
  # Explicitly represent weeks with zero appearances
  tidyr::complete(
    post_week = seq(
      min(post_week),
      max(post_week),
      by = "week"
    ),
    media_profile,
    fill = list(domain_appearances = 0)
  )

temporal_q2_wolves
```

```{r}
# ==============================================================================
# WEEKLY MEDIA-DOMAIN APPEARANCES IN WOLVES' Q2 POSTS
# ==============================================================================
plot_q2_wolf_timeline <- ggplot(
  temporal_q2_wolves,
  aes(
    x = post_week,
    y = domain_appearances,
    color = media_profile,
    group = media_profile
  )
) +
  geom_line(linewidth = 1) +
  geom_point(data = temporal_q2_wolves %>%
      dplyr::filter(domain_appearances > 0),
    alpha = 0.4
  ) +
  scale_color_manual(
    values = c(
      "Right | Exclusive | Core" = "coral",
      "Center | Cross-Partisan | Core" = "grey",
      "Left | Cross-Partisan | Core" = "darkgreen"
    )
  ) +
  labs(
    title = "Media Domains in Wolves' Election-System Propaganda Over Time",
    subtitle = "Weekly domain appearances in Q2 posts across the three most recurrent media profiles.",
    x = "Timeline",
    y = "Number of Domain Appearances",
    color = "Media Profile"
  ) +
  theme_minimal(base_family = "EB Garamond", base_size = 45) +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "bottom"
  )

ggsave("plot_q2_wolf_timeline.png", plot = plot_q2_wolf_timeline, width = 11, height = 8, dpi = 300)
plot_q2_wolf_timeline
```
Inspect posts for mainstream/centrist reporting is being used to support, criticize, reinterpret, or attack the information being shared.
```{r}
# ==============================================================================
# QUALITATIVE INSPECTION OF CENTER | CROSS-PARTISAN | CORE MEDIA IN WOLVES' Q2
# ==============================================================================
# Identify unique Q2 posts by wolves containing domains from the
# Center | Cross-Partisan | Core profile
q2_center_core_candidates <- q2_wolf_domains %>%
  dplyr::filter(media_profile == "Center | Cross-Partisan | Core") %>%
  # Avoid counting the same domain twice if it appears as both
  # a linked URL and a textual mention
  dplyr::distinct(postID, author, domain) %>%
  
  # Recover post text and timestamp
  dplyr::left_join(q12_posts %>%
      dplyr::select(postID, author, timestamp, text_combined) %>%
      dplyr::distinct(),
    by = c("postID", "author")) %>%
  
  dplyr::filter(!is.na(text_combined), text_combined != "") %>%
  
  # Collapse multiple qualifying domains within the same post
  dplyr::group_by(postID, author, timestamp, text_combined) %>%
  dplyr::summarise(
    domains = paste(
      sort(unique(domain)),
      collapse = "; "),
    .groups = "drop"
  )


# -------------------------
# Random qualitative sample
# -------------------------
set.seed(999)
sample_n_q2 <- min(10, nrow(q2_center_core_candidates))

q2_center_core_sample <- q2_center_core_candidates %>%
  dplyr::slice_sample(n = sample_n_q2)

cat("Qualitative Sample: Wolves' Q2 Posts Featuring Center | Cross-Partisan | Core Media\n")
cat("=================================================================================\n\n")

for(i in 1:nrow(q2_center_core_sample)) {
  
  cat("POST [", i, "]\n", sep = "")
  cat("Author:  ", q2_center_core_sample$author[i], "\n")
  cat("Domain:  ", q2_center_core_sample$domain[i], "\n")
  cat("Text:\n", q2_center_core_sample$text_combined[i], "\n")
  cat("---------------------------------------------------------------------------------\n\n")
}
```




##6. Domain scores

```{r}
# ==============================================================================
# APPENDIX TABLE: MEDIA DOMAINS, IDEOLOGY, AND REFERENCE FREQUENCY
# ==============================================================================
media_domain_appendix <- domain_long_clean %>%
  
  # Add politicians' ideological scores
  dplyr::inner_join(
    nodes_breakdown %>%
      dplyr::select(
        author,
        ideology_2021
      ),
    by = "author"
  ) %>%
  
  # Summarize at the domain level
  dplyr::group_by(domain) %>%
  dplyr::summarise(
    
    # Total number of references to the domain
    n_references = sum(
      share_count,
      na.rm = TRUE
    ),
    
    # Number of distinct politicians referencing the domain
    n_politicians = dplyr::n_distinct(author),
    
    # Ideological center of gravity, weighted by references
    ideological_score = weighted.mean(
      ideology_2021,
      w = share_count,
      na.rm = TRUE
    ),
    
    .groups = "drop"
  ) %>%
  
  # Retain domains with sufficient frequency and coverage
  dplyr::filter(
    n_references >= 10,
    n_politicians >= 3
  ) %>%
  
  # Format for appendix table
  dplyr::transmute(
    domain,
    ideological_score = round(ideological_score, 3),
    n_references
  ) %>%
  
  # Most frequently referenced domains first
  dplyr::arrange(
    dplyr::desc(n_references)
  )


# Inspect
media_domain_appendix %>%
  print(n = 50)


# Export CSV
readr::write_csv(
  media_domain_appendix,
  here::here(
    "_output",
    "media_domain_ideology_appendix.csv"
  )
)
```
Ideological scores represent the weighted mean ideological position of politicians referencing each domain, with references used as weights; negative values indicate more left-leaning audiences and positive values indicate more right-leaning audiences. Reference frequency indicates the total number of times a domain was referenced. The table includes only domains referenced at least 10 times and by at least three distinct politicians.





# DUMPSTER
```{r}
# ==============================================================================
# Multi-Modal Classification of Election Denialism
# ==============================================================================
# 1. Prepare the post-level dataset using the composite metric
post_level_analysis_robust <- df_fb_election %>%
  filter(!is.na(domain), domain != "", !is.na(Q2), !is.na(PEC135)) %>%
  mutate(
    post_week = floor_date(timestamp, "week"),
    # True denialism:
    # Q2 = 1: post contains propaganda against the electoral system
    # PEC135 = 1: author voted in favor of PEC135
    true_denialism = as.integer(Q2 == 1 & PEC135 == 1)
  ) %>%

  # Add domain characteristics AFTER defining true denialism
  left_join(
    domain_typologies %>%
      select(domain, media_profile,
        cat_partisanship, cat_dispersion, cat_salience),
    by = "domain")

# VALIDATE CLASSIFICATION
true_denialism_check <- post_level_analysis_robust %>%
  count(Q2, PEC135, true_denialism) %>%
  arrange(desc(true_denialism), Q2, PEC135)

true_denialism_check
```

```{r}
df_fb_election %>%
  filter(Q2 == 1, PEC135 == 1) %>%
  mutate(
    domain_status = if_else(
      !is.na(domain) & domain != "",
      "Has linked domain",
      "No linked domain"
    )
  ) %>%
  count(domain_status) %>%
  mutate(
    percentage = round(n / sum(n) * 100, 2)
  )
```

```{r}
# Media Typology Composition of True Denialism
true_denialism_by_profile <- post_level_analysis_robust %>%
  filter(true_denialism == 1) %>%
  mutate(
    media_profile = coalesce(media_profile, "Unclassified")
  ) %>%
  count(
    media_profile,
    cat_partisanship,
    cat_dispersion,
    cat_salience,
    name = "domain_appearances"
  ) %>%
  mutate(
    share_of_true_denialism =
      domain_appearances / sum(domain_appearances) * 100
  ) %>%
  arrange(desc(domain_appearances))

true_denialism_by_profile
```

```{r}
# 2. Descriptive Probability: Media types predicting true denialism
denialism_by_profile <- post_level_analysis_robust %>%
  group_by(media_profile) %>%
  summarise(
    total_posts_with_link = n(),
    true_denial_posts = sum(true_denialism, na.rm = TRUE),
    pct_true_denial = (true_denial_posts / total_posts_with_link) * 100,
    .groups = "drop"
  ) %>%
  # Filter out low-N noise profiles
  filter(total_posts_with_link >= 50) %>%
  arrange(desc(pct_true_denial))

print("Probability of Election Denialism (Q2=1 & PEC135=1) by Media Typology:")
print(denialism_by_profile)

# 3. Visualization 1: The Discursive Vector (Corrected)
ggplot(denialism_by_profile, aes(x = reorder(media_profile, pct_true_denial), y = pct_true_denial)) +
  geom_col(aes(fill = grepl("Right \\| Exclusive", media_profile)), alpha = 0.9) +
  coord_flip() +
  scale_fill_manual(values = c("TRUE" = "darkred", "FALSE" = "gray70")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  labs(
    title = "Alternative Media as Vectors of True Election Denialism",
    subtitle = "Percentage of posts flagged for denialism (Textual Skepticism + PEC135 Support).",
    x = NULL,
    y = "Probability of Post Containing True Denialism",
    fill = "Far-Right Alternative Ecosystem"
  ) +
  theme_minimal(base_family = "EB Garamond", base_size = 30) +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "none"
  )

# ==============================================================================
# STEP 11: Temporal Analysis of True Denialism
# ==============================================================================

# Aggregate the volume of true denialist posts over time
temporal_denialism <- post_level_analysis_robust %>%
  filter(true_denialism == 1) %>%
  mutate(
    broad_media_type = case_when(
      cat_partisanship == "Right" & cat_dispersion == "Exclusive" ~ "Far-Right Alternative",
      cat_partisanship == "Center" ~ "Mainstream/Centrist",
      TRUE ~ "Other"
    )
  ) %>%
  group_by(post_week, broad_media_type) %>%
  summarise(denialist_volume = n(), .groups = "drop")

# Visualization 2: The Timeline
ggplot(temporal_denialism, aes(x = post_week, y = denialist_volume, color = broad_media_type)) +
  geom_line(size = 1.2) +
  geom_point(alpha = 0.6) +
  scale_color_manual(values = c("Far-Right Alternative" = "darkred", "Mainstream/Centrist" = "gray60", "Other" = "steelblue")) +
  labs(
    title = "The Timeline of Discursive Radicalization",
    subtitle = "Weekly volume of denialist posts by PEC135 supporters, categorized by media link.",
    x = "Timeline",
    y = "Volume of True Denialist Posts",
    color = "Linked Media Ecosystem"
  ) +
  theme_minimal(base_family = "EB Garamond", base_size = 30) +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "bottom"
  )
```

```{r}
# ==============================================================================
# APPENDIX FIGURES: Multi-Modal Classification of Election Denialism
# ==============================================================================
# 1. Descriptive Probability Bar Chart
plot_denialism_bar <- ggplot(denialism_by_profile, aes(x = reorder(media_profile, pct_true_denial), y = pct_true_denial)) +
  geom_col(aes(fill = grepl("Right \\| Exclusive", media_profile)), alpha = 0.9) +
  coord_flip() +
  scale_fill_manual(values = c("TRUE" = "darkred", "FALSE" = "gray70")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  labs(
    title = "Alternative Media as Vectors of Attacks on Election Integrity",
    subtitle = "Percentage of posts flagged for Textual Skepticism + PEC135 Support.",
    x = NULL,
    y = "Probability of Post Containing Election Undermining Content",
    fill = "Far-Right Alternative Ecosystem"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "none",
    plot.background = element_rect(fill = "white", color = NA) # Ensures printable background
  )

# Export Bar Chart
ggsave("appendix_fig1_denialism_probability.png", plot = plot_denialism_bar, width = 10, height = 6, dpi = 300)
print(plot_denialism_bar)


# 2. Timeline of Discursive Radicalization
plot_denialism_timeline <- ggplot(temporal_denialism, aes(x = post_week, y = denialist_volume, color = broad_media_type)) +
  geom_line(linewidth = 1.2) + # Note: using linewidth instead of size for updated ggplot2 standards
  geom_point(alpha = 0.6) +
  scale_color_manual(values = c(
    "Far-Right Alternative" = "darkred", 
    "Mainstream/Centrist" = "gray60", 
    "Other" = "steelblue"
  )) +
  labs(
    title = "The Timeline of Discursive Radicalization",
    subtitle = "Weekly volume of denialist posts by PEC135 supporters, categorized by media link.",
    x = "Timeline",
    y = "Volume of True Denialist Posts",
    color = "Linked Media Ecosystem"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "bottom",
    plot.background = element_rect(fill = "white", color = NA) # Ensures printable background
  )

# Export Timeline
ggsave("appendix_fig2_denialism_timeline.png", plot = plot_denialism_timeline, width = 10, height = 6, dpi = 300)
print(plot_denialism_timeline)
```

```{r}
# ==============================================================================
# STEP 13: Qualitative Validation of Refutational Sharing (True Denialists Only)
# ==============================================================================

# 1. Isolate the intersection of True Denialism + Mainstream Media
set.seed(123) # Using a new seed for a fresh draw

true_refutational_sample <- post_level_analysis_robust %>%
  filter(true_denialism == 1 & media_profile == "Center | Cross-Partisan | Core") %>%
  # Ensure the text field is populated
  filter(!is.na(text_combined) & text_combined != "") %>%
  # Randomly select 10 posts
  slice_sample(n = 10) %>%
  select(author, domain, text_combined)

# 2. Print the results clearly to the console
cat("Qualitative Sample: 10 TRUE Denialist Posts Linking to Mainstream Media\n")
cat("=======================================================================\n\n")

for(i in 1:nrow(true_refutational_sample)) {
  cat("POST [", i, "]\n", sep = "")
  cat("Author:  ", true_refutational_sample$author[i], "\n")
  cat("Domain:  ", true_refutational_sample$domain[i], "\n")
  cat("Text:\n", true_refutational_sample$text_combined[i], "\n")
  cat("-----------------------------------------------------------------------\n\n")
}
```
```{r}
# ==============================================================================
# STEP 14: Inductive Extraction of Denialist Domains (Bottom-Up)
# ==============================================================================

# Extract the specific domains driving True Election Denialism
denialist_domain_drivers <- post_level_analysis_robust %>%
  # Ensure we have a valid domain
  filter(!is.na(domain) & domain != "") %>%
  group_by(domain) %>%
  summarise(
    total_shares = n(),
    true_denial_shares = sum(true_denialism, na.rm = TRUE),
    # Calculate the probability that a link to this domain accompanies a denialist post
    pct_denial = (true_denial_shares / total_shares) * 100,
    .groups = "drop"
  ) %>%
  # Filter out low-N noise (domains shared fewer than 15 times overall)
  filter(total_shares >= 15) %>%
  # Sort by absolute volume of denialist shares to see the main engines
  arrange(desc(true_denial_shares))

# Print the top 20 domains by absolute volume
print("Top 20 Domains by Absolute Volume of True Denialism:")
print(head(denialist_domain_drivers, 20))

# Print the top 20 domains by proportion/probability 
# (This isolates the purest echo chambers)
print("Top 20 Domains by Probability/Density of True Denialism:")
print(head(denialist_domain_drivers %>% arrange(desc(pct_denial)), 20))
```
### The Tri-Partite Media Strategy of the Connective Faction

Previous iterations of the analysis relied on *a priori* domain typologies, which inadvertently obscured the functional differences between digital platforms and editorial publishers. To isolate the actual vectors of anti-democratic rhetoric, we adopted an inductive approach, extracting the specific web domains most frequently associated with true election denialism ($Q2 = 1$ and $PEC 135 = 1$). 

The resulting distribution reveals that the populist connective faction does not rely on a monolithic echo chamber, but rather a sophisticated, tri-partite media architecture:

1. **Ideological Sanctuaries (High Density):** Right-wing alternative publishers such as *Revista Oeste* and *Gazeta do Povo* act as the intellectual core of the denialist narrative. While sharing volume is relatively low, the density of radicalization is severe: links to these domains exhibit a 20% to 30% probability of accompanying election-skeptical text.
2. **Unregulated Infrastructure (High Volume):** Video hosting platforms, overwhelmingly *YouTube*, serve as the primary infrastructural engine. YouTube generated the highest absolute volume of denialist shares, allowing right-wing elites to broadcast unfiltered, hour-long live streams directly to the connective faction without editorial friction.
3. **Adversarial Foils (Low Density, High Baseline Volume):** Mainstream legacy media (*Folha de S.Paulo*, *Estadão*) maintain massive overall sharing volumes across the right wing, but their association with denialism is fractional (under 1%). This quantifies the "refutational sharing" dynamic: mainstream media is occasionally weaponized as an adversarial prop to validate a populist grievance, but it is not the primary incubator of the ideology.

Ultimately, establishing a connective faction requires more than alternative media consumption; it requires exploiting platforms for reach, alternative publishers for ideological validation, and mainstream media for adversarial outrage.


```{r}
# ==============================================================================
# STEP 15: Visualizing the Architecture and Testing Factional Specificity
# ==============================================================================
library(ggplot2)
library(ggrepel) # For clean text labels on the scatterplot

# 1. Visualizing the Tri-Partite Architecture
architecture_plot <- ggplot(denialist_domain_drivers, aes(x = total_shares, y = pct_denial)) +
  geom_point(alpha = 0.8, color = "darkred", size = 3) +
  geom_text_repel(aes(label = domain), size = 4, max.overlaps = 15) +
  # We use a log scale on the X-axis because Folha and YouTube volume 
  # would otherwise crush the sanctuaries into the left margin
  scale_x_log10() + 
  labs(
    title = "The Tri-Partite Media Architecture of Connective Factions",
    subtitle = "Mapping the Volume vs. Density of True Election Denialism",
    x = "Total Shares by Pro-Reform Actors (Log Scale)",
    y = "Probability of Linked Post Containing True Denialism (%)"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold"))

# Print the plot
print(architecture_plot)

# 2. Testing Factional Specificity: Are Sanctuaries specific to the Wolves?
# We manually define the categories based on the inductive results
sanctuary_domains <- c("revistaoeste", "gazetadopovo")
foil_domains <- c("folha", "estadao")
infra_domains <- c("youtube", "google") # 'google' acts as youtube redirects

# Filter the dataset and cross-tabulate domain usage by faction
faction_media_usage <- post_level_analysis_robust %>%
  filter(domain %in% c(sanctuary_domains, foil_domains, infra_domains)) %>%
  # Join the nodes dataset to get the manual is_wolf label
  left_join(nodes_breakdown %>% select(author, is_wolf), by = "author") %>%
  # Ensure we only look at actors with a known status
  filter(!is.na(is_wolf)) %>%
  mutate(
    media_function = case_when(
      domain %in% sanctuary_domains ~ "Ideological Sanctuaries",
      domain %in% foil_domains ~ "Mainstream Foils",
      domain %in% infra_domains ~ "Unregulated Infrastructure"
    ),
    wolf_status = ifelse(is_wolf == 1, "The Wolves", "Institutional Right")
  ) %>%
  group_by(wolf_status, media_function) %>%
  summarise(
    total_shares = n(),
    .groups = "drop"
  ) %>%
  # Calculate the relative proportion of their media diet within these categories
  group_by(wolf_status) %>%
  mutate(pct_of_diet = (total_shares / sum(total_shares)) * 100) %>%
  ungroup() %>%
  arrange(wolf_status, desc(pct_of_diet))

cat("\n--- DIET COMPOSITION: WOLVES VS INSTITUTIONAL RIGHT ---\n")
print(faction_media_usage)

# 3. Formal Statistical Test: Chi-Square
# Does media function depend on factional status?

diet_matrix_corrected <- xtabs(total_shares ~ wolf_status + media_function, data = faction_media_usage)

cat("\n--- TRUE DIET MATRIX ---\n")
print(diet_matrix_corrected)

# Re-run the Chi-Square test
chisq_result_corrected <- chisq.test(diet_matrix_corrected)
cat("\n--- CORRECTED CHI-SQUARE TEST ---\n")
print(chisq_result_corrected)
```

