---
title: "_3_Wolves_Analysis"
author: "André K. Rodarte"
date: "2026-05-15"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(showtext)
library(here)
library(sysfonts)
library(scales)
library(broom)
library(lubridate)
library(car)
library(patchwork)
library(ggplot2)
font_add_google("EB Garamond", "EB Garamond")
showtext_auto()
```


# Data

```{r}
# Entire dataset
df_fb <- read_rds(
  here("..", "_processed_data", "df_fb_GPT.rds"))
# Filtered dataset + GPT analysis
df_fb_election <- read_rds(
  here("..", "_processed_data", "df_fb_election.rds"))

# Information about politicians
nodes_breakdown <- read_csv(
  here("..", "_processed_data", "nodes_breakdown.csv"))

# Party/Ideology Data
parties_ideology_scores <- read_csv(
  here("..", "_data", "parties_ideology_scores.csv"))

# Domain data
account_by_media_domain_counts <- read_rds(
  here("..", "_processed_data", "account_by_media_domain_counts.rds"))
```
*Handling missing values*
```{r}
# PODEMOS's scores were missing, so I'm adding them manually here. There are 12 other missing values due to party changes / isolated cases.
party_ideology_lookup <- parties_ideology_scores %>%
  transmute(
    party = str_to_upper(str_squish(Party)),
    ideology_2021_lookup = `2021_ideological_score`
  )

nodes_breakdown <- nodes_breakdown %>%
  mutate(
    party = str_to_upper(str_squish(party))
  ) %>%
  left_join(
    party_ideology_lookup,
    by = "party"
  ) %>%
  mutate(
    ideology_2021 = coalesce(ideology_2021, ideology_2021_lookup)
  ) %>%
  select(-ideology_2021_lookup)
```


# Set Up
```{r}
group_colors <- c(
  "All other parliamentarians" = "grey60",
  "Wolves" = "navyblue"
)

# Adding label for the plots
nodes_grouped <- nodes_breakdown %>%
  mutate(
    wolf_group = case_when(
      is_wolf == 1 ~ "Wolves",
      is_wolf == 0 ~ "All other parliamentarians",
      TRUE ~ NA_character_
    ),
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")
    )
  ) %>%
  filter(!is.na(wolf_group))

# Plots Shared Theme
theme_wolves <- function() {
  theme_minimal(base_family = "EB Garamond", base_size = 30) +
    theme(
      text = element_text(family = "EB Garamond", size = 30),
      plot.title = element_text(face = "bold", size = 40),
      axis.title = element_text(size = 32),
      axis.text = element_text(size = 30),
      legend.title = element_text(size = 30),
      legend.text = element_text(size = 30),
      strip.text = element_text(size = 32, face = "bold")
    )
}

# Export location
output_path <- here::here("_output")


# ----------------------------
# ANOVA
# ----------------------------
eta_squared_from_aov <- function(model) {
  aov_table <- broom::tidy(model)
  
  ss_effect <- aov_table %>%
    filter(term != "Residuals") %>%
    pull(sumsq)
  
  ss_total <- sum(aov_table$sumsq, na.rm = TRUE)
  
  tibble(
    term = aov_table %>%
      filter(term != "Residuals") %>%
      pull(term),
    eta_squared = ss_effect / ss_total
  )
}
```

# Categorical Analysis

```{r}
mainstream_domains <- c("aosfatos", "band", "bbc", "bbccouk", "bbcin", "buzzfeed", "clarin", "cnn", "cnnbrasil", "correiobraziliense", "dailymailcouk", "eldiarioes", "elpais", "elpaiscomuy", "estadao", "exame", "extraglobo", "folha", "folha1", "g1globo", "gazetadopovo", "globo", "globo", "huffpost", "huffpostbrasil", "independentcouk", "infomoney", "istoedinheiro", "istoe", "lemondefr", "metropolenoticias", "nexojornal", "noticiasuol", "nytimes", "ogloboglobo", "poder360", "r7", "reuters", "sbt", "sbtinterior", "sbtnews", "telegraphcouk", "terra", "theguardian", "uol", "valor", "washingtonpost", "wsj", "yahoo")

hyper_partisan_domains <- c("agoranoticiasbrasil", "aliadosbrasil", "brasilsemmedo", "capixabaempregos", "cartacapital", "esquerdadiario", "esquerdaonline", "financasbrasil", "intercept", "jacobin", "jornaldacidadeonline", "jovempan", "mbl", "mblnews", "midianinja", "mises", "noticiasdebrasilia", "novaiguacu24h", "oantagonismo", "oantagonista", "opiniaoes", "pensandodireita", "plenonews", "renovamidia", "revistaonline", "revistaoeste", "romanews", "tercalivre", "terrabrasilnoticias", "theintercept", "veja", "vejario", "vejasp")

party_domains <- c("cstpsol", "democratas", "mulheresrepublicanas10", "novo", "novonacamara", "pcdob", "pcdobba", "pcdobnacamara", "pdt", "pdtnacamara", "pl22", "podemos", "pps", "prb10", "prb10rj", "prb10sp", "prbmg10", "prbmulher10", "prbnacamara", "progressistas", "pros", "pros90", "prosnacamara", "psb40", "psb40bahia", "psbnacamara", "psc", "psd", "psdmg", "psdb", "psdbnacamara", "psdcamara", "pslsp", "psol", "psol50", "psol50sp", "psolbemviver", "psolcamarasp", "psolcarioca", "psolnacamara", "psolniteroi", "psolsaude", "psolsemente", "pt", "ptalagoas", "ptassembleiasp", "ptbahia", "ptb", "ptbnacamara", "ptcarioca", "ptceara", "ptmt", "ptnaalep", "ptnacamara", "ptnosenado", "ptpaulista", "ptpr", "ptsaopaulo", "ptsc", "ptsul", "pv", "republicanos10", "republicanos1010", "republicanos10mg", "republicanos10nacamara", "republicanos10riopreto", "republicanos10sp", "solidariedaderj")

clean_domain_key <- function(x) {
  x %>%
    stringi::stri_trans_general(id = "Latin-ASCII") %>%
    stringr::str_to_lower() %>%
    stringr::str_replace_all("^https?://", "") %>%
    stringr::str_replace_all("^www\\.", "") %>%
    stringr::str_replace_all("[^a-z0-9]", "") %>%
    stringr::str_trim()
}

classify_domain <- function(domain) {
  domain_key <- clean_domain_key(domain)
  dplyr::case_when(
    domain_key %in% mainstream_domains ~ "Mainstream",
    domain_key %in% hyper_partisan_domains ~ "Hyper-partisan",
    domain_key %in% party_domains ~ "Party domains",
    domain_key %in% radio_domains ~ "Radio",
    TRUE ~ "Others"
  )
}
```

```{r}
# Domain usage summaries by account and wolf status
# Convert account_by_media_domain_counts into long format
account_domain_long_for_usage <- account_by_media_domain_counts %>%
  as.data.frame(check.names = FALSE) %>%
  tidyr::pivot_longer(
    cols = -author,
    names_to = "domain",
    values_to = "n_domain_references"
  ) %>%
  dplyr::filter(n_domain_references > 0) %>%
  dplyr::mutate(
    domain_category = classify_domain(domain)
  )

# Account-level post counts from df_fb
account_post_counts <- df_fb %>%
  dplyr::count(author, name = "n_posts")


# Account-level domain usage table
domain_usage_author <- nodes_breakdown %>%
  dplyr::select(author, is_wolf) %>%
  dplyr::left_join(account_post_counts, by = "author") %>%
  dplyr::left_join(
    account_domain_long_for_usage %>%
      dplyr::group_by(author) %>%
      dplyr::summarise(
        n_domains_references = sum(n_domain_references, na.rm = TRUE),
        n_unique_domain_references = dplyr::n_distinct(domain),
        mainstream_domains = sum(
          n_domain_references[domain_category == "Mainstream"],
          na.rm = TRUE
        ),
        hyper_partisan_domains = sum(
          n_domain_references[domain_category == "Hyper-partisan"],
          na.rm = TRUE
        ),
        party_domains = sum(
          n_domain_references[domain_category == "Party domains"],
          na.rm = TRUE
        ),
        .groups = "drop"
      ),
    by = "author"
  ) %>%
  dplyr::mutate(
    dplyr::across(
      c(
        n_posts,
        n_domains_references,
        n_unique_domain_references,
        mainstream_domains,
        hyper_partisan_domains,
        party_domains
      ),
      ~ dplyr::coalesce(.x, 0)
    ),
    ratio_domains_references = 100 * n_domains_references / n_posts,
    ratio_mainstream = 100 * mainstream_domains / n_posts,
    ratio_hyper_partisan = 100 * hyper_partisan_domains / n_posts,
    ratio_party_domains = 100 * party_domains / n_posts
  )

# Inspect
glimpse(domain_usage_author)
```

#### Group Comparison

```{r}
domain_usage_group <- domain_usage_author %>%
  dplyr::mutate(
    wolf_group = dplyr::case_when(
      is_wolf == 1 ~ "Wolves",
      is_wolf == 0 ~ "All other parliamentarians",
      TRUE ~ NA_character_
    )
  ) %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::group_by(wolf_group) %>%
  dplyr::summarise(
    n_members = dplyr::n(),
    # Posts
    total_posts = sum(n_posts, na.rm = TRUE),
    mean_posts = mean(n_posts, na.rm = TRUE),
    sd_posts = sd(n_posts, na.rm = TRUE),
    # Domain references
    total_domain_references = sum(n_domains_references, na.rm = TRUE),
    mean_domain_references = mean(n_domains_references, na.rm = TRUE),
    sd_domain_references = sd(n_domains_references, na.rm = TRUE),
    # Unique domains
    total_unique_domain_references = sum(n_unique_domain_references, na.rm = TRUE),
    # Domain references per 100 posts
    ratio_domain_references = 100 * total_domain_references / total_posts,
    
    # Account-level average of the ratio
    mean_ratio_domain_references = mean(
      ratio_domains_references, na.rm = TRUE),
    sd_ratio_domain_references = sd(ratio_domains_references, na.rm = TRUE),
    .groups = "drop") %>%
  tidyr::pivot_longer(
    cols = -wolf_group,
    names_to = "measure",
    values_to = "value"
  ) %>%
  tidyr::pivot_wider(
    names_from = wolf_group,
    values_from = value
  )

# Format
domain_usage_group_formatted <- domain_usage_group %>%
  dplyr::mutate(
    dplyr::across(
      c(`All other parliamentarians`, Wolves),
      ~ dplyr::case_when(
        # Count variables: no decimals
        measure %in% c(
          "n_members",
          "total_posts",
          "total_domain_references",
          "total_unique_domain_references"
        ) ~ round(.x, 0),

        # Means, SDs, and ratios: two decimals
        TRUE ~ round(.x, 2)
      )
    )
  )

# Inspect
domain_usage_group_formatted
```

```{r}
# Create account-level post counts with no linked domain
posts_no_domains_author <- df_fb %>%
  dplyr::mutate(
    has_linked_domain = !is.na(domain) & domain != ""
  ) %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    n_posts_no_domains = sum(!has_linked_domain, na.rm = TRUE),
    .groups = "drop"
  )

# Group-level comparison
domain_category_counts <- domain_usage_author %>%
  dplyr::left_join(
    posts_no_domains_author,
    by = "author"
  ) %>%
  dplyr::mutate(
    n_posts_no_domains = dplyr::coalesce(n_posts_no_domains, 0),
    
    ratio_posts_no_domains = 100 * n_posts_no_domains / n_posts,
    
    wolf_group = dplyr::case_when(
      is_wolf == 1 ~ "Wolves",
      is_wolf == 0 ~ "All other parliamentarians",
      TRUE ~ NA_character_
    )
  ) %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::group_by(wolf_group) %>%
  dplyr::summarise(
    # Group size and activity
    n_members = dplyr::n(),
    total_posts = sum(n_posts, na.rm = TRUE),
    mean_posts = mean(n_posts, na.rm = TRUE),
    sd_posts = sd(n_posts, na.rm = TRUE),
    
    # Hyper-partisan domains
    mean_hyperpartisan_references = mean(hyper_partisan_domains, na.rm = TRUE),
    ratio_hyperpartisan_references =
      100 * sum(hyper_partisan_domains, na.rm = TRUE) / sum(n_posts, na.rm = TRUE),
    mean_ratio_hyperpartisan_references =
      mean(ratio_hyper_partisan, na.rm = TRUE),
    
    # Mainstream domains
    mean_mainstream_references = mean(mainstream_domains, na.rm = TRUE),
    ratio_mainstream_references =
      100 * sum(mainstream_domains, na.rm = TRUE) / sum(n_posts, na.rm = TRUE),
    mean_ratio_mainstream_references =
      mean(ratio_mainstream, na.rm = TRUE),
    
    # Party domains
    mean_partydomains_references = mean(party_domains, na.rm = TRUE),
    ratio_partydomains_references =
      100 * sum(party_domains, na.rm = TRUE) / sum(n_posts, na.rm = TRUE),
    mean_ratio_partydomains_references =
      mean(ratio_party_domains, na.rm = TRUE),
    
    # Posts with no linked domain
    mean_posts_no_domains = mean(n_posts_no_domains, na.rm = TRUE),
    ratio_posts_no_domains =
      100 * sum(n_posts_no_domains, na.rm = TRUE) / sum(n_posts, na.rm = TRUE),
    mean_ratio_posts_no_domains =
      mean(ratio_posts_no_domains, na.rm = TRUE),
    
    .groups = "drop"
  ) %>%
  tidyr::pivot_longer(
    cols = -wolf_group,
    names_to = "measure",
    values_to = "value"
  ) %>%
  tidyr::pivot_wider(
    names_from = wolf_group,
    values_from = value
  ) %>%
  dplyr::mutate(
    dplyr::across(
      c(`All other parliamentarians`, Wolves),
      ~ dplyr::case_when(
        measure %in% c(
          "n_members",
          "total_posts"
        ) ~ round(.x, 0),
        TRUE ~ round(.x, 2)
      )
    )
  )

# Inspect
domain_category_counts
```

##### ANOVA

```{r}
# ANOVAs: DOMAIN REFERENCES BY GROUP
eta_squared_from_aov <- function(model) {
  effectsize::eta_squared(model, partial = FALSE)
}

# Prepare data
domain_usage_anova <- domain_usage_author %>%
  mutate(
    wolf_group = case_when(
      is_wolf == 1 ~ "Wolves",
      is_wolf == 0 ~ "All other parliamentarians",
      TRUE ~ NA_character_
    ),
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")
    )
  ) %>%
  filter(!is.na(wolf_group))


############################################
#### A. Mean domain references by group  ###
############################################
# Raw count of domain references
anova_domain_references <- aov(
  n_domains_references ~ wolf_group,
  data = domain_usage_anova
)

anova_domain_references_tidy <- broom::tidy(anova_domain_references)
anova_domain_references_eta <- eta_squared_from_aov(anova_domain_references)

# Results
summary(anova_domain_references)
anova_domain_references_tidy
anova_domain_references_eta


# Optional: use the rate per 100 posts instead of raw counts
# anova_ratio_domain_references <- aov(
#   ratio_domains_references ~ wolf_group,
#   data = domain_usage_anova
# )
# 
# anova_ratio_domain_references_tidy <- broom::tidy(anova_ratio_domain_references)
# anova_ratio_domain_references_eta <- eta_squared_from_aov(anova_ratio_domain_references)
# 
# # Results
# summary(anova_ratio_domain_references)
# anova_ratio_domain_references_tidy
# anova_ratio_domain_references_eta
```

```{r}
# Mean domain references by category and group 
domain_category_anova_long <- domain_usage_anova %>%
  select(
    author,
    wolf_group,
    mainstream_domains,
    hyper_partisan_domains,
    ratio_mainstream,
    ratio_hyper_partisan
  ) %>%
  pivot_longer(
    cols = c(mainstream_domains, hyper_partisan_domains),
    names_to = "domain_category",
    values_to = "n_category_references"
  ) %>%
  mutate(
    domain_category = recode(
      domain_category,
      mainstream_domains = "Mainstream media",
      hyper_partisan_domains = "Hyper-partisan media"
    ),
    domain_category = factor(
      domain_category,
      levels = c("Mainstream media", "Hyper-partisan media")))

# Two-way ANOVA:
# - Does usage differ by group?
# - Does usage differ by category?
# - Does the category difference vary by group?
anova_category_group <- aov(
  n_category_references ~ wolf_group * domain_category,
  data = domain_category_anova_long)

anova_category_group_tidy <- broom::tidy(anova_category_group)
anova_category_group_eta <- eta_squared_from_aov(anova_category_group)

# Results
summary(anova_category_group)
anova_category_group_tidy
anova_category_group_eta
```

##### Plots

```{r}
domain_references_summary <- domain_usage_author %>%
  dplyr::mutate(
    wolf_group = dplyr::case_when(
      is_wolf == 1 ~ "Wolves",
      is_wolf == 0 ~ "All other parliamentarians",
      TRUE ~ NA_character_
    ),
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")
    )
  ) %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::group_by(wolf_group) %>%
  dplyr::summarise(
    group_mean_domain_references = mean(n_domains_references, na.rm = TRUE),
    group_sd_domain_references = sd(n_domains_references, na.rm = TRUE),
    .groups = "drop"
  )

p_mean_domain_references <- ggplot(
  domain_references_summary,
  aes(
    x = wolf_group,
    y = group_mean_domain_references,
    fill = wolf_group
  )
) +
  geom_col(width = 0.65) +
  geom_errorbar(
    aes(
      ymin = pmax(group_mean_domain_references - group_sd_domain_references, 0),
      ymax = group_mean_domain_references + group_sd_domain_references
    ),
    width = 0.1,
    linewidth = 0.8
  ) +
  scale_fill_manual(values = group_colors) +
  scale_y_continuous(labels = scales::comma) +
  labs(
    title = "Mean Number of Domain References by Group",
    x = NULL,
    y = ""
  ) +
  theme_wolves() +
  theme(
    legend.position = "none"
  )

p_mean_domain_references
```

```{r}
#### Plot: Mean domain references by category and group
domain_category_summary <- domain_usage_author %>%
  dplyr::mutate(
    wolf_group = dplyr::case_when(
      is_wolf == 1 ~ "Wolves",
      is_wolf == 0 ~ "All other parliamentarians",
      TRUE ~ NA_character_
    ),
    wolf_group = factor(
      wolf_group,
      levels = c("All other parliamentarians", "Wolves")
    )
  ) %>%
  dplyr::filter(!is.na(wolf_group)) %>%
  dplyr::select(
    author,
    wolf_group,
    mainstream_domains,
    hyper_partisan_domains,
  ) %>%
  tidyr::pivot_longer(
    cols = c(
      mainstream_domains,
      hyper_partisan_domains,
    ),
    names_to = "domain_category",
    values_to = "n_references"
  ) %>%
  dplyr::mutate(
    domain_category = dplyr::recode(
      domain_category,
      mainstream_domains = "Mainstream media",
      hyper_partisan_domains = "Hyper-partisan media"
    ),
    domain_category = factor(
      domain_category,
      levels = c(
        "Mainstream media",
        "Hyper-partisan media"))) %>%
  dplyr::group_by(wolf_group, domain_category) %>%
  dplyr::summarise(
    group_mean_references = mean(n_references, na.rm = TRUE),
    group_sd_references = sd(n_references, na.rm = TRUE),
    .groups = "drop")

p_mean_domain_categories <- ggplot(
  domain_category_summary,
  aes(
    x = domain_category,
    y = group_mean_references,
    fill = wolf_group)) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.65
  ) +
  geom_errorbar(
    aes(
      ymin = pmax(group_mean_references - group_sd_references, 0),
      ymax = group_mean_references + group_sd_references
    ),
    position = position_dodge(width = 0.8),
    width = 0.1,
    linewidth = 0.8
  ) +
  scale_fill_manual(values = group_colors) +
  scale_y_continuous(labels = scales::comma) +
  labs(
    title = "Mean Number of Domain References by Category",
    x = NULL,
    y = "",
    fill = NULL
  ) +
  theme_wolves()

p_mean_domain_categories
```

```{r}
#### Save
dir.create(output_path, recursive = TRUE, showWarnings = FALSE)

ggplot2::ggsave(
  filename = file.path(output_path, "mean_domain_references_by_group.png"),
  plot = p_mean_domain_references,
  width = 8,
  height = 6,
  dpi = 300
)

ggplot2::ggsave(
  filename = file.path(output_path, "mean_domain_references_by_category.png"),
  plot = p_mean_domain_categories,
  width = 8,
  height = 5,
  dpi = 300
)
```

# Curd's Analyses come here
*[Goal] Examine patterns of media domain references based on two dimensions:* 
*Exclusive vs. Shared Domains:* the extent to which media domain references appear across the political spectrum.
*Central vs. Fringe Domains:* the location within the political spectrum 

*Output:* (1.) Parliamentarians analysis (2.) Media domains analysis (to be shared in the appendix). 

