---
title: "VotingMachines"
author: "André K. Rodarte"
date: "2024-06-04"
output: html_document
---
# Set up
```{r setup, include=FALSE}
#install.packages("conText")
library(tidyverse)
library(tidytext)
library(dplyr)
library(here)

#Text
library(stopwords)
library(stringi)
library(tidyverse) 
library(stringr)   
library(tidytext)  
library(text2vec)  
library(widyr)     
library(irlba)     
library(umap)      
library(quanteda)  
library(conText)

# Domains
library(urltools)
library(purrr)
library(urltools)
library(httr)
library(httr2)
#devtools::install_github("ironholds/urltools")
  library("urltools")


# GPT Analysis
library(httr2)
library(dplyr)
library(purrr)
library(stringr)
library(progressr)
library(tibble)

#Word embeddings
library(Matrix)
library(igraph)

# Fonts
 # install.packages("showtext")
 # install.packages("sysfonts")
library(showtext)
library(sysfonts)
font_add_google("EB Garamond", "ebgaramond")
# Automatically use showtext for new plots
showtext_auto()

# Other
options(digits = 3)
set.seed(999) 

#Output
output_path <- "C:/Users/andre/Documents/GitHub/VotingMachines/_output"
```

```{r, warning=FALSE}
df_fb <- readr::read_csv('df_FB_processed.csv')
# Introduction of the bill: [11/10/2019]. See https://www.camara.leg.br/noticias/598363-pec-torna-obrigatorio-voto-impresso-em-eleicoes-no-brasil

#Inspect
# df_fb %>%
#   summarise(
#     first_timestamp = min(timestamp, na.rm = TRUE),
#     last_timestamp  = max(timestamp, na.rm = TRUE),
#     n_missing_timestamps = sum(is.na(timestamp))
#   )
```
# Domains Analysis
### URL Extraction
```{r}
df_fb <- df_fb %>%
  mutate(
    url_clean = if_else(
      !is.na(url_original) &
        str_detect(url_original, regex("facebook", ignore_case = TRUE)),
      NA_character_,
      url_original
    )
  )
```

```{r}
# Helper: ensure scheme present so regex and urltools behave consistently
add_scheme_if_missing <- function(x) {
  ifelse(is.na(x) | x == "", NA_character_,
         ifelse(str_detect(x, "^[a-zA-Z][a-zA-Z0-9+.-]*://"), x, paste0("https://", x)))
}

# Helper Functions
ensure_scheme <- function(x) {
  ifelse(
    is.na(x) | x == "",
    NA_character_,
    ifelse(
      str_detect(x, "^[a-zA-Z][a-zA-Z0-9+.-]*://"),
      x,
      paste0("https://", x)
    )
  )
}

extract_host <- function(url) {
  url2 <- add_scheme_if_missing(url)
  host <- ifelse(
    is.na(url2),
    NA_character_,
    sub("^https?://([^/]+).*", "\\1", url2, ignore.case = TRUE)
  )
  tolower(host)
}


# Registrable domain (eTLD+1), robust + vectorized
   # Handles NAs cleanly and emoves .com, .com.br, .org.br
   # Fixes cases like veja.abril.com.br → veja

registrable_domain <- function(url) {

  # ---- Normalize ----
  url_norm <- tolower(url)
  url_norm <- str_remove(url_norm, "^https?://")
  url_norm <- str_remove(url_norm, "^www[0-9]?\\.")
  url_norm <- str_remove(url_norm, "/.*$")

  extracted <- suffix_extract(url_norm)

  domain_full <- ifelse(
    is.na(extracted$domain) | is.na(extracted$suffix),
    NA_character_,
    paste0(extracted$domain, ".", extracted$suffix)
  )

  # Remove generic endings
  domain_simplified <- str_remove(domain_full, "\\.(com|org)(\\.br)?$")

  # ---- Host-level parsing ----
  host <- extract_host(url)
  host <- str_remove(host, "^www[0-9]?\\.")
  subdomain <- str_extract(host, "^[^.]+")

  domain_final <- domain_simplified

  # ---- GROUP RULES ----

  ## Abril (veja.abril.com.br → veja)
  domain_final <- ifelse(
    str_detect(host, "abril\\.com\\.br$") & subdomain != "abril",
    subdomain,
    domain_final
  )

  ## Globo (*.globo.com → brand.globo)
  domain_final <- ifelse(
    str_detect(host, "\\.globo\\.com$") & subdomain != "globo",
    paste0(subdomain, ".globo"),
    domain_final
  )

  ## UOL
  uol_verticals <- c(
    "noticias", "economia", "esporte", "entretenimento", "universa",
    "splash", "tilt", "vivabem", "nossa", "carros", "tv", "tab",
    "blog", "colunas", "educacao", "ciencia", "ecoa"
  )

  domain_final <- ifelse(
    str_detect(host, "\\.uol\\.com\\.br$") & subdomain != "uol",
    ifelse(subdomain %in% uol_verticals,
           paste0(subdomain, ".uol"),
           subdomain),
    domain_final
  )

  ## clicRBS (*.clicrbs.com.br → brand.clicrbs)
  domain_final <- ifelse(
    str_detect(host, "\\.clicrbs\\.com\\.br$") & subdomain != "clicrbs",
    paste0(subdomain, ".clicrbs"),
    domain_final
  )

  ## IG (*.ig.com.br → brand.ig)
  domain_final <- ifelse(
    str_detect(host, "\\.ig\\.com\\.br$") & subdomain != "ig",
    paste0(subdomain, ".ig"),
    domain_final
  )

  domain_final
}
```

```{r}
df_fb <- df_fb %>%
  mutate(
    url_fixed  = ensure_scheme(url_clean),
    host       = extract_host(url_fixed),
    domain     = registrable_domain(url_fixed)
  ) %>%
  select(-url_fixed)
```

```{r}
#Inspect
domains_top_overall <- df_fb %>%
  filter(!is.na(domain), domain != "") %>%
  count(domain, name = "n") %>%
  arrange(desc(n))

# Number of Link posts
sum(df_fb$type == "Link", na.rm = TRUE)
# Number of rows with an extracted domain
sum(!is.na(df_fb$domain) & df_fb$domain != "")
```
**Shortened URLs**
```{r}
library(progressr)

`%||%` <- function(a, b) if (is.null(a)) b else a

short_domains <- c("bit.ly", "buff.ly")
TIMEOUT_SEC <- 10
SLEEP_SEC   <- 0.15
RETRIES     <- 2
UA <- "Mozilla/5.0 (compatible; LinkUnshortener/1.0; +research)"

get_host <- function(u) {
  u <- tolower(u %||% "")
  u <- str_remove(u, "^https?://")
  u <- str_remove(u, "^www[0-9]?\\.")
  str_extract(u, "^[^/]+")
}

# Only called when we detect a Bitly preview/security page
extract_destination_from_html_fast <- function(html_text) {
  # Lightweight regex approach (no rvest):
  # grab absolute URLs from href="..."; drop bitly/buffly/bitly.com; pick longest.
  hrefs <- str_match_all(html_text, 'href\\s*=\\s*"((?:https?://)[^"]+)"')[[1]]
  if (nrow(hrefs) == 0) return(NA_character_)
  candidates <- unique(hrefs[, 2])

  candidates <- candidates[!str_detect(candidates, regex("bit\\.ly|buff\\.ly|bitly\\.com", ignore_case = TRUE))]
  if (length(candidates) == 0) return(NA_character_)

  candidates[which.max(nchar(candidates))]
}

resolve_short_url <- function(url,
                              timeout_sec = TIMEOUT_SEC,
                              retries = RETRIES,
                              sleep_sec = SLEEP_SEC) {

  if (is.na(url) || url == "") {
    return(c(url_final = NA_character_, method = "skip", status = NA_character_, error = NA_character_))
  }

  req_base <- request(url) %>%
    req_user_agent(UA) %>%
    req_timeout(timeout_sec) %>%
    req_retry(max_tries = retries + 1)

  # 1) HEAD with redirects
  head_out <- tryCatch({
    resp <- req_base %>% req_method("HEAD") %>% req_perform()
    final_url <- resp_url(resp)
    status <- as.character(resp_status(resp))
    c(url_final = final_url, method = "HEAD", status = status, error = NA_character_)
  }, error = function(e) {
    c(url_final = url, method = "HEAD_error", status = NA_character_, error = conditionMessage(e))
  })

  Sys.sleep(sleep_sec)

  # If resolved to non-shortener and not bitly.com, accept
  fh <- get_host(head_out["url_final"])
  if (!is.na(fh) &&
      !fh %in% short_domains &&
      !str_detect(head_out["url_final"], regex("bitly\\.com", ignore_case = TRUE))) {
    return(head_out)
  }

  # 2) GET only if we're still on shortener / bitly preview
  get_out <- tryCatch({
    resp <- req_base %>% req_method("GET") %>% req_perform()
    status <- as.character(resp_status(resp))
    final_url <- resp_url(resp)

    body_txt <- resp_body_string(resp)
    dest <- extract_destination_from_html_fast(body_txt)

    if (!is.na(dest) && dest != "") {
      c(url_final = dest, method = "GET_parse", status = status, error = NA_character_)
    } else {
      c(url_final = final_url, method = "GET_no_dest", status = status,
        error = "Could not extract destination from HTML (preview/security page or blocked).")
    }
  }, error = function(e) {
    c(url_final = url, method = "GET_error", status = NA_character_, error = conditionMessage(e))
  })

  Sys.sleep(sleep_sec)
  get_out
}

# ---- 1) unique short URLs only (small vector) ----
short_urls <- df_fb$url_clean[
  !is.na(df_fb$url_clean) &
    df_fb$url_clean != "" &
    df_fb$domain %in% short_domains
]
short_urls <- unique(short_urls)

# ---- 2) resolve with progress, produce ONE log object ----
handlers("progress")

with_progress({
  p <- progressor(along = short_urls)

  res_list <- map(short_urls, ~{
    p(message = "Unshortening bit.ly / buff.ly…")
    resolve_short_url(.x)
  })

  unshort_log <- tibble(
    url_short = short_urls,
    url_final = map_chr(res_list, ~ .x[["url_final"]]),
    method    = map_chr(res_list, ~ .x[["method"]]),
    status    = map_chr(res_list, ~ .x[["status"]]),
    error     = map_chr(res_list, ~ .x[["error"]])
  )
})

# ---- 3) overwrite url_clean via a fast named-lookup ----
resolved_ok <- with(unshort_log,
  !is.na(url_final) &
    url_final != url_short &
    !get_host(url_final) %in% short_domains &
    !str_detect(url_final, regex("bitly\\.com", ignore_case = TRUE))
)

lookup <- unshort_log$url_final
names(lookup) <- unshort_log$url_short
lookup_ok <- lookup[resolved_ok]

# Replace only for shortener rows; keep everything else unchanged
is_short_row <- df_fb$domain %in% short_domains &
  !is.na(df_fb$url_clean) & df_fb$url_clean != ""

df_fb$url_clean[is_short_row] <- ifelse(
  df_fb$url_clean[is_short_row] %in% names(lookup_ok),
  unname(lookup_ok[df_fb$url_clean[is_short_row]]),
  df_fb$url_clean[is_short_row]
)

# (Optional) keep the log for auditing:
 unshort_log %>% count(method, sort = TRUE)
```

I identified shortened links by examining URLs that appeared at least 50 times, yielding 221 Bitly and 57 Buff.ly links. These URLs were expanded using HTTP redirect resolution, successfully resolving 159 Bitly links. Unresolved links typically returned HTTP errors or were blocked by security restrictions, reflecting link decay and platform-level protections rather than data-processing limitations.

### Gephi

```{r}
norm <- function(x) trimws(tolower(x))

df_gephi_overall <- df_fb %>%
  dplyr::select(author, domain, party, PEC135, page_followers) %>%
  dplyr::mutate(
    author = norm(author),
    domain    = norm(domain)
  )

# EDGES (author → domain), with prefixed IDs 
edges_table_overall <- df_gephi_overall %>%
  dplyr::filter(
    !is.na(author), author != "",
    !is.na(domain),    domain    != ""
  ) %>%
  dplyr::transmute(
    Source = paste0("author::", author),
    Target = paste0("domain::", domain)
  )

# NODES
author_nodes_overall <- df_gephi_overall %>%
  dplyr::filter(!is.na(author), author != "") %>%
  dplyr::group_by(author) %>%
  dplyr::summarise(
    Id            = paste0("author::", dplyr::first(author)),
    Label         = dplyr::first(author),
    party         = dplyr::first(stats::na.omit(party)),
    PEC135        = dplyr::first(stats::na.omit(PEC135)),
    avg_followers = mean(page_followers, na.rm = TRUE),
    total_posts   = dplyr::n(),
    type          = "author",
    .groups       = "drop"
  ) %>%
  # bring in PDR_posts from fb_breakdown (author == author)
  dplyr::left_join(
    fb_breakdown %>%
      dplyr::transmute(
        author = author,
        PDR_posts = as.integer(PDR_posts)
      ),
    by = "author"
  ) %>%
  dplyr::mutate(
    party         = dplyr::if_else(is.na(party) | party == "", "NotApplicable", as.character(party)),
    PEC135        = as.integer(dplyr::if_else(is.na(PEC135), -1L, PEC135)),
    avg_followers = as.double(dplyr::if_else(is.na(avg_followers) | is.nan(avg_followers), 0, avg_followers)),
    total_posts   = as.integer(total_posts),

    # keep PDR_posts only when PEC135 == 1, else 0
    PDR_posts     = dplyr::if_else(PEC135 == 1L, dplyr::coalesce(PDR_posts, 0L), 0L)
  )

# DOMAIN NODES
domain_nodes_overall <- edges_table_overall %>%
  dplyr::distinct(Target) %>%
  dplyr::transmute(
    Id            = Target,
    Label         = sub("^domain::", "", Target),
    party         = "NotApplicable",
    PEC135        = -1L,
    avg_followers = 0,
    total_posts   = 0L,
    type          = "domain"
  )

nodes_table_overall <- dplyr::bind_rows(author_nodes_overall, domain_nodes_overall) %>%
  dplyr::distinct(Id, .keep_all = TRUE)

# EXPORT
write.csv(nodes_table_overall, "nodes_table_overall.csv", row.names = FALSE, na = "")
write.csv(edges_table_overall, "edges_table_overall.csv", row.names = FALSE, na = "")
```

### Domain categorization
```{r}
domain_analysis <- edges_table_overall %>%
  dplyr::mutate(domain = sub("^domain::", "", Target)) %>%
  dplyr::group_by(domain) %>%
  dplyr::summarise(n_pages = dplyr::n_distinct(Source), .groups = "drop") %>%
  dplyr::mutate(
    category = dplyr::case_when(

      # --- STATE DOMAINS ---
      stringr::str_detect(domain, stringr::fixed("leg.br")) |
        stringr::str_detect(domain, stringr::fixed(".gov")) |
        domain %in% c(
          "fapesp.br","fiocruz.br","mpf.mp.br","stf.jus.br","tse.jus.br",
          "tjpr.jus.br","tjsc.jus.br","tjap.jus.br","tjmg.jus.br","trf2.jus.br",
          "sabesp","prefeitura.rio","embrapa.br","sebrae"
        ) ~ "state_domains",

      # --- BLOGS ---
      stringr::str_detect(domain, stringr::regex("blog", ignore_case = TRUE)) |
        domain %in% c("cozinhabruta") ~ "blog_domains",

      # --- INDIVIDUAL ---
      domain %in% c(
      "capitaoaugusto", "carolinedetoni", "deputadojoaodaniel", "fernandapsol", "ivanvalente", "jilmartatto", "paulosampaio", "renatasouzapsol", "samiabomfim", "taliriapetrone"
  ) |
    n_pages == 1 ~ "individual_domains",

      # --- MAINSTREAM MEDIA ---
      domain %in% c(
        "folha","noticias.uol","band","g1.globo","oglobo.globo","estadao","bbc","washingtonpost","exame","extra.globo","folha1","gazetadopovo","glo.bo","lemonde.fr","nytimes","elpais","eldiario.es","correiobraziliense","clarin","cnn","cnnbrasil","istoedinheiro","istoe","reuters","theguardian","uol","valor","bbc.co.uk","bbc.in","elpais.com.uy","wsj","aosfatos","dailymail.co.uk","independent.co.uk","infomoney","sbt","sbtinterior","sbtnews","metropolenoticias", "telegraph.co.uk"
      ) |
        stringr::str_detect(domain, stringr::fixed(".uol")) |
        stringr::str_detect(domain, stringr::fixed(".globo")) ~ "mainstream_domains",

      # --- PLATFORMS ---
      domain %in% c(
        "google","youtube","linkedin","instagram","netflix","pscp.tv","tiktok",
        "whatsapp","youtu.be","substack","wikipedia","medium"
      ) ~ "platform_domains",

      # --- PARTY DOMAINS ---
      domain %in% c(
        "pt","ptnacamara","psol","ptceara","podemos","pcdobnacamara","pcdob","pcdobba","pdt","pdtnacamara","pps","prb10","prb10rj","republicanos10","republicanos1010","mulheresrepublicanas10","pl22","prbnacamara","pros","prosnacamara","psb40","psbnacamara","psd","psdb","psdbnacamara","psdcamara","psol50","psolcarioca","psolnacamara","pt-pr","ptb","ptbnacamara","ptnosenado","ptsaopaulo","ptsul","republicanos10nacamara","prb10sp","prbmg10","prbmulher10","pros90","psb40bahia","psc","psd-mg","psl-sp","psol50sp","psolbemviver","psolcamarasp","psolniteroi","psolsaude","psolsemente","pt-assembleia-sp","ptalagoas","ptbahia","ptcarioca","ptmt","ptnaalep","ptpaulista","ptsc","pv","republicanos10mg","republicanos10riopreto","republicanos10sp","solidariedaderj","cstpsol","democratas","novo","novonacamara","progressistas"
      ) ~ "party_domains",

      # --- IDEOLOGICAL ---
      domain %in% c(
        "cartacapital","jacobin","jovempan","piaui","midianinja","brasilsemmedo",
        "tercalivre","renovamidia","plenonews","romanews","esquerdadiario",
        "esquerdaonline","intercept","theintercept","veja","vejario","vejasp"
      ) ~ "ideological_domains",

      # --- RADIO ---
      domain %in% c(
        "radiobandeirantes","bandnewsfm","bandnewsfmcuritiba","bandnewsfmrio","radiocabiuna","radiocacula","radiocaxias","radioclubfm.net","radiocomunitariaclubefm","radioconvencao","radiocorredor","radiocostaverdefm","radiocruzdemalta","radiofmz","radiofolhabv","radiogeracao", "metropolitanoonline" ,"radioglobocampogrande","radioguaratuba","radiohora","radioiara","radiointegracaoam1180","radioipiranga","radiometropole","radionereuramos","radionovaprogresso","radiopanoramicafm","radiopeaobrasil","radioprata","radiosanfm","radiosantacruz","radiosaoluiz","radiosaopedrense","radioschroederfm","radiosoledade","radiotaquara","radioterena","radiotucunare","radioturmalina","radiouniversitariafm","radioveracruz","radiowebcp","94fm","anchor.fm","cbncaruaru","cbncuritiba","cbnlondrina","cbnmaringa","cbnrecife","cbnvitoria"
      ) ~ "radio_domains",

      # --- MOVEMENTS & CIVIL SOCIETY ---
      domain %in% c(
        "mises","mblnews","mst","catracalivre","coalizaonegrapordireitos",
        "coletivojuntas","eleicoesantirracistas","emdefesadofundoamazonia",
        "frentedaprimeirainfancia","frenteforabolsonaro","frentenacionaldeluta",
        "frenteparlamentarindigena","mulherespormaisdireitos","mundonegro.inf.br",
        "mundosindical","oxfam",
        "febraban","fecomercio-se","sinasefebrasilia","sindautoescola",
        "sindbancarios","sindcefetmg","sindcop","sindesvdf","sindifes",
        "sindifisconacional","sindilojas-sp","sindilojasgravatai","sindipetro",
        "sindipetroprsc","sindipetrorn","sindiprev-se","sindiserfrs","sindmepa",
        "sindsaudesp","sindsprev","sinffazfisco","sinjorba","sinpofesc","sinposba",
        "sinprfmg","sinproesemma","sinprors","sinssp","sinteal","sintectrj",
        "sintufrj","sissaude","sistemafaep","cutbrasilia",
        "cut","cutrs","greenpeace","almapreta","appsindicato",
        "casomarielleeanderson","consultaquilombolaja","democraciasocialista",
        "institutomariellefranco","movimentorevista","mtst",
        "observatoriodademocracia","observatoriodaimprensa",
        "observatoriodatelevisao","observatoriodoconhecimento","observatoriog",
        "rendabasica"
      ) ~ "movements_civil_society",

      # --- ONLINE NEWS ---
      domain %in% c(
        "nexojornal","oantagonista","poder360","buzzfeed","yahoo",
        "huffpost","huffpostbrasil","r7","terra","terrabrasilnoticias"
      ) ~ "online_news_domains",

      TRUE ~ "other_domains"
    )
  ) %>%
  dplyr::group_by(category) %>%
  dplyr::summarise(domains = list(sort(unique(domain))), .groups = "drop") %>%
  dplyr::mutate(
    category = factor(
      category,
      levels = c(
        "individual_domains",
        "mainstream_domains",
        "online_news_domains",
        "party_domains",
        "ideological_domains",
        "movements_civil_society",
        "radio_domains",
        "platform_domains",
        "blog_domains",
        "state_domains",
        "other_domains"
      )
    )
  ) %>%
  dplyr::arrange(category) %>%
  dplyr::mutate(category = as.character(category))

domain_analysis_visualization <- domain_analysis %>%
  dplyr::mutate(domains = vapply(domains, paste, collapse = ", ", FUN.VALUE = character(1)))
```

## Participation breakdown

```{r}
fb_breakdown <- df_fb %>%
  arrange(author, timestamp) %>%
  group_by(author) %>%
  summarise(
    total_posts = n(),
    avg_interactions = round(mean(interactions, na.rm = TRUE), 2),
    sd_interactions  = round(sd(interactions, na.rm = TRUE), 2),
    native_video_posts = sum(type == "Native Video", na.rm = TRUE),
    photo_posts = sum(type == "Photo", na.rm = TRUE),
    live_video_complete_posts = sum(type == "Live Video Complete", na.rm = TRUE),
    link_posts = sum(type == "Link", na.rm = TRUE),
    youtube_posts = sum(type == "YouTube", na.rm = TRUE),
    followers_start = first(page_followers[!is.na(page_followers)]),
    followers_end   = last(page_followers[!is.na(page_followers)]),
    followers_change = followers_end - followers_start,
    .groups = "drop")
  # ) %>%
  # left_join(author_pec, by = "author")
```

```{r}
# Build a lookup table (domain -> category)
domain_lookup <- domain_analysis_visualization %>%
  mutate(
    category = str_trim(category),
    domains  = str_split(domains, "\\s*,\\s*")  
  ) %>%
  unnest(domains) %>%
  transmute(
    domain   = str_to_lower(str_trim(domains)),
    category = category
  ) %>%
  filter(!is.na(domain), domain != "") %>%
  distinct(domain, .keep_all = TRUE)

# Count, per author, how many times they referenced each category
domain_counts_by_author <- GPT_processed_data %>%
  mutate(domain = str_to_lower(str_trim(domain))) %>%
  filter(!is.na(domain), domain != "") %>%
  inner_join(domain_lookup, by = "domain") %>%
  count(author, category, name = "n_domain_refs") %>%
  tidyr::pivot_wider(
    names_from  = category,
    values_from = n_domain_refs,
    values_fill = 0
  )

# Join into fb_breakdown
fb_breakdown <- fb_breakdown %>%
  left_join(domain_counts_by_author, by = "author") %>%
  mutate(
    # ensure these exist even for authors with zero matched domains
    mainstream_domains   = coalesce(mainstream_domains, 0L),
    individual_domains   = coalesce(individual_domains, 0L),
    online_news_domains  = coalesce(online_news_domains, 0L),
    party_domains        = coalesce(party_domains, 0L),
    ideological_domains  = coalesce(ideological_domains, 0L),
    platform_domains     = coalesce(platform_domains, 0L),
    blog_domains         = coalesce(blog_domains, 0L),
    state_domains        = coalesce(state_domains, 0L)
  )
```

```{r}
font_add_google("EB Garamond", "ebgaramond")
showtext_auto()

# keep only PEC135 groups 0 and 1 (and keep their existing factor order)
tmp_levels <- c("0", "1", "3", "NA")

content_summary_total_wide <- fb_breakdown %>%
  mutate(
    pec_group = factor(
      dplyr::case_when(
        is.na(PEC135) ~ "NA",
        TRUE ~ as.character(PEC135)
      ),
      levels = tmp_levels
    ),
    side = dplyr::recode(pec_group, `0` = "Against PEC", `1` = "Pro PEC")
  ) %>%
  filter(pec_group %in% c("0", "1")) %>%
  group_by(pec_group, side) %>%
  summarise(
    avg_posts = mean(total_posts, na.rm = TRUE),
    sd_posts  = sd(total_posts, na.rm = TRUE),

    mean_avg_interactions = mean(avg_interactions, na.rm = TRUE),
    sd_avg_interactions   = sd(avg_interactions, na.rm = TRUE),

    avg_follower_change = mean(followers_change, na.rm = TRUE),
    sd_follower_change  = sd(followers_change, na.rm = TRUE),
    .groups = "drop"
  )

content_comparison_total <- bind_rows(
  content_summary_total_wide %>%
    transmute(side, metric = "Average Posts",
              avg = avg_posts, sd = sd_posts),

  content_summary_total_wide %>%
    transmute(side, metric = "Average Interactions",
              avg = mean_avg_interactions, sd = sd_avg_interactions),

  content_summary_total_wide %>%
    transmute(side, metric = "Average Follower Growth",
              avg = avg_follower_change, sd = sd_follower_change)
)

# quick check table
content_comparison_total %>%
  filter(metric == "Average Interactions") %>%
  select(side, avg, sd)

# plot (keep colors aligned with original 0/1 ordering by controlling factor levels)
content_comparison_total <- content_comparison_total %>%
  mutate(side = factor(side, levels = c("Against PEC", "Pro PEC")))

ggplot(content_comparison_total, aes(x = side, y = avg, fill = side)) +
  geom_bar(stat = "identity", width = 0.6) +
  geom_errorbar(
    aes(ymin = avg - sd, ymax = avg + sd),
    width = 0.2,
    linewidth = 0.8
  ) +
  facet_wrap(~ metric, scales = "free_y") +
  labs(
    title = "Participation Breakdown",
    x = "", y = ""
  ) +
  theme_minimal(base_family = "garamond") +
  theme(
    text = element_text(family = "ebgaramond"),
    axis.text.x = element_text(size = 30),
    axis.text.y = element_text(size = 30),
    legend.position = "none",
    plot.title = element_text(size = 40, face = "bold"),
    strip.text = element_text(size = 30)
  )
```

```{r}
#C:\Users\andre\Documents\GitHub\VotingMachines\output
ggsave(
  filename = "Participation_Breakdown_PEC-GROUPS.png",
  path = "C:/Users/andre/Documents/GitHub/VotingMachines/output",
  plot = last_plot(),
  device = "png",
  width = 10,
  height = 6,
  dpi = 300
)
```

```{r}
content_summary_total <- fb_breakdown %>%
  mutate(
    side = factor(
      case_when(
        is.na(PEC135) ~ "NA",
        TRUE ~ as.character(PEC135)
      ),
      levels = c("0", "1", "3", "NA")
    )
  ) %>%
  filter(side %in% c("0", "1")) %>%
  group_by(side) %>%
  summarise(
    photo_posts        = sum(photo_posts, na.rm = TRUE),
    native_video_posts = sum(native_video_posts, na.rm = TRUE),
    link_posts         = sum(link_posts, na.rm = TRUE),
    youtube_posts      = sum(youtube_posts, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_longer(cols = -side, names_to = "type", values_to = "count") %>%
  mutate(
    type = recode(type,
      "photo_posts"        = "Photo Posts",
      "link_posts"         = "Posts with Links",
      "native_video_posts" = "Native Videos",
      "youtube_posts"      = "YouTube Links"
    ),
    side_label = dplyr::recode(side, `0` = "Against", `1` = "Pro")
  )

ggplot(content_summary_total, aes(x = type, y = count, fill = side_label)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(
    title = "Comparison of Content Format Usage",
    y = "Number of Posts",
    x = " "
  ) +
  theme_minimal(base_family = "garamond") +
  theme(
    text = element_text(family = "ebgaramond"),
    plot.title = element_text(size = 30, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 20),
    legend.title = element_blank(),
    legend.text = element_text(size = 20)
  )
```

```{r}
domain_rates_total <- fb_breakdown %>%
  mutate(
    side = factor(
      case_when(
        is.na(PEC135) ~ "NA",
        TRUE ~ as.character(PEC135)
      ),
      levels = c("0", "1", "3", "NA")
    )
  ) %>%
  filter(side %in% c("0", "1")) %>%
  group_by(side) %>%
  summarise(
    total_posts = sum(total_posts, na.rm = TRUE),

    mainstream_domains  = sum(mainstream_domains,  na.rm = TRUE),
    individual_domains  = sum(individual_domains,  na.rm = TRUE),
    party_domains       = sum(party_domains,       na.rm = TRUE),
    platform_domains    = sum(platform_domains,    na.rm = TRUE),
    blog_domains        = sum(blog_domains,        na.rm = TRUE),
    state_domains       = sum(state_domains,       na.rm = TRUE),
    radio_domains       = sum(radio_domains,       na.rm = TRUE),
    movements_civil_society = sum(movements_civil_society, na.rm = TRUE),

    # keep these for total_domains, but we’ll hide them later
    ideological_domains = sum(ideological_domains, na.rm = TRUE),
    online_news_domains = sum(online_news_domains, na.rm = TRUE),
    other_domains       = sum(other_domains,       na.rm = TRUE),

    total_domains = sum(
      mainstream_domains, individual_domains, online_news_domains, party_domains,
      ideological_domains, platform_domains, blog_domains, state_domains,
      radio_domains, movements_civil_society, other_domains,
      na.rm = TRUE
    ),
    .groups = "drop"
  ) %>%
  mutate(
    across(
      c(total_domains, mainstream_domains, individual_domains, party_domains,
        platform_domains, blog_domains, state_domains,
        radio_domains, movements_civil_society,
        ideological_domains, online_news_domains, other_domains),
      ~ 100 * .x / total_posts
    )
  ) %>%
  select(-total_posts) %>%
  
  # REMOVE UNFINISHED COLUMNS
  select(-ideological_domains, -online_news_domains, -other_domains) %>%
  pivot_longer(cols = -side, names_to = "domain_type", values_to = "rate_per_100") %>%
  
  
  mutate(
    domain_type = recode(domain_type,
      "total_domains"      = "Total domains",
      "mainstream_domains" = "Mainstream domains",
      "individual_domains" = "Individual domains",
      "party_domains"      = "Party domains",
      "platform_domains"   = "Platform domains",
      "blog_domains"       = "Blog domains",
      "state_domains"      = "State domains",
      "radio_domains"      = "Radio domains",
      "movements_civil_society" = "Movements & civil society"
    ),
    side_label = dplyr::recode(side, `0` = "Against", `1` = "Pro")
  )


ggplot(domain_rates_total, aes(x = domain_type, y = rate_per_100, fill = side_label)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_number(accuracy = 0.1, suffix = " per 100")) +
  labs(
    title = "Domain Mentions (Rates per 100 Posts)",
    y = "Rate",
    x = " "
  ) +
  theme_minimal(base_family = "garamond") +
  theme(
    text = element_text(family = "ebgaramond"),
    plot.title = element_text(size = 40, face = "bold"),
    axis.title = element_text(size = 30),
    axis.text.x = element_text(size = 30, angle = 30, hjust = 1),
    axis.text.y = element_text(size = 30),
    legend.title = element_blank(),
    legend.text = element_text(size = 30)
  )
```

```{r}
ggsave(
  filename = "Domains_Breakdown_PEC-GROUPS.png",
  path = "C:/Users/andre/Documents/GitHub/VotingMachines/output",
  plot = last_plot(),
  device = "png",
  width = 10,
  height = 6,
  dpi = 300
)
```

## Communication Style Breakdown
```{r}
# Create dominant_style
df_fb <- df_fb %>%
  mutate(
    dominant_style = case_when(
      parochial_matches == 0 &
        programmatic_matches == 0 &
        propagandistic_matches == 0 ~ "No match",

      parochial_matches > programmatic_matches &
        parochial_matches > propagandistic_matches ~ "Parochial",

      programmatic_matches > parochial_matches &
        programmatic_matches > propagandistic_matches ~ "Programmatic",

      propagandistic_matches > parochial_matches &
        propagandistic_matches > programmatic_matches ~ "Propagandistic",

      TRUE ~ "Tie"
    ),
    dominant_style = factor(
      dominant_style,
      levels = c("Parochial", "Programmatic", "Propagandistic", "Tie", "No match")
    )
  )

```

# Election Integrity Subset

## Regex Filtering
```{r}
# List of keywords
voting_keywords <- unique(c(

  ## PEC 135 / voto impresso debate (labels + shorthand)
  "pec 135", "pec135", "pec 13519", "pec 135 2019", "13519", "1352019",

  ## urnas eletronicas (generic + phrase + no-space)
  "urna", "urnas", "urna eletronica", "urnas eletronicas", "urnaeletronica",

  ## voto impresso / auditavel (phrase + no-space + broad tokens)
  "voto impresso", "votos impressos",
  "voto auditavel", "votos auditaveis",
  "votoimpresso", "votoauditavel",

  ## fraude / manipulacao / irregularidades (broad + phrase + no-space)
  "fraude", "fraudar", "fraudado", "fraudada", "fraudados", "fraudadas",
  "fraude eleitoral", "fraudes eleitorais",
  "fraude nas urnas", "eleicoes fraudadas",
  "fraudar urnas", "fraudar as eleicoes",
  "urnasfraudadas", "urnafraudada",
  "fraudenasurnas",

  ## auditoria / recontagem (process terms)
  "auditoria", "auditar", "auditagem", 
  "apuracao dos votos", "apurar votos", 
  "recontagem de votos", "recontar votos",

  ## seguranca / hackers / vulnerabilidades 
  "hacker", "hackers", "hackear", "hackeado",
  "ataque", "ataques", "ataque hacker",
  "invasao", "invadir",
  "codigofonte", "codigo fonte",
  "golpe eleitoral",
  
  ## instituicoes / atores (often invoked in integrity claims)
  "tse", "justica eleitoral", "smartmatic"
  ))
```

```{r}
# FACEBOOK
# Filter the dataframe to keep rows containing at least one of the keywords
keywords_pattern <- paste(voting_keywords, collapse = "|")

df_fb_filtered <- df_fb %>%
  filter(str_detect(text_combined, keywords_pattern))
```

## GPT Filtering

#### Sample

```{r}
# Load your API key
my_API <- "...."

`%||%` <- function(a,b) if (is.null(a)) b else a
```

#### Filtered DF
```{r}
# API caller
gpt_model <- "gpt-4.1-mini"
# JSON API caller
hey_chatGPT_json <- function(prompt_text,
                             api_key = my_API,
                             model = "gpt-4.1-mini",
                             temperature = 0,
                             max_tries = 6,
                             max_tokens = 80,
                             schema_name = "classification",
                             schema) {
  
  attempt <- 1
  
  repeat {
    
    resp <- tryCatch({
      request("https://api.openai.com/v1/chat/completions") %>%
        req_auth_bearer_token(api_key) %>%
        req_timeout(120) %>%
        req_body_json(
          list(
            model = model,
            temperature = temperature,
            max_tokens = max_tokens,
            messages = list(
              list(
                role = "user",
                content = prompt_text
              )
            ),
            response_format = list(
              type = "json_schema",
              json_schema = list(
                name = schema_name,
                strict = TRUE,
                schema = schema
              )
            )
          ),
          auto_unbox = TRUE
        ) %>%
        req_perform()
    }, error = function(e) {
      message("API attempt ", attempt, " failed: ", conditionMessage(e))
      NULL
    })
    
    if (!is.null(resp)) {
      content <- tryCatch(
        resp_body_json(resp)$choices[[1]]$message$content,
        error = function(e) {
          message("Could not extract response content: ", conditionMessage(e))
          NULL
        }
      )
      
      if (!is.null(content) && nzchar(content)) {
        parsed <- tryCatch(
          jsonlite::fromJSON(content),
          error = function(e) {
            message("Could not parse JSON content: ", conditionMessage(e))
            NULL
          }
        )
        
        if (!is.null(parsed)) {
          return(parsed)
        }
      }
    }
    
    if (attempt >= max_tries) return(NULL)
    
    Sys.sleep(min(2^attempt, 30))
    attempt <- attempt + 1
  }
}

# --- Prompt builders ---
build_prompt_q12 <- function(post_text) {
  paste0(
    "Voce esta analisando postagens de politicos brasileiros.\n\n",
    
    "Classifique a postagem respondendo a DUAS perguntas binarias.\n\n",
    
    "Q1: A postagem e sobre o funcionamento institucional ou tecnico do sistema/processo eleitoral?\n",
    "Codifique Q1=1 apenas se a postagem discutir pelo menos um dos seguintes temas:\n",
    "- PEC 135/2019;\n",
    "- voto impresso ou voto auditavel;\n",
    "- urnas eletronicas;\n",
    "- cedulas ou sistema de votacao;\n",
    "- auditoria das urnas ou dos votos;\n",
    "- apuracao, contagem, recontagem, transmissao ou totalizacao de votos;\n",
    "- TSE/TRE como autoridades que organizam, fiscalizam ou validam a eleicao;\n",
    "- seguranca das urnas, ataques hackers contra urnas ou sistemas eleitorais;\n",
    "- legitimidade do processo de votacao, apuracao, totalizacao ou certificacao dos resultados.\n\n",
    
    "Q2: Se Q1=1, a postagem questiona a integridade, seguranca, confiabilidade ou legitimidade do sistema/processo eleitoral?\n",
    "Codifique Q2=1 apenas se a suspeita recair sobre urnas, voto eletronico, voto impresso/auditavel,\n",
    "auditoria, apuracao, contagem, recontagem, transmissao, totalizacao, certificacao,\n",
    "TSE/TRE ou legitimidade dos resultados oficiais.\n\n",
    
    "EXCLUA, codificando Q1=0 e Q2=0, postagens que tratem apenas de:\n",
    "- corrupcao de candidatos;\n",
    "- lavagem de dinheiro;\n",
    "- fundo partidario ou fundo eleitoral;\n",
    "- difamacao ou propaganda eleitoral;\n",
    "- processos judiciais contra candidatos;\n",
    
    "REGRA CENTRAL:\n",
    "Mesmo que a postagem use palavras como fraude, corrupcao, eleicao, urnas ou resultado,\n",
    "codifique Q2=0 se ela nao questionar diretamente o sistema de votacao, apuracao,\n",
    "auditoria, totalizacao, certificacao, TSE/TRE ou legitimidade dos resultados oficiais.\n\n",
    
    
    "EXEMPLOS POSITIVOS:\n",
    "- urnas eletronicas podem ser fraudadas: Q1=1 Q2=1;\n",
    "- defesa do voto impresso/auditavel por falta de confiabilidade das urnas: Q1=1 Q2=1;\n",
    "- informacao institucional sobre data/local de votacao, sem questionar integridade: Q1=1 Q2=0.\n\n",
    
    "Responda apenas no JSON solicitado.\n\n",
    
    "POST:\n",
    post_text
  )
}

build_prompt_q3 <- function(post_text) {
  paste0(
    "Voce esta analisando uma postagem que JA foi classificada como questionamento da integridade,\n",
    "seguranca, confiabilidade ou legitimidade do sistema/processo eleitoral brasileiro.\n\n",
    
    "Q3: A postagem menciona ou usa exemplos de OUTROS PAISES para discutir integridade,\n",
    "fraude, seguranca, confiabilidade ou legitimidade de urnas, voto, apuracao,\n",
    "auditoria, totalizacao ou resultados eleitorais?\n\n",
    
    "Codifique Q3=1 se a postagem mencionar explicitamente outro pais, por exemplo EUA,\n",
    "Estados Unidos, Venezuela, Argentina, Alemanha, Paraguai, Bolivia, etc., como comparacao,\n",
    "exemplo ou justificativa em discussao sobre integridade eleitoral.\n\n",
    
    "Codifique Q3=0 se a postagem tratar apenas do Brasil ou nao usar outro pais como exemplo.\n\n",
    
    "Responda apenas no JSON solicitado.\n\n",
    
    "POST:\n",
    post_text
  )
}

# --- Parsers (robust to small variations) ---
schema_q12 <- list(
  type = "object",
  additionalProperties = FALSE,
  properties = list(
    Q1 = list(type = "integer", enum = list(0, 1)),
    Q2 = list(type = "integer", enum = list(0, 1))
  ),
  required = list("Q1", "Q2"))

schema_q3 <- list(
  type = "object",
  additionalProperties = FALSE,
  properties = list(
    Q3 = list(type = "integer", enum = list(0, 1))
  ),
  required = list("Q3"))


parse_q12_json <- function(x) {
  if (is.null(x)) {
    return(tibble(
      Q1 = NA_integer_,
      Q2 = NA_integer_,
      GPT_Q12_success = FALSE
    ))
  }
  
  q1 <- suppressWarnings(as.integer(x$Q1))
  q2 <- suppressWarnings(as.integer(x$Q2))
  
  if (!is.na(q1) && q1 == 0L) q2 <- 0L
  
  tibble(
    Q1 = q1,
    Q2 = q2,
    GPT_Q12_success = !is.na(q1) & !is.na(q2)
  )
}


parse_q3_json <- function(x) {
  if (is.null(x)) {
    return(tibble(
      Q3 = NA_integer_,
      GPT_Q3_success = FALSE
    ))
  }
  q3 <- suppressWarnings(as.integer(x$Q3))
  tibble(
    Q3 = q3,
    GPT_Q3_success = !is.na(q3)
  )
}


# --- Wrappers that return 1-row tibbles ---
hey_chatGPT_Q12 <- function(post_text,
                            api_key = my_API,
                            model = gpt_model,
                            temperature = 0,
                            max_tries = 6) {
  
  prompt <- build_prompt_q12(post_text)
  
  out <- hey_chatGPT_json(
    prompt_text = prompt,
    api_key = api_key,
    model = model,
    temperature = temperature,
    max_tries = max_tries,
    max_tokens = 80,
    schema_name = "q12_classification",
    schema = schema_q12
  )
  
  parse_q12_json(out)
}


hey_chatGPT_Q3 <- function(post_text,
                           api_key = my_API,
                           model = gpt_model,
                           temperature = 0,
                           max_tries = 6) {
  
  prompt <- build_prompt_q3(post_text)
  
  out <- hey_chatGPT_json(
    prompt_text = prompt,
    api_key = api_key,
    model = model,
    temperature = temperature,
    max_tries = max_tries,
    max_tokens = 40,
    schema_name = "q3_classification",
    schema = schema_q3
  )
  
  parse_q3_json(out)
}
```

*Sample*
```{r}
df_sample <- df_fb_filtered %>%
  filter(!is.na(text_combined), text_combined != "") %>%
  slice_sample(n = 150)

# library(progressr)
handlers("progress")

with_progress({
  p <- progressor(along = df_sample$text_combined)

  df_sample <- df_sample %>%
    mutate(
      GPT_Q12_raw = map(
        text_combined,
        ~{
          p(message = "Classificando Q1/Q2...")
          hey_chatGPT_Q12(.x)
        }
      )
    ) %>%
    unnest_wider(GPT_Q12_raw) %>%
    mutate(
      Q1 = as.integer(replace_na(Q1, 0L)),
      Q2 = as.integer(replace_na(Q2, 0L)),
      Q2 = if_else(Q1 == 0L, 0L, Q2)
    )
})

#Q3
with_progress({
  idx_need_q3 <- which(df_sample$Q1 == 1L & df_sample$Q2 == 1L)
  p <- progressor(along = idx_need_q3)

  df_sample$Q3 <- 0L
  df_sample$GPT_Q3_success <- NA

  if (length(idx_need_q3) > 0) {
    q3_tbl <- map_dfr(
      idx_need_q3,
      ~{
        p(message = "Classificando Q3...")
        out <- hey_chatGPT_Q3(df_sample$text_combined[.x])
        tibble(row_index = .x) %>%
          bind_cols(out)
      }
    )

    df_sample$Q3[q3_tbl$row_index] <- as.integer(replace_na(q3_tbl$Q3, 0L))
    df_sample$GPT_Q3_success[q3_tbl$row_index] <- q3_tbl$GPT_Q3_success
  }
})

# ---- Check distributions ----
df_sample %>% count(Q1)
df_sample %>% count(Q2)
df_sample %>% count(Q3)

# Optional: check the full decision-tree combinations
df_sample %>% count(Q1, Q2, Q3)
```

*Full data*
```{r}
handlers("progress")  # once per session
 #  Create folder for intermediate outputs
 dir.create("_openai_classification_cache", showWarnings = FALSE)
 checkpoint_q12 <- "_openai_classification_cache/df_fb_filtered_q12_checkpoint.rds"
 checkpoint_q3  <- "_openai_classification_cache/df_fb_filtered_q123_checkpoint.rds"
 
# ---------------------------
# PASS 1: Q1 + Q2 for all posts
# ---------------------------
if (file.exists(checkpoint_q12)) {
  
  df_fb_filtered <- readr::read_rds(checkpoint_q12)
  
} else {
  
  df_fb_filtered <- df_fb_filtered %>%
    mutate(
      row_index = row_number(),
      Q1 = NA_integer_,
      Q2 = NA_integer_,
      GPT_Q12_success = FALSE
    )
}

batch_size <- 100
idx_need_q12 <- which((is.na(df_fb_filtered$Q1) | is.na(df_fb_filtered$Q2)) &
    !is.na(df_fb_filtered$text_combined) &
    stringr::str_squish(df_fb_filtered$text_combined) != "")

q12_batches <- split(idx_need_q12, ceiling(seq_along(idx_need_q12) / batch_size))

with_progress({
  
  p <- progressor(along = idx_need_q12)
  
  for (batch in q12_batches) {
    
    q12_tbl <- map_dfr(
      batch,
      ~{
        p(message = "PASSO 1/2: Classificando Q1 e Q2...")
        
        out <- hey_chatGPT_Q12(
          post_text = df_fb_filtered$text_combined[.x],
          model = gpt_model
        )
        
        tibble(row_index = .x) %>%
          bind_cols(out)
      }
    )
    
    df_fb_filtered$Q1[q12_tbl$row_index] <- q12_tbl$Q1
    df_fb_filtered$Q2[q12_tbl$row_index] <- q12_tbl$Q2
    df_fb_filtered$GPT_Q12_success[q12_tbl$row_index] <- q12_tbl$GPT_Q12_success
    
    readr::write_rds(df_fb_filtered, checkpoint_q12)
  }
})

# Conservative treatment of failures:
# Keep the success indicator for auditing, but code failed cases as 0 for downstream filtering.
df_fb_filtered <- df_fb_filtered %>%
  mutate(
    Q1 = as.integer(replace_na(Q1, 0L)),
    Q2 = as.integer(replace_na(Q2, 0L)),
    Q2 = if_else(Q1 == 0L, 0L, Q2)
  )

# readr::write_rds(df_fb_filtered, checkpoint_q12)


# ---------------------------
# PASS 2: Q3 only if Q1==1 & Q2==1
# ---------------------------

if (file.exists(checkpoint_q3)) {
  
  df_fb_filtered <- readr::read_rds(checkpoint_q3)
  
} else {
  
  if (!"Q3" %in% names(df_fb_filtered)) {
    df_fb_filtered$Q3 <- 0L
  }
  
  if (!"GPT_Q3_success" %in% names(df_fb_filtered)) {
    df_fb_filtered$GPT_Q3_success <- NA
  }
}

idx_need_q3 <- which(
  df_fb_filtered$Q1 == 1L &
    df_fb_filtered$Q2 == 1L &
    (is.na(df_fb_filtered$Q3) | is.na(df_fb_filtered$GPT_Q3_success))
)

q3_batches <- split(idx_need_q3, ceiling(seq_along(idx_need_q3) / batch_size))

with_progress({
  
  p <- progressor(along = idx_need_q3)
  
  if (length(idx_need_q3) > 0) {
    
    for (batch in q3_batches) {
      
      q3_tbl <- map_dfr(
        batch,
        ~{
          p(message = "PASSO 2/2: Classificando Q3...")
          
          out <- hey_chatGPT_Q3(
            post_text = df_fb_filtered$text_combined[.x],
            model = gpt_model
          )
          
          tibble(row_index = .x) %>%
            bind_cols(out)
        }
      )
      
      df_fb_filtered$Q3[q3_tbl$row_index] <- as.integer(replace_na(q3_tbl$Q3, 0L))
      df_fb_filtered$GPT_Q3_success[q3_tbl$row_index] <- q3_tbl$GPT_Q3_success
      
      readr::write_rds(df_fb_filtered, checkpoint_q3)
    }
  }
})

# Everyone who is not Q1=1 & Q2=1 should have Q3=0
df_fb_filtered <- df_fb_filtered %>%
  mutate(
    Q3 = if_else(Q1 == 1L & Q2 == 1L, as.integer(replace_na(Q3, 0L)), 0L)
  )

# readr::write_rds(df_fb_filtered, checkpoint_q3)
```

```{r}
df_fb_filtered %>% count(Q1)
df_fb_filtered %>% count(Q2)
df_fb_filtered %>% count(Q1, Q2, Q3)

# Should be zero
df_fb_filtered %>%
  filter(Q2 == 1L, Q1 != 1L) %>%
  nrow()

# API failures
df_fb_filtered %>%
  summarise(
    n_posts = n(),
    q12_failures = sum(!GPT_Q12_success, na.rm = TRUE),
    q3_needed = sum(Q1 == 1L & Q2 == 1L),
    q3_failures = sum(Q1 == 1L & Q2 == 1L & !GPT_Q3_success, na.rm = TRUE)
  )
```

# Descriptive Analysis
## Election Posts Subset
```{r}
df_filtered_breakdown <- df_fb_filtered %>%
  summarise(
    PEC135 = {
      x <- unique(PEC135[!is.na(PEC135)])
      if (length(x) == 0) NA_real_ else x[1]
    },

    Q1_posts = sum(Q1 == 1, na.rm = TRUE),
    Q2_posts = sum(Q2 == 1, na.rm = TRUE),
    Q3_posts = sum(Q3 == 1, na.rm = TRUE),

    native_video_posts = sum(type == "Native Video", na.rm = TRUE),
    photo_posts = sum(type == "Photo", na.rm = TRUE),
    live_video_complete_posts = sum(type == "Live Video Complete", na.rm = TRUE),
    link_posts = sum(type == "Link", na.rm = TRUE),
    youtube_posts = sum(type == "YouTube", na.rm = TRUE),

    party = {
      x <- unique(party[!is.na(party)])
      if (length(x) == 0) NA_character_ else x[1]
    },

    party_ideology = {
      x <- unique(ideology_2021[!is.na(ideology_2021)])
      if (length(x) == 0) NA_real_ else x[1]
    },

    domain = {
      x <- sort(unique(domain[!is.na(domain)]))
      if (length(x) == 0) NA_character_ else paste(x, collapse = ";")
    },

    .by = author
  )
```

## Overall Data
```{r}
fb_breakdown <- df_fb %>%
  arrange(author, timestamp) %>%
  summarise(
    PEC135 = {
      x <- unique(PEC135[!is.na(PEC135)])
      if (length(x) == 0) NA_real_ else x[1]
    },

    native_video_posts = sum(type == "Native Video", na.rm = TRUE),
    photo_posts = sum(type == "Photo", na.rm = TRUE),
    live_video_complete_posts = sum(type == "Live Video Complete", na.rm = TRUE),
    link_posts = sum(type == "Link", na.rm = TRUE),
    youtube_posts = sum(type == "YouTube", na.rm = TRUE),

    state = {
      x <- unique(state[!is.na(state)])
      if (length(x) == 0) NA_character_ else x[1]
    },

    party = {
      x <- unique(party[!is.na(party)])
      if (length(x) == 0) NA_character_ else x[1]
    },

    party_ideology = {
      x <- unique(ideology_2021[!is.na(ideology_2021)])
      if (length(x) == 0) NA_real_ else x[1]
    },

    hashtags = {
      x <- unique(trimws(unlist(strsplit(hashtags[!is.na(hashtags)], ","))))
      x <- sort(x[x != ""])
      if (length(x) == 0) NA_character_ else paste(x, collapse = ";")
    },

    domain = {
      x <- sort(unique(domain[!is.na(domain)]))
      if (length(x) == 0) NA_character_ else paste(x, collapse = ";")
    },

    total_posts = n(),

    avg_engagement = mean(engagement, na.rm = TRUE),
    sd_engagement = sd(engagement, na.rm = TRUE),

    followers_start = {
      x <- page_followers[!is.na(page_followers)]
      if (length(x) == 0) NA_real_ else x[1]
    },

    followers_end = {
      x <- page_followers[!is.na(page_followers)]
      if (length(x) == 0) NA_real_ else x[length(x)]
    },

    followers_change = followers_end - followers_start,

    mean_followership = {
      x <- page_followers[!is.na(page_followers)]
      if (length(x) == 0) NA_real_ else round(mean(x), 0)
    },

    parochial_matches_total = sum(parochial_matches, na.rm = TRUE),
    parochial_matches_average = round(mean(parochial_matches, na.rm = TRUE), 3),

    programmatic_matches_total = sum(programmatic_matches, na.rm = TRUE),
    programmatic_matches_average = round(mean(programmatic_matches, na.rm = TRUE), 3),

    propagandistic_matches_total = sum(propagandistic_matches, na.rm = TRUE),
    propagandistic_matches_average = round(mean(propagandistic_matches, na.rm = TRUE), 3),

    parochial_posts = sum(dominant_style == "Parochial", na.rm = TRUE),
    programmatic_posts = sum(dominant_style == "Programmatic", na.rm = TRUE),
    propagandistic_posts = sum(dominant_style == "Propagandistic", na.rm = TRUE),
    tie_posts = sum(dominant_style == "Tie", na.rm = TRUE),
    no_match_posts = sum(dominant_style == "No match", na.rm = TRUE),

    .by = author
  ) %>%
  left_join(
    df_filtered_breakdown %>%
      select(author, Q1_posts, Q2_posts, Q3_posts),
    by = "author"
  ) %>%
  mutate(
    Q1_posts = coalesce(Q1_posts, 0L),
    Q2_posts = coalesce(Q2_posts, 0L),
    Q3_posts = coalesce(Q3_posts, 0L),

    group = if_else(
      PEC135 == 1 & Q2_posts >= 1,
      "Wolves",
      "Other politicians",
      missing = "Other politicians"
    ),
    group = factor(group, levels = c("Other politicians", "Wolves"))
  ) %>%
  select(author,group,PEC135,Q1_posts,Q2_posts,Q3_posts,native_video_posts,photo_posts,live_video_complete_posts,
         link_posts,youtube_posts,state,party,party_ideology,hashtags,domain,total_posts,avg_engagement,sd_engagement,
         followers_start,followers_end,followers_change,mean_followership,
         parochial_matches_total,parochial_matches_average,programmatic_matches_total,programmatic_matches_average,
         propagandistic_matches_total,propagandistic_matches_average,parochial_posts,programmatic_posts,
         propagandistic_posts
  )
```

```{r}
fb_breakdown %>%
  summarise(
    `PEC135 + Q1` = sum(PEC135 == 1 & Q1_posts >= 1, na.rm = TRUE),
    `PEC135 + Q1 + Q2` = sum(PEC135 == 1 & Q1_posts >= 5 & Q2_posts >= 5, na.rm = TRUE),
    `PEC135 + Q1 + Q2 + Q3` = sum(PEC135 == 1 & Q1_posts >= 5 & Q2_posts >= 5 & Q3_posts >= 1, na.rm = TRUE)
  ) %>%
  tidyr::pivot_longer(
    cols = everything(),
    names_to = "condition",
    values_to = "n_authors"
  )
```
#### Export
```{r}
# Export df_fb after GPT analysis
readr::write_csv2(
  df_fb,
  here::here("_processed_data", "df_fb_GPT.csv")
)
readr::write_rds(
  df_fb,
  here::here("_processed_data", "df_fb_GPT.rds")
)

# Export GPT_processed_data 
readr::write_csv2(
  df_fb_filtered,
  here::here("_processed_data", "election_dataset.csv")
)
readr::write_rds(
  df_fb_filtered,
  here::here("_processed_data", "election_dataset.rds")
)
```

# TO BE REVISED
### Communication Style
```{r}
p_style <- fb_breakdown %>%
  group_by(group) %>%
  summarise(
    parochial_mean = mean(parochial_matches_average, na.rm = TRUE),
    parochial_sd = sd(parochial_matches_average, na.rm = TRUE),

    programmatic_mean = mean(programmatic_matches_average, na.rm = TRUE),
    programmatic_sd = sd(programmatic_matches_average, na.rm = TRUE),

    propagandistic_mean = mean(propagandistic_matches_average, na.rm = TRUE),
    propagandistic_sd = sd(propagandistic_matches_average, na.rm = TRUE),

    .groups = "drop"
  ) %>%
  pivot_longer(
    cols = -group,
    names_to = c("style", ".value"),
    names_pattern = "(.*)_(mean|sd)"
  ) %>%
  mutate(
    style = recode(
      style,
      "parochial" = "Parochial",
      "programmatic" = "Programmatic",
      "propagandistic" = "Propagandistic"
    ),
    style = factor(style, levels = c("Parochial", "Programmatic", "Propagandistic"))
  ) %>%
  ggplot(aes(x = style, y = mean, fill = group)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(
    aes(ymin = pmax(mean - sd, 0), ymax = mean + sd),
    position = position_dodge(width = 0.8),
    width = 0.2,
    linewidth = 0.8
  ) +
  scale_fill_manual(values = c(
    "Wolves" = "coral",
    "Other politicians" = "darkgrey"
  )) +
  labs(
    title = "Average Content-Style Matches by Group",
    x = "",
    y = "Average number of matches per post",
    fill = ""
  ) +
  theme_minimal(base_family = "EB Garamond") +
  theme(
    text = element_text(family = "EB Garamond"),
    plot.title = element_text(size = 34, face = "bold", hjust = 0),
    axis.title = element_text(size = 26),
    axis.text.x = element_text(size = 24),
    axis.text.y = element_text(size = 22),
    legend.title = element_blank(),
    legend.text = element_text(size = 22),
    legend.position = "right",
    panel.grid.minor = element_blank(),
    plot.margin = margin(20, 30, 20, 30)
  )

p_style
```

```{r}
ggsave(
  filename = "Styles_Avg.png",
  path = output_path,
  plot = p_style,
  device = "png",
  width = 12,
  height = 7,
  dpi = 300
)
```


```{r}
p_dominant_style <- df_fb %>%
  left_join(
    fb_breakdown %>% select(author, group),
    by = "author"
  ) %>%
  filter(!is.na(group)) %>%
  mutate(
    dominant_style = factor(
      dominant_style,
      levels = c("Parochial", "Programmatic", "Propagandistic", "Tie", "No match")
    )
  ) %>%
  count(author, group, dominant_style, name = "n_posts") %>%
  group_by(author, group) %>%
  mutate(prop_posts = 100 * n_posts / sum(n_posts)) %>%
  ungroup() %>%
  filter(dominant_style %in% c("Parochial", "Programmatic", "Propagandistic")) %>%
  group_by(group, dominant_style) %>%
  summarise(
    mean = mean(prop_posts, na.rm = TRUE),
    sd = sd(prop_posts, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = dominant_style, y = mean, fill = group)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(
    aes(ymin = pmax(mean - sd, 0), ymax = mean + sd),
    position = position_dodge(width = 0.8),
    width = 0.2,
    linewidth = 0.8
  ) +
  scale_fill_manual(values = c(
    "Wolves" = "coral",
    "Other politicians" = "darkgrey"
  )) +
  scale_y_continuous(
    labels = scales::label_number(accuracy = 0.1, suffix = "%")
  ) +
  labs(
    title = "Dominant Content Style by Group",
    x = "",
    y = "Mean percentage of posts per account",
    fill = ""
  ) +
  theme_minimal(base_family = "EB Garamond") +
  theme(
    text = element_text(family = "EB Garamond"),
    plot.title = element_text(size = 34, face = "bold", hjust = 0),
    axis.title = element_text(size = 26),
    axis.text.x = element_text(size = 24),
    axis.text.y = element_text(size = 22),
    legend.title = element_blank(),
    legend.text = element_text(size = 22),
    legend.position = "right",
    panel.grid.minor = element_blank(),
    plot.margin = margin(20, 30, 20, 30)
  )

p_dominant_style
```

```{r}
ggsave(
  filename = "Dominant_Style.png",
  path = output_path,
  plot = p_dominant_style,
  device = "png",
  width = 12,
  height = 7,
  dpi = 300
)
```

```{r}
df_fb %>%
  left_join(fb_breakdown %>% select(author, group), by = "author") %>%
  mutate(
    dominant_style = case_when(
      parochial_matches == 0 & programmatic_matches == 0 & propagandistic_matches == 0 ~ "No match",
      parochial_matches > programmatic_matches & parochial_matches > propagandistic_matches ~ "Parochial",
      programmatic_matches > parochial_matches & programmatic_matches > propagandistic_matches ~ "Programmatic",
      propagandistic_matches > parochial_matches & propagandistic_matches > programmatic_matches ~ "Propagandistic",
      TRUE ~ "Tie"
    )
  ) %>%
  count(group, dominant_style) %>%
  group_by(group) %>%
  mutate(percent = round(100 * n / sum(n), 2))
```


# Discursive analysis

```{r}
words_to_embed <- c(
"voto", "votos", "impresso", "urna", "urnas", "eletronica", "auditavel", "pec", "pec135", "sistema", "cedula", "cedulas", "pec 135", "13519", "1352019", "eletronicas", "urnaeletronica", "auditaveis", "votoimpresso", "codigo fonte"
)

stopwords <- c(
"13519", "2018", "2020", "2022", "a", "agora", "ao", "aos", "as", "ano", "aqui", "ate", "cada", "como", "com", "da", "das", "de", "desde", "dia", "do", "dos", "durante", "ele", "eles", "em", "e", "eu", "entre", "era", "essa", "esse", "estao", "estaram", "estarei", "esta", "fez", "ficam", "foi", "foram", "fazer", "ha", "havia", "hoje", "ir","isso", "ja", "mais", "mas", "meio", "meu", "mesmo", "mil", "minha", "na", "nas", "nao", "nas", "nem", "no", "nos", "nossa", "nosso", "novo", "o", "ontem", "os", "ou", "para", "pela", "pelo", "pelos", "por", "pra", "proximo", "pode", "qual", "quando", "quem", "quer", "que", "retorno", "riograndedosul", "sabe", "sao", "se", "seja", "sem", "sera", "ser", "seria", "seu", "seus", "sim", "sido", "so", "sobre", "sou", "suas", "sua", "tambem", "teu", "tenha", "tem", "tenho", "ter", "tera", "todos", "todas", "todo", "trata", "um", "uma", "uso", "vai", "vamos", "vao", "vem", "via", "voce", "volta", "ela", "num", "feira", "hora", "deu", "apos", "esses", "atual"
)
```

The next section calculates the pointwise mutual information value of terms included in the 'body' of our social media posts. This value is defined as the logarithm of the probability of finding two words together, normalized for the probability of finding each of the words alone. To do so, I also calculated the probability that a word (W2) appears in association with the key words in 'words_to_embed' (W1), divided by the total number of word pairings across the whole corpus (and log-transformed). Based on this analysis, we are able to map out the semantic space of these social media posts.

### Against PEC135

```{r}
voting_skipgrams <- fb_against_subset %>%
  unnest_tokens(ngram, body, token = "ngrams", n = 6) %>%
    dplyr::mutate(ngramID = row_number()) %>% 
    tidyr::unite(skipgramID, postID, ngramID) %>%
    unnest_tokens(word, ngram)

voting_probs <- voting_skipgrams %>%
    pairwise_count(word, skipgramID, diag = TRUE, sort = TRUE) %>% 
    mutate(p = n / sum(n))

voting_unigram_probs <- fb_against_subset %>%
  unnest_tokens(word, body) %>%
  dplyr::count(word, sort = TRUE) %>%
  mutate(p = n / sum(n))

#normalize skipgram probabilities
voting_normalized_prob <- voting_probs %>%
    filter(n > 20) %>% #filter out skipgrams with n <=20
    dplyr::rename(word1 = item1, word2 = item2) %>%
    left_join(voting_unigram_probs %>%
                  select(word1 = word, p1 = p),
              by = "word1") %>%
    left_join(voting_unigram_probs %>%
                  select(word2 = word, p2 = p),
              by = "word2") %>%
    mutate(p_together = p / p1 / p2)
```

```{r}
against_p_together <- voting_normalized_prob %>%
    filter(word1 %in% words_to_embed) %>%
    arrange(word1, -p_together) %>%
    filter(p_together >= 0.6) %>% 
    filter(!word1 %in% stopwords & !word2 %in% stopwords)
# [p_together <1]
```

**Extract new words from word2 that are not in the original list**

```{r}
new_words <- setdiff(unique(against_p_together$word2), words_to_embed)

#Second pass — compute co-occurrences for the new words
against_p_together2 <- voting_normalized_prob %>%
  filter(word1 %in% new_words) %>%
  arrange(word1, -p_together) %>%
  filter(p_together >= 0.6) %>%
  filter(!word1 %in% stopwords & !word2 %in% stopwords)

#Combine both passes
against_p_together <- bind_rows(against_p_together, against_p_together2) %>%
  select(-p, -p1, -p2) %>%
  rename(Source = word1, Target = word2)

#remove rows with the same terms
against_p_together <- against_p_together %>%
  filter(Source != Target)
```

#### Term occurrences

```{r}
#Create a dataframe with unique terms from Source and Target columns
against_unique_terms <- data.frame(
  term = unique(c(against_p_together$Source, against_p_together$Target)),
  stringsAsFactors = FALSE
)
                     
# Create a regular expression pattern to match any of the unique ids
against_pattern <- paste(against_unique_terms$term, collapse = "|")

# Extract all occurrences of unique ids from "body" column
against_nodes <- lapply(fb_against_subset[c("body")], function(x) {
  str_extract_all(x, against_pattern, simplify = FALSE)
})

against_nodes_list <- against_nodes %>%
  unlist() %>%
  as.data.frame()

  colnames(against_nodes_list) <- "Id"
  
  against_nodes_list <- against_nodes_list %>%
  filter(!is.na(Id))

against_nodes_mentioned <- against_nodes_list %>%
  group_by(Id) %>%
  count()

# write.csv(against_nodes_mentioned, "against_nodes_mentioned.csv", row.names = FALSE)
```

```{r}
# Split the against_pattern string into individual words
against_words <- str_split(against_pattern, "\\|")[[1]]

# Create the against_authors_count dataset
against_unique_authors <- unique(fb_against_subset$author)
against_authors_count <- data.frame(author = against_unique_authors)

# Function to count occurrences of words in a text
count_occurrences <- function(text, words) {
  word_counts <- sapply(words, function(word) sum(str_count(text, fixed(word))))
  return(word_counts)
}

# Iterate over each author and each row to count occurrences
for (i in 1:nrow(against_authors_count)) {
  author <- against_authors_count$author[i]
  author_rows <- fb_against_subset %>% filter(author == !!author)
  
  word_counts <- count_occurrences(
    paste(author_rows$body, author_rows$body_image, author_rows$body_link, author_rows$body_description, collapse = " "),
    against_words
  )
  
  against_authors_count[i, names(word_counts)] <- word_counts
}

against_authors_count[is.na(against_authors_count)] <- 0

print(against_authors_count)
```

##### Gephi

```{r}
# Melt the against_authors_count dataframe
gephi_against_authors_count <- pivot_longer(against_authors_count, -author, names_to = "Target", values_to = "n")

# Rename the 'author' column to 'Source'
gephi_against_authors_count <- rename(gephi_against_authors_count, Source = author)

# Expand the rows based on the 'n' count
gephi_against_authors_count <- gephi_against_authors_count %>%
  uncount(n) %>%
  select(Source, Target)

# Export the dataset to a CSV file
# write.csv(gephi_against_authors_count, "gephi_against_authors_count.csv", row.names = FALSE)
```

```{r}
unique_against_names <- unique(c(gephi_against_authors_count$Source, gephi_against_authors_count$Target))

# Create the new dataset gephi_against_nodes
gephi_against_nodes <- data.frame(Name = unique_against_names)

# Add Node_Type column with default value 0
gephi_against_nodes$Node_Type <- 0

# Set Node_Type to 1 for matches with fb_against_individual_breakdown$author
gephi_against_nodes$Node_Type[gephi_against_nodes$Name %in% fb_against_individual_breakdown$author] <- 1

gephi_against_nodes$total_posts <- NA

# Create a named vector for total_posts from fb_against_individual_breakdown
total_posts_vector <- setNames(fb_against_individual_breakdown$total_posts, fb_against_individual_breakdown$author)

# Assign total_posts values based on matching names
gephi_against_nodes$total_posts <- total_posts_vector[gephi_against_nodes$Name]

# Replace NA with 0 for those without a match (if desired)
gephi_against_nodes$total_posts[is.na(gephi_against_nodes$total_posts)] <- 0

# Create a named vector for term frequencies from against_nodes_mentioned
against_term_frequency_vector <- setNames(against_nodes_mentioned$n, against_nodes_mentioned$Id)

# Create the Term_Frequency column separately to avoid referencing it before creation
gephi_against_nodes <- gephi_against_nodes %>%
  mutate(Term_Frequency = if_else(
    Node_Type == 0,
    against_term_frequency_vector[Name],
    NA_real_
  ))

# Replace NAs with 0
gephi_against_nodes <- gephi_against_nodes %>%
  mutate(Term_Frequency = replace_na(Term_Frequency, 0))

# Gephi Labeling 
gephi_against_nodes <- gephi_against_nodes %>%
  mutate(Labels = Name)

 # write.csv(gephi_against_nodes, file = "gephi_against_nodes.csv", row.names = FALSE)
```

## Pro PEC

```{r}
pro_voting_skipgrams <- fb_pro_subset %>%
  unnest_tokens(ngram, body, token = "ngrams", n = 6) %>%
    dplyr::mutate(ngramID = row_number()) %>% 
    tidyr::unite(skipgramID, postID, ngramID) %>%
    unnest_tokens(word, ngram)

pro_voting_probs <- pro_voting_skipgrams %>%
    pairwise_count(word, skipgramID, diag = TRUE, sort = TRUE) %>% 
    mutate(p = n / sum(n))

pro_voting_unigram_probs <- fb_pro_subset %>%
  unnest_tokens(word, body) %>%
  dplyr::count(word, sort = TRUE) %>%
  mutate(p = n / sum(n))

#normalize skipgram probabilities
pro_voting_normalized_prob <- pro_voting_probs %>%
    filter(n > 20) %>% #filter out skipgrams with n <=20
    dplyr::rename(word1 = item1, word2 = item2) %>%
    left_join(pro_voting_unigram_probs %>%
                  select(word1 = word, p1 = p),
              by = "word1") %>%
    left_join(pro_voting_unigram_probs %>%
                  select(word2 = word, p2 = p),
              by = "word2") %>%
    mutate(p_together = p / p1 / p2)
```

```{r}
pro_p_together <- pro_voting_normalized_prob %>%
    filter(word1 %in% words_to_embed) %>%
    arrange(word1, -p_together) %>%
    filter(p_together >= 0.6) %>% 
    filter(!word1 %in% stopwords & !word2 %in% stopwords)
# [p_together <1]
```

**Extract new words from word2 that are not in the original list**

```{r}
new_words_pro <- setdiff(unique(pro_p_together$word2), words_to_embed)

# Second pass: word1 in new words
pro_p_together2 <- pro_voting_normalized_prob %>%
  filter(word1 %in% new_words_pro) %>%
  arrange(word1, -p_together) %>%
  filter(p_together >= 0.6) %>%
  filter(!word1 %in% stopwords & !word2 %in% stopwords)

# Combine both passes
pro_p_together <- bind_rows(pro_p_together, pro_p_together2) %>%
  select(-p, -p1, -p2) %>%
  rename(Source = word1, Target = word2)

# Remove rows where Source == Target
pro_p_together <- pro_p_together %>%
  filter(Source != Target)
```

#### Terms occurrences

```{r}
#Create a dataframe with unique terms from Source and Target columns
pro_unique_terms <- data.frame(
  term = unique(c(pro_p_together$Source, pro_p_together$Target)),
  stringsAsFactors = FALSE
)
                     
# Create a regular expression pattern to match any of the unique ids
pro_pattern <- paste(pro_unique_terms$term, collapse = "|")

# Extract all occurrences of unique ids from "body" column
pro_nodes <- lapply(fb_against_subset[c("body", "body_image", "body_link", "body_description")], function(x) {
  str_extract_all(x, pro_pattern, simplify = FALSE)
})

pro_nodes_list <- pro_nodes %>%
  unlist() %>%
  as.data.frame()

  colnames(pro_nodes_list) <- "Id"
  
  pro_nodes_list <- pro_nodes_list %>%
  filter(!is.na(Id))

pro_nodes_mentioned <- pro_nodes_list %>%
  group_by(Id) %>%
  count()

# write.csv(pro_nodes_mentioned, "pro_nodes_mentioned.csv", row.names = FALSE)
```

```{r}
# Split the pro_pattern string into individual words
pro_words <- str_split(pro_pattern, "\\|")[[1]]

# Create the pro_authors_count dataset
unique_authors <- unique(fb_pro_subset$author)
pro_authors_count <- data.frame(author = unique_authors)

# Function to count occurrences of words in a text
count_occurrences <- function(text, words) {
  word_counts <- sapply(words, function(word) sum(str_count(text, fixed(word))))
  return(word_counts)
}

# Iterate over each author and each row to count occurrences
for (i in 1:nrow(pro_authors_count)) {
  author <- pro_authors_count$author[i]
  author_rows <- fb_pro_subset %>% filter(author == !!author)
  
  word_counts <- count_occurrences(
    paste(author_rows$body, author_rows$body_image, author_rows$body_link, author_rows$body_description, collapse = " "),
    pro_words
  )
  
  pro_authors_count[i, names(word_counts)] <- word_counts
}

pro_authors_count[is.na(pro_authors_count)] <- 0

print(pro_authors_count)
```

##### Gephi

```{r}
# Melt the pro_authors_count dataframe
gephi_pro_authors_count <- pivot_longer(pro_authors_count, -author, names_to = "Target", values_to = "n")

# Rename the 'author' column to 'Source'
gephi_pro_authors_count <- rename(gephi_pro_authors_count, Source = author)

# Expand the rows based on the 'n' count
gephi_pro_authors_count <- gephi_pro_authors_count %>%
  uncount(n) %>%
  select(Source, Target)

# Export the dataset to a CSV file
write.csv(gephi_pro_authors_count, "gephi_pro_authors_count.csv", row.names = FALSE)
```
